### 2016-04-11 scquant/MANUAL/squant-SOP.Rmd
scquant sanity check

---
title: | 
  | Portable Proteomics Pipeline (P3) 
  | Spectrum Count Quantification
author: "Daniel Kristiyanto (daniel.kristiyanto@pnnl.gov)"
date: \today
fontsize: 11pt
output: pdf_document
bibliography: ref.bib
csl: biomed-central.csl
header-includes:
  \usepackage{fancyhdr}
  \usepackage{graphicx}
  \usepackage{hyperref}
  \pagestyle{fancy}
  \setlength\headheight{28pt}
  \rhead{\includegraphics[width = .2\textwidth]{pnnllogo.png}}
  \fancyfoot[LE,RO]{kristiyanto/p3:scquant}
---
\rule{\textwidth}{1pt}
Portable Proteomics Pipeline (P3) is a series of protein mass spectrometry data pre-processing pipelines in Docker containers. The packages includes protein identification, filtering, and quantification for both labeled and label-free mass spectrometry data.

This document discuss the ```kristiyanto/p3:scquant``` container, a spectrum count quantification pipeline for label-free mass spectrometry protein quantification. The pipeline is based on MSnID pipeline [@msnid].

#Input
The container takes the following files: 
```
p3.config # Configuration file
*.mzid    # mzIdentML files resulted from p3:msgf container or other identification tools.
```

```p3.config``` may contain various parameters for p3 related containers. To run spectrum count quantification, ```p3.config``` must contain the following information:

```
[spectrum_count]
score_treshold = 7.0  # The scoring treshold 
error_treshold = 20   # Error Treshold
fdr = 0.01            # False Discovery Rate
iteration = 5000      # Number of iteration

```
#Running the Container
to run the container, a docker engine must be installed. A more information about installing Docker engine is available at \url{https://docs.docker.com/engine/installation/}. Input files must be mounted to ```/root/data``` within the container. This can be done by using ```-v``` switch. For MacOS and Windows users, the folder should be located under ```C:\Users``` or ```/Users/```. More information about volumens in Docker containers is available at \url{http://container-solutions.com/understanding-volumes-docker/}

```
# Download/update the container from DockerHub
docker pull kristiyanto/p3:squant   
# Run the container
docker run --rm -v /Users/path/files:/root/data kristiyanto/p3:scquant
```

#Output
Once the quantification process is completed, ```LabelFreeQuant.txt``` and ```msnset.rda``` are generated. ```LabelFreeQuant.txt``` is a tab delimited file with the quantification results, with each column represented from each of the ```mzid``` file provided. ```msnset.rda``` is an msnset object for the result that can be easily imported to R for additional analysis.

# Pipeline
```kristiyanto/p3:scquant``` is based on R, and it uses MSnID package and pipeline. A more detailed information about the pipeline is available at \url{http://bioconductor.org/packages/release/bioc/vignettes/MSnID/inst/doc/msnid_vignette.pdf}.

For this documentation, three ```mzid``` files are processed.

```{r echo=FALSE,warning=FALSE, message=FALSE}
library("ggplot2")
library("rpx")
library("mzID")
library("MSnID")
library("MSnbase")
setwd("~/Desktop/biodiversity/")
load("scquant_results.RData")
pepCleav <- unique(psms(mzid)[,c("numMissCleavages", "isDecoy", "peptide")])
pepCleav <- as.data.frame(table(pepCleav[,c("numMissCleavages", "isDecoy")]))
```

```{r}
# Files
print(mz.files)
prop.table(table(mzid$numIrregCleavages))
```

```{r echo=FALSE}
ggplot(pepCleav, aes(x=numMissCleavages, y=Freq, fill=isDecoy)) + geom_bar(stat='identity', position='dodge')+ggtitle("Number of Missed Cleavages")
```

## Filter
Filtering is done by using the parameter defined in the ```p3.config``` file. The filtering is including the error calculation (`variable: error_treshold`), scoring (`variable: score_treshold`), and filter optimization (`variable: iteration and fdr`).
```{r}
show(mzid)
show(fObj)
evaluate_filter(prj, fObj, level="PSM")
evaluate_filter(prj, fObj, level="peptide")
evaluate_filter(prj, fObj, level="accession")
show(prj)
```
##Quantification
Quantification is done by using the MSnBase package [@msnbase].
```{r}
msnset  <- as(prj, "MSnSet")
msnset  <- combineFeatures(msnset, fData(msnset)$accession, redundancy.handler="unique", 
                           fun="sum",cv=FALSE)
```

##Results
```{r}
exprs.table     <- exprs(msnset)
exprs.table     <- cbind(Protein=row.names(exprs.table), as.data.frame(exprs.table))
head(exprs.table)
```

# References

### 2016-04-11 scquant/filter.R

@@ -17,7 +17,7 @@ if (length(args)!=4) {
 }
 
 print("score.treshold:", score.treshold)
-print("error.treshold", error.treshold)
+print("error.treshold:", error.treshold)
 print("fdr", fdr)
 print("iteration", iteration)
 
@@ -29,12 +29,12 @@ mz.files <- list.files(path = ".", pattern ="mzid", all.files = F,
 ####################################### FILTERING ###################################################
 
 prj               <- MSnID(".")
-prj               <- read_mzIDs(object = prj, mzids = mz.files)
-prj               <- assess_termini(prj)
-prj               <- assess_missed_cleavages(prj)
-show(prj)
+mzid              <- read_mzIDs(object = prj, mzids = mz.files)
+mzid              <- assess_termini(mzid)
+mzid              <- assess_missed_cleavages(mzid)
+show(mzid)
 #print(paste("Before Filtering:",length(accessions(prj))))
-prj               <- apply_filter(prj, "numIrregCleavages == 0")
+prj               <- apply_filter(mzid, "numIrregCleavages == 0")
 prj               <- apply_filter(prj, "numMissCleavages < 2")
 prj$msmsScore     <- -log10(prj$`MS-GF:SpecEValue`)
 prj               <- correct_peak_selection(prj)
@@ -56,10 +56,9 @@ prj <- apply_filter(prj, "!grepl('XXX_', accession)")
 ####################################### QUANTIFICATION ###################################################
 msnset  <- as(prj, "MSnSet")
 msnset  <- combineFeatures(msnset, fData(msnset)$accession, redundancy.handler="unique", fun="sum",cv=FALSE)
-rm(prj)
-gc()
-tmp     <- exprs(msnset)
-tmp     <- cbind(Protein=row.names(tmp), as.data.frame(tmp))
+exprs.table     <- exprs(msnset)
+exprs.table     <- cbind(Protein=row.names(exprs.table), as.data.frame(exprs.table))
           
 write.table(tmp, file="SpectrumCount.txt", sep="\t", row.names = F, col.names = T)
 save(msnset, file = "msnset.rda")
+save.image(file="scquant_results.RData")

### 2016-04-11 itraquant/MANUAL/iTRAQ4_Quantification.Rmd
itraquant documentation

---
title: | 
  | Portable Proteomics Pipeline (P3) 
  | Labelled (iTRAQ4) Quantification
author: "Daniel Kristiyanto (daniel.kristiyanto@pnnl.gov)"
date: \today
fontsize: 11pt
output: pdf_document
bibliography: ../../media/ref.bib
nocite: |
  @domon2006mass, @deutsch2010mass, @MSnba83
csl: ../../media/biomed-central.csl
header-includes:
  \usepackage{fancyhdr}
  \usepackage{graphicx}
  \usepackage{hyperref}
  \pagestyle{fancy}
  \setlength\headheight{28pt}
  \rhead{\includegraphics[width = .2\textwidth]{../../media/pnnllogo.png}}
  \fancyfoot[LE,RO]{kristiyanto/p3:itraquant}
---
\rule{\textwidth}{1pt}
Portable Proteomics Pipeline (P3) is a series of protein mass spectrometry data pre-processing pipelines in Docker containers. The packages includes protein identification, filtering, and quantification for both labeled and label-free mass spectrometry data.

This document discuss the ```kristiyanto/p3:itraquant``` container, a spectrum count quantification pipeline for label-free mass spectrometry protein quantification. The pipeline is based on MSNbase pipeline [@msnbase].

#Input
The container takes the following files: 
```
p3.config # Configuration file
*.mzid    # mzIdentML files resulted from p3:msgf container or other identification tools.
*.mzML    # Mass Spectrometer output files
```

```p3.config``` may contain various parameters for p3 related containers. To run spectrum count quantification, ```p3.config``` must contain the following information:

```
[itraq4]
evalue_treshold = 1e-10 # Evalue treshold. Features with evalue higher than 
                # this value will be discarded. 
                # Check MSNbase: removeNoID documentation for more detailed information.
pNA    = 0      # 0 to 1. Ratio of NA allowed for a feature. 
                # 0 indicates that features with any missing value will be discarded. 
                # Check MSNbase: filterNA documentation for more detailed information.
quant_method = sum      # Quantification method.
                # Check MSNbase: quantify documentation for more detailed information.
combine_by = mean       # Function used for feature aggregation.
                # Check MSNbase: combineFeatures for more detailed documentation for more detailed information.
```
#Running the Container
to run the container, a docker engine must be installed. A more information about installing Docker engine is available at \url{https://docs.docker.com/engine/installation/}. Input files must be mounted to ```/root/data``` within the container. This can be done by using ```-v``` switch. For MacOS and Windows users, the folder should be located under ```C:\Users``` or ```/Users/```. More information about volumens in Docker containers is available at \url{http://container-solutions.com/understanding-volumes-docker/}

```
# Download/update the container from DockerHub
docker pull kristiyanto/p3:itraquant   
# Run the container
docker run --rm -v /Users/path/files:/root/data kristiyanto/p3:itraquant
```

#Output
Once the quantification process is completed, ```LabelledQuant.txt```, ```evalue.txt```, and ```msnset.rda``` are generated. ```LabelledQuant.txt``` is a tab delimited file with the quantification results, with each column represented from each of the ```mzML``` file provided. ```evalue.txt``` is the raw data of the identification and evalue for each features. ```msnset.rda``` is an msnset object for the final result that can be easily imported to R for additional analysis.

# Pipeline
```kristiyanto/p3:scquant``` is based on R, and it uses MSNbase [@msnbase] package and pipeline. A more detailed information about the pipeline is available at \url{http://bioconductor.org/packages/release/bioc/vignettes/MSnID/inst/doc/msnid_vignette.pdf}.

For this documentation, three paired of experiment files are processed.

```{r echo=FALSE,warning=FALSE, message=FALSE}
library("ggplot2")
library(MSnbase)
library(mzID)
library(stringr)
setwd("~/Desktop/tcga/")
load("itraq_results.RData")

```

```{r}
# Files
print(mzid.files)
print(mzml.files)
```

## Identification
Identification is performed by using ```addIdentificationData()``` function from MSnBase package.

```{r}
idSummary(msexp.id)
fData(msexp.id)[1:3,]
```

## Filter
Filtering is done by: 1) Removing unidentified features, and features with e-value higher than ```evalue_treshold``` value described in ```p3.config```. 2) features that are asssigned by multiple protein groups.

```{r}
# Prior Filtering
length(msexp.id)
k                 <- (fData(msexp.id)$'ms-gf:evalue'< evalue_treshold)
k[is.na(k)]       <- FALSE
msexp.filter1     <- removeNoId(msexp.id, keep=k)
length(msexp.filter1)
msexp.filter2     <- removeMultipleAssignment(msexp.filter1)
length(msexp.filter2)
fData(msexp.filter2)[1:3,]
```

##Quantification
Quantification is done by using the MSnBase package [@msnbase], with method specified on the `p3.config` file.
```{r}
head(exprs(qnt))
qnt.filtered      <- filterNA(qnt, pNA = pNA)
head(exprs(qnt.filtered))
```

##Results
subsequently, the features are aggregated by accession ID, with the value calculated using the function denoted on the `p3.config`.
```{r}
length(exprs(qnt))
result  <- combineFeatures(qnt, groupBy = fData(qnt)$accession, fun=combine_by)
length(exprs(result))
head(exprs(result))
```

# References

### 2016-04-11 itraquant/itraq.R

@@ -1,9 +1,15 @@
+## Labelled (iTRAQ4) Mass Spectometry Protein Quantification
+## Docker Package: p3:itraquant
+## Daniel Kristiyanto (daniel.kristiyanto@pnnl.gov)
+
 library(MSnbase)
 library(mzID)
 library(stringr)
 
 setwd("/root/data")
 
+evalue_treshold = 1e-10
+pNA             = 0
 ####################################### READ FILE ###################################################
 print("Isobaric Tagging Quantification")
 mzid.files        <- list.files(path = ".", pattern ="mzid", all.files = F, 
@@ -16,37 +22,30 @@ msexp.raw         <- readMSData(mzml.files)
 
 ####################################### IDENTIFICATION ###################################################
 print("Identifiying...")
-msexp             <- addIdentificationData(msexp.raw, id = mzids.raw)
-idSummary(msexp)
-msexp             <- removeNoId(msexp)
-msexp             <- removeMultipleAssignment(msexp)
+msexp.id          <- addIdentificationData(msexp.raw, id = mzids.raw)
+idSummary(msexp.id)
+k                 <- (fData(msexp.id)$'ms-gf:evalue'< e.value)
+k[is.na(k)]       <- FALSE
+msexp.filter1     <- removeNoId(msexp.id, keep=k)
+msexp.filter2     <- removeMultipleAssignment(msexp.filter1)
 
-####################################### CLEAN UP ###################################################
-rm(mzid.files)
-rm(mzml.files)
-rm(msexp.raw)
-rm(mzids.raw)
-gc()
 ####################################### QUANTIFICATION ###################################################
 print("Quantifying...")
-qnt               <- quantify(msexp, method="max", reporters=iTRAQ4, strict=F, verbose=F)
-qnt               <- filterNA(qnt, pNA = 0)
-agg               <- combineFeatures(qnt, groupBy = fData(qnt)$accession, fun="mean")
+qnt               <- quantify(msexp.filter2, method="max", reporters=iTRAQ4, strict=F, verbose=F)
+qnt.filtered      <- filterNA(qnt, pNA = pNA)
+result            <- combineFeatures(qnt, groupBy = fData(qnt)$accession, fun="mean")
 
-head(exprs(agg))
+head(exprs(result))
 ####################################### OUTPUT ###################################################
[…]

### 2016-04-27 STEP1/_functions.py
ALL IN ONE!

@@ -1,222 +1,0 @@
-# DANIEL.KRISTIYANTO@PNNL.GOV
-# MSGF
-
-import os
-import sys
-import subprocess
-import re
-from os.path import isfile, join
-from urllib.parse import urlparse
-from ftplib import FTP
-######################## CHECK OPTIONS ###########################
-def get_msgf_opts(cfg_file):
-	r_options = []
-	global_options = SafeConfigParser()
-	try: 
-		global_options.read(cfg_file)
-		sc_options = ["method","msgf_options","source"]
-		for o in sc_options:
-			print(o +": "+global_options.get("step1",o))
-			r_options.append(global_options.get("step1",o))
-		return global_options
-	except:
-		print("Configuration File Error.")
-
-def get_sc_opts(cfg_file):
-	r_options = []
-	parser = SafeConfigParser()
-	try: 
-		parser.read(cfg_file)
-		sc_options = ["score_treshold","error_treshold", "fdr", "iteration"]
-		for o in sc_options:
-			print(o +": "+parser.get("spectrum_count",o))
-			r_options.append(parser.get("spectrum_count",o))
-		return r_options
-	except:
-		print("Configuration File Error.")
-
-
-def get_itraq_opts(cfg_file):
-	r_options = []
-	parser = SafeConfigParser()
-	try: 
-		parser.read(cfg_file)
-		sc_options = ["evalue_treshold","pNA", "quant_method", "combine_by"]
-		for o in sc_options:
-			print(o +": "+parser.get("itraq4",o))
-			r_options.append(parser.get("itraq4",o))
-		return r_options
-	except:
-		print("Configuration File Error.")
-
-
-######################## SUB PROCESSES ###########################
-
-def write_config(working_dir):
-	try:
-		with open(os.path.join(working_dir,"p3.config"),"w") as f:
-			f.write("[step1]\n")
-			f.write("#ftp_src1=\n")
-			f.write("#ftp_src2=\n")
-			f.write("method=spectrum_count\n")
-			f.write("msgf_options=\n")
-			f.write("[spectrum_count]\n")
-			f.write("score_treshold = 7.0\n")
-			f.write("error_treshold = 20\n")
-			f.write("fdr = 0.01\n")
-			f.write("iteration = 5000\n")
-			f.write("#[itraq4]\n")
[…]

### 2016-04-27 STEP1/entry.py

@@ -1,53 +1,381 @@
-# THIS SCRIPT WILL SCAN FOR THE FILES IN A FOLDER
-# EXTRACT, IF NECESSARY, AND RUN MGSF PLUS TO 
-# NORMALIZE THE DATA
-# DANIEL.KRISTIYANTO@PNNL.GOV
-# Docker container: msgf
+##########################################################################
+## P3: Portable Proteomics Pipeline
+## DANIEL KRISTIYANTO (daniel.kristiyanto@pnnl.gov)
+## APR 27, 2016
+##########################################################################
 
-######################## ENV ###########################
+
 import gzip
+import sys
 import os
 import glob
 import os.path
-import subprocess
+import subprocess 
 import re
 import csv
 from ftplib import FTP
-from _functions import *
-from datetime import timedelta
+import configparser
 from datetime import datetime
 import time
+from urllib.parse import urlparse
 
-working_dir = os.getcwd() +"/data/"
+# Set Env
+working_dir = "/root/data"
+working_dir = "/Users/Daniel/Desktop/LABELLED"
+config_file = "p3.config"
+maxwait = 3 * 60 * 60 # Wait for 3 hours
+os.chdir(working_dir) if os.path.isdir(working_dir) else sys.exit("{} not found. Please make sure it's properly mounted.".format(working_dir))
 
-spectrum 	= []
-out 		= []
-db 			= None
-module 		= None
-input_csv	= None
-start_time = time.time()
-print("Start at:", str(datetime.now()))
+def main():
 
-db, input_csv 			= scan_dir(working_dir)
+    start_time = time.time()
+    print("Starting at: {}".format(str(datetime.now())))
+    
+    # Scan for config file
+    if os.path.isfile(config_file) is False:
+        print("p3.config is not found.")
+        write_blank_p3(config_file)
+
+    # Gather the files
+    options = check_config(config_file)
+    get_files(options)
+    
+        
+    # Unzip the files 
+    unzip_files()
+
+    # Re-List the files
+    fasta = scan_fasta()
+    
+    spectrum = scan_files((".mzml",".mgf",".mzxml",".ms2",".pkl"))
+    
+    if (len(spectrum)!=0):
+        print("{} Spectrum files found: {}".format(len(spectrum), spectrum))
+    else:
+        print("File not found Accepted files: {}".format(ext))
+    
+    Q_METHOD = options.get("QUANTIFICATION","METHOD").upper()
[…]

### 2016-04-27 STEP1/entry.py
ALL IN ONE!

@@ -138,7 +138,7 @@ def itraq(mzid, options):
     lock = mzid[:-5] + ".rda.tmp"
     out = mzid[:-5]+".rda"
     if os.path.isfile(out) or os.path.isfile(lock):
-        print("{} exists. Skipping".format(lock))
+        print("{} ... next.".format(lock))
     else:
         cmd = ['Rscript', "itraq.R"]
         mzml = ""
@@ -268,7 +268,7 @@ def fetch_ftp(ftp_url):
     print("Downloading...")
     for filename in ftp.nlst(filematch)[0:3]:
         if os.path.isfile(filename):
-            print("{} already exists. Skipping..".format(filename))
+            print("{} already exists. Next..".format(filename))
         else:
             try:
                 fhandle = open(filename, 'wb')

### 2016-04-28 STEP1/entry.py
itraquant for p3

@@ -14,7 +14,7 @@ import subprocess
 import re
 import csv
 from ftplib import FTP
-import configparser
+from backports import configparser
 from datetime import datetime
 import time
 from urllib.parse import urlparse
@@ -28,354 +28,357 @@ os.chdir(working_dir) if os.path.isdir(working_dir) else sys.exit("{} not found.
 
 def main():
 
-    start_time = time.time()
-    print("Starting at: {}".format(str(datetime.now())))
-    
-    # Scan for config file
-    if os.path.isfile(config_file) is False:
-        print("p3.config is not found.")
-        write_blank_p3(config_file)
+	start_time = time.time()
+	print("Starting at: {}".format(str(datetime.now())))
+	
+	# Scan for config file
+	if os.path.isfile(config_file) is False:
+		print("p3.config is not found.")
+		write_blank_p3(config_file)
 
-    # Gather the files
-    options = check_config(config_file)
-    get_files(options)
-    
-        
-    # Unzip the files 
-    unzip_files()
+	# Gather the files
+	options = check_config(config_file)
+	get_files(options)
+	
+		
+	# Unzip the files 
+	unzip_files()
 
-    # Re-List the files
-    fasta = scan_fasta()
-    
-    spectrum = scan_files((".mzml",".mgf",".mzxml",".ms2",".pkl"))
-    
-    if (len(spectrum)!=0):
-        print("{} Spectrum files found: {}".format(len(spectrum), spectrum))
-    else:
-        print("File not found Accepted files: {}".format(ext))
-    
-    Q_METHOD = options.get("QUANTIFICATION","METHOD").upper()
-    RUN_MSGF = (options.get("MSGF", "RUN_MSGF").upper() == "YES")
-    
-    print("Running MSGF") if RUN_MSGF else print("Skipping MSGF identification...")
-    
-    
-    # Run MSGF 
-    if fasta and spectrum and RUN_MSGF:
-        try:
-            msgf_opts = options.get("MSGF", "MSGF_OPTIONS").upper()
-            if (len_msgf_opts !=0): msgf(spectrum, fasta, options, msgf_opts)
-        except:
-            msgf(spectrum, fasta, options)
-    
+	# Re-List the files
+	fasta = scan_fasta()
+	
[…]

### 2016-04-28 STEP1/itraq.R

@@ -1,0 +1,81 @@
+## Labelled (iTRAQ4) Mass Spectometry Protein Quantification
+## Docker Package: p3:itraquant
+## Daniel Kristiyanto (daniel.kristiyanto@pnnl.gov)
+
+library(MSnbase)
+library(mzID)
+library(stringr)
+
+start.time = Sys.time()
+args = commandArgs(trailingOnly=TRUE)
+
+print(args)
+
+if (length(args)!=4) {
+  stop("Arguments ", call.=FALSE)
+} else {
+  evalue_treshold  	= as.double(args[1])
+  pNA 				= as.numeric(args[2])
+  quant_method		= args[3]
+  combine_by		= args[4]
+}
+
+print(paste("evalue_treshold:", evalue_treshold))
+print(paste("pNA:", pNA))
+print(paste("quant_method:", quant_method))
+print(paste("combine_by:", combine_by))
+
+setwd("/root/data")
+
+####################################### READ FILE ###################################################
+print("Isobaric Tagging Quantification")
+mzid.files        <- list.files(path = ".", pattern ="mzid", all.files = F, 
+                       full.names = F, recursive = F, ignore.case = T, include.dirs = F)
+mzml.files        <- list.files(path = ".", pattern ="mzML$|mzXML$", all.files = F, 
+                       full.names = F, recursive = F, ignore.case = T, include.dirs = F)
+
+mzids.raw         <- mzID(mzid.files)
+msexp.raw         <- readMSData(mzml.files)
+
+####################################### IDENTIFICATION & FILTERING ###################################################
+print("Identifiying...")
+msexp.id          <- addIdentificationData(msexp.raw, id = mzids.raw)
+idSummary(msexp.id)
+rm(mzid.files)
+rm(mzml.files)
+rm(mzids.raw)
+rm(msexp.raw)
+gc(verbose = FALSE)
+
+print("Filtering...")
+k                 <- (fData(msexp.id)$'ms-gf:evalue'< evalue_treshold)
+k[is.na(k)]       <- FALSE
+msexp.filter1     <- removeNoId(msexp.id, keep=k)
+msexp.filter2     <- removeMultipleAssignment(msexp.filter1)
+
+rm(msexp.id)
+rm(msexp.filter1)
+gc(verbose = FALSE)
+####################################### QUANTIFICATION ###################################################
+print("Quantifying...")
[…]

### 2016-04-28 STEP1/entry.py
all in one.

@@ -14,14 +14,14 @@ import subprocess
 import re
 import csv
 from ftplib import FTP
-from backports import configparser
+import configparser
 from datetime import datetime
 import time
 from urllib.parse import urlparse
 
 # Set Env
 working_dir = "/root/data"
-working_dir = "/Users/Daniel/Desktop/LABELLED"
+#working_dir = "/Users/Daniel/Desktop/LABELLED"
 config_file = "p3.config"
 maxwait = 3 * 60 * 60 # Wait for 3 hours
 os.chdir(working_dir) if os.path.isdir(working_dir) else sys.exit("{} not found. Please make sure it's properly mounted.".format(working_dir))
@@ -46,27 +46,30 @@ def main():
 
 	# Re-List the files
 	fasta = scan_fasta()
-	
-	spectrum = scan_files((".mzml",".mgf",".mzxml",".ms2",".pkl"))
+	sp_files_ext = (".mzml",".mgf",".mzxml",".ms2",".pkl", ".mzXML")
+	spectrum = scan_files(sp_files_ext)
 	
 	if (len(spectrum)!=0):
 		print("{} Spectrum files found: {}".format(len(spectrum), spectrum))
 	else:
-		print("File not found Accepted files: {}".format(ext))
+		print("No spectrum files found. Accepted format:{} ".format(sp_files_ext))
 	
 	Q_METHOD = options.get("QUANTIFICATION","METHOD").upper()
 	RUN_MSGF = (options.get("MSGF", "RUN_MSGF").upper() == "YES")
 	
-	#print("Running MSGF") if RUN_MSGF else print("Skipping MSGF identification...")
-	
-	
+
 	# Run MSGF 
 	if fasta and spectrum and RUN_MSGF:
+		print("Running MSGF") 
+
 		try:
 			msgf_opts = options.get("MSGF", "MSGF_OPTIONS").upper()
 			if (len_msgf_opts !=0): msgf(spectrum, fasta, options, msgf_opts)
 		except:
 			msgf(spectrum, fasta, options)
+	else:
+		print("Skipping MSGF identification...")
+
 	
 
 	if Q_METHOD == "SPECTRUM_COUNT":
@@ -79,6 +82,7 @@ def main():
 			if len(mzid_set) == 0:
 				sys.exit("No .mzid file found")
 			elif len(scan_files('.mzid.tmp')) != 0: 
[…]

### 2016-04-28 STEP1/itraq.R

@@ -1,5 +1,5 @@
 ## Labelled (iTRAQ4) Mass Spectometry Protein Quantification
-## Docker Package: p3:itraquant
+## Docker Package: p3
 ## Daniel Kristiyanto (daniel.kristiyanto@pnnl.gov)
 
 library(MSnbase)
@@ -11,28 +11,30 @@ args = commandArgs(trailingOnly=TRUE)
 
 print(args)
 
-if (length(args)!=4) {
+if (length(args)!=6) {
   stop("Arguments ", call.=FALSE)
 } else {
-  evalue_treshold  	= as.double(args[1])
-  pNA 				= as.numeric(args[2])
-  quant_method		= args[3]
-  combine_by		= args[4]
+  mzml.files 		= args[1]
+  mzid.files 		= args[2]
+  evalue_treshold  	= as.double(args[3])
+  pNA 				= as.numeric(args[4])
+  quant_method		= args[5]
+  out_file 			= args[6]
 }
 
 print(paste("evalue_treshold:", evalue_treshold))
 print(paste("pNA:", pNA))
 print(paste("quant_method:", quant_method))
-print(paste("combine_by:", combine_by))
+
 
 setwd("/root/data")
 
 ####################################### READ FILE ###################################################
 print("Isobaric Tagging Quantification")
-mzid.files        <- list.files(path = ".", pattern ="mzid", all.files = F, 
-                       full.names = F, recursive = F, ignore.case = T, include.dirs = F)
-mzml.files        <- list.files(path = ".", pattern ="mzML$|mzXML$", all.files = F, 
-                       full.names = F, recursive = F, ignore.case = T, include.dirs = F)
+#mzid.files        <- list.files(path = ".", pattern ="mzid", all.files = F, 
+#                       full.names = F, recursive = F, ignore.case = T, include.dirs = F)
+#mzml.files        <- list.files(path = ".", pattern ="mzML$|mzXML$", all.files = F, 
+#                       full.names = F, recursive = F, ignore.case = T, include.dirs = F)
 
 mzids.raw         <- mzID(mzid.files)
 msexp.raw         <- readMSData(mzml.files)
@@ -63,19 +65,20 @@ qnt.filtered      <- filterNA(qnt, pNA = pNA)
 rm(msexp.filter2)
 rm(qnt)
 gc(verbose = FALSE)
-result            <- combineFeatures(qnt.filtered, groupBy = fData(qnt.filtered)$accession, fun=combine_by)
[…]

### 2016-04-28 STEP1/itraqfolding.R

@@ -1,0 +1,29 @@
+## Labelled (iTRAQ4) Mass Spectometry Protein Quantification
+## Docker Package: p3
+## Daniel Kristiyanto (daniel.kristiyanto@pnnl.gov)
+#######################
+
+library(MSnbase)
+
+
+setwd("/root/data")
+msnset.files        <- list.files(path = ".", pattern ="rda", all.files = F, 
+                      full.names = F, recursive = F, ignore.case = T, include.dirs = F)
+
+for (i in 1:length(msnset.files))
+{
+    load(msnset.files[i])
+    curr <- paste0(substr(msnset.files[i],1,4), i)
+    #sampleNames(qnt.filtered) <- curr
+    #qnt.filtered < updateFvarLabels(qnt.filtered, curr)
+    dim(qnt.filtered)
+    if (i == 1 )
+    {
+      msn.set <- qnt.filtered
+      qnt.filtered <- NULL
+    } else {
+      msn.set <- combine(msn.set, qnt.filtered)
+      qnt.filtered <- NULL
+    }
+}  
+

### 2016-04-28 STEP1/scquant.R

@@ -1,0 +1,65 @@
+library("rpx")
+library("mzID")
+library("MSnID")
+library("MSnbase")
+
+args = commandArgs(trailingOnly=TRUE)
+
+print(args)
+
+if (length(args)!=4) {
+  stop("Areguments ", call.=FALSE)
+} else {
+  score.treshold  = as.numeric(args[1])
+  error.treshold  = as.numeric(args[2])
+  fdr             = as.double(args[3])
+  iteration       = as.numeric(args[4])
+}
+
+print(paste("score_treshold:", score.treshold))
+print(paste("error_treshold:", error.treshold))
+print(paste("fdr:", fdr))
+print(paste("iteration:", iteration))
+
+setwd("/root/data/")
+
+mz.files <- list.files(path = ".", pattern ="mzid", all.files = F, 
+                       full.names = F, recursive = F, ignore.case = T, include.dirs = F)
+
+####################################### FILTERING ###################################################
+
+prj               <- MSnID(".")
+mzid              <- read_mzIDs(object = prj, mzids = mz.files)
+mzid              <- assess_termini(mzid)
+mzid              <- assess_missed_cleavages(mzid)
+show(mzid)
+#print(paste("Before Filtering:",length(accessions(prj))))
+prj               <- apply_filter(mzid, "numIrregCleavages == 0")
+rm(mzid)
+gc()
+prj               <- apply_filter(prj, "numMissCleavages < 2")
+prj$msmsScore     <- -log10(prj$`MS-GF:SpecEValue`)
+prj               <- correct_peak_selection(prj)
+prj$massError     <- abs(mass_measurement_error(prj)) # ppm
+fObj              <- MSnIDFilter(prj)
+fObj$msmsScore    <- list(comparison=">", threshold=score.treshold)
+fObj$massError    <- list(comparison="<", threshold=error.treshold)
+fObj.grid         <- optimize_filter(fObj, prj, fdr.max=fdr,
+                                     method="Grid", level="peptide", n.iter=iteration)
+set.seed(0)
+fObj.sann         <- optimize_filter(fObj.grid, prj, fdr.max=fdr,
+                                     method="SANN", level="peptide", n.iter=iteration)
+prj               <- apply_filter(prj, fObj.sann)
+
+prj <- apply_filter(prj, "!grepl('Contaminant', accession)")
+prj <- apply_filter(prj, "!grepl('XXX_', accession)")
+
[…]

### 2016-04-28 STEP1/entry.py
all in one

@@ -211,7 +211,6 @@ def scquant(mzid_set, options):
 	for k in opts_set:
 		cmd.append(str(R_OPTS[k]))
 	print(cmd)
-
 	subprocess.call(cmd)
 	
 	

### 2016-04-28 STEP1/itraq.R

@@ -22,6 +22,11 @@ if (length(args)!=6) {
   out_file 			= args[6]
 }
 
+print("=======================================")
+print(" iTRAQ4 Quantification")
+print("=======================================")
+
+
 print(paste("evalue_treshold:", evalue_treshold))
 print(paste("pNA:", pNA))
 print(paste("quant_method:", quant_method))

### 2016-04-28 STEP1/scquant.R

@@ -16,12 +16,23 @@ if (length(args)!=4) {
   iteration       = as.numeric(args[4])
 }
 
+
+
+print("=======================================")
+print("Spectrum Count / Label Free Quantification")
+print("=======================================")
+
+
 print(paste("score_treshold:", score.treshold))
 print(paste("error_treshold:", error.treshold))
 print(paste("fdr:", fdr))
 print(paste("iteration:", iteration))
 
 setwd("/root/data/")
+
+print("=======================================")
+print("Spectrum Count / Label Free Quantification")
+print("=======================================")
 
 mz.files <- list.files(path = ".", pattern ="mzid", all.files = F, 
                        full.names = F, recursive = F, ignore.case = T, include.dirs = F)

### 2016-04-28 STEP1/entry.py
fixing exit bug

@@ -18,6 +18,8 @@ import configparser
 from datetime import datetime
 import time
 from urllib.parse import urlparse
+from datetime import timedelta
+
 
 # Set Env
 working_dir = "/root/data"
@@ -45,7 +47,6 @@ def main():
 	unzip_files()
 
 	# Re-List the files
-	fasta = scan_fasta()
 	sp_files_ext = (".mzml",".mgf",".mzxml",".ms2",".pkl", ".mzXML")
 	spectrum = scan_files(sp_files_ext)
 	
@@ -56,7 +57,8 @@ def main():
 	
 	Q_METHOD = options.get("QUANTIFICATION","METHOD").upper()
 	RUN_MSGF = (options.get("MSGF", "RUN_MSGF").upper() == "YES")
-	
+	fasta = scan_fasta()
+
 
 	# Run MSGF 
 	if fasta and spectrum and RUN_MSGF:
@@ -70,7 +72,11 @@ def main():
 	else:
 		print("Skipping MSGF identification...")
 
-	
+	try:
+		maxwait = options.get("SOURCE", "MAXWAIT")
+		print("Max wait updated to {} seconds".format(maxwait))
+	except:
+		pass
 
 	if Q_METHOD == "SPECTRUM_COUNT":
 		keep_waiting = True
@@ -86,7 +92,7 @@ def main():
 				print("MSGF identification is being run by other containers. Waiting...")
 				if wait > maxwait:
 					keep_waiting = False
-					sys.exit("Had waited for 2 hours. Quitting now. \n Perhaps remove .tmp files and rerun containers?")
+					sys.exit("Had waited for {}s. Quitting now. \n Perhaps remove .tmp files and rerun containers?".format(maxwait))
 				else: wait = wait + 5 
 				time.sleep(5)
 			else:
@@ -104,7 +110,7 @@ def main():
 			print("Identification is being run by other containers. Waiting...")
 			if wait > maxwait:
 				keep_waiting = False
-				sys.exit("Had waited for 2 hours. Quitting now. \n Perhaps remove .tmp files and rerun containers?")
+				sys.exit("Had waited for {} hours. Quitting now. \n Perhaps remove .tmp files and rerun containers?".format(maxwait))
 			else: 
 				wait = wait + 10
 				lock_files = scan_files(".rda.tmp")
@@ -113,7 +119,8 @@ def main():
 		itraq_folding(options)
 
 	stop_time = time.time()
[…]

### 2016-04-29 itraquant/Benchmark/itraq-benchmark.Rmd
Bechmark

---
title: | 
  | Portable Proteomics Pipeline (P3) 
  | Labelled (iTRAQ4) Benchmark
author: "Daniel Kristiyanto (daniel.kristiyanto@pnnl.gov)"
date: \today
fontsize: 11pt
output: pdf_document
bibliography: ../../media/ref.bib
nocite: |
  @domon2006mass, @deutsch2010mass, @MSnba83
csl: ../../media/biomed-central.csl
header-includes:
  \usepackage{fancyhdr}
  \usepackage{graphicx}
  \usepackage{hyperref}
  \pagestyle{fancy}
  \setlength\headheight{28pt}
  \rhead{\includegraphics[width = .2\textwidth]{../../media/pnnllogo.png}}
  \fancyfoot[LE,RO]{kristiyanto/p3:benchmark}
---
\rule{\textwidth}{1pt}

```{r, warning=FALSE, echo=FALSE, include=FALSE}
#setwd("~/Documents/GITHUB/P3/itraquant/Benchmark/itraq-benchmark/")
load("~/Documents/GITHUB/P3/itraquant/Benchmark/itraq-benchmark/itraq-benchmark.RData")
library(MSnbase)
library(mzID)
cols. <- c()
cols <- c("accession", "pepseq", "ms-gf:evalue")

```

This document is to benchmark and as a sanity check to the iTRAQ4 method for the Portable Proteomics Pipelines (P3) containers.

## Results from PNNL
For this first purpose, `r length(mzid.files)` first file TCGA calculated by PNNL used as the comparasion:
```{r}
show(mzml.sp)
dim(msexp.sp) # The size of table
head(msexp.sp)[1:3,]
```

## Result from P3 container
For comparation, `r length(mzml.files )` file were also loaded and then merged with the identification data using the MSnBase package. A similar filter also applied: (1) unidentified spectrum with msgf e-value < `e evalue_treshold` and (2) spectrum with multiple identification were removed
```{r}
idSummary(msexp.id)
dim(fData(msexp.id)) # before filter
head(fData(msexp.id)[order(fData(msexp.id)[,"scan number(s)"]),])[1:3,cols]
dim(fData(msexp.filter2)) # After Filter
head(fData(msexp.id)[order(fData(msexp.filter2)[,"scan number(s)"]),])[1:3,cols]
```

## Comparing the results
Here is the results from the P3 container. Quantification used "MAX".
```{r}
head(qnt.id[order(qnt.id$accession),])[1:3,cols.p3]
```

To put in contrast, the data aboved is merged with the data from PNNL. `iTRAQ4.114 - iTRAQ4.114` indicates results from P3, while `Ion_114 - Ion_117` indicate results from PNNL.

```{r}
head(qnt.merged[,c(cols.p3, "Ion_114", "Ion_115", "Ion_116", "Ion_117")])[1:3,]
```

To see if the results coherence, correlation among each ions is computed:
```{r}
cor(qnt.merged$iTRAQ4.114, qnt.merged$Ion_114, method = "spearman", "pairwise.complete.obs")
cor(qnt.merged$iTRAQ4.115, qnt.merged$Ion_115, method = "spearman", "pairwise.complete.obs")
cor(qnt.merged$iTRAQ4.116, qnt.merged$Ion_116, method = "spearman", "pairwise.complete.obs")
cor(qnt.merged$iTRAQ4.117, qnt.merged$Ion_117, method = "spearman", "pairwise.complete.obs")
```

### 2016-04-29 itraquant/Benchmark/itraq-benchmark.R

@@ -1,0 +1,67 @@
+## Labelled (iTRAQ4) Mass Spectometry Protein Quantification
+## Benchmark for iTRAQ4 
+## Daniel Kristiyanto (daniel.kristiyanto@pnnl.gov)
+
+library(MSnbase)
+library(mzID)
+library(stringr)
+library(dplyr)
+start.time = Sys.time()
+
+evalue_treshold = 75
+pNA = 0
+quant_method = trap
+combine_by = mean
+
+####################################### READ FILE FROM PNNL ###################################################
+
+setwd("~/Documents/GITHUB/P3/itraquant/Benchmark/itraq-benchmark/PNNL")
+mzml.sp        <- list.files(path = ".", pattern ="txt", all.files = F, 
+                             full.names = F, recursive = F, ignore.case = T, include.dirs = F)[1]
+
+msexp.sp <- read.table(mzml.sp, sep="\t", header = T)
+
+
+####################################### READ FILE ###################################################
+print("Isobaric Tagging Quantification")
+setwd("~/Documents/GITHUB/P3/itraquant/Benchmark/itraq-benchmark/")
+
+mzid.files        <- list.files(path = ".", pattern ="mzid", all.files = F, 
+                                full.names = F, recursive = F, ignore.case = T, include.dirs = F)[1]
+mzml.files        <- list.files(path = ".", pattern ="mzML$|mzXML$", all.files = F, 
+                                full.names = F, recursive = F, ignore.case = T, include.dirs = F)[1]
+
+mzids.raw         <- mzID(mzid.files)
+msexp.raw         <- readMSData(mzml.files)
+mzid.flat         <- flatten(mzids.raw)
+
+
+####################################### IDENTIFICATION & FILTERING ###################################################
+print("Identifiying...")
+msexp.id          <- addIdentificationData(msexp.raw, id = mzids.raw)
+msexp.sp.id       <- merge(msexp.sp, mzid.flat, by.x = "ScanNumber", by.y="scan number(s)", all=T)
+
+msexp.sp.filtered <- msexp.sp.id[!is.na(msexp.sp.id$accession),]
[…]

### 2016-04-29 itraquant/Benchmark/itraq-benchmark.Rmd
itraq benchmark

@@
 ```{r}
-cor(qnt.merged$iTRAQ4.114, qnt.merged$Ion_114, method = "spearman", "pairwise.complete.obs")
+# Correlation for Ion Reporter 114
+cor(qnt.merged$iTRAQ4.114, qnt.merged$Ion_114, method = "spearman","pairwise.complete.obs")
+# Correlation for Ion Reporter 115
 cor(qnt.merged$iTRAQ4.115, qnt.merged$Ion_115, method = "spearman", "pairwise.complete.obs")
+# Correlation for Ion Reporter 116
 cor(qnt.merged$iTRAQ4.116, qnt.merged$Ion_116, method = "spearman", "pairwise.complete.obs")
+# Correlation for Ion Reporter 117
 cor(qnt.merged$iTRAQ4.117, qnt.merged$Ion_117, method = "spearman", "pairwise.complete.obs")
 ```
+
+# References

### 2016-05-04 itraquant/Benchmark/itraq-benchmark.Rmd
benchmark
benchmark results

--- 2016-04-29 itraquant/Benchmark/itraq-benchmark.Rmd
@@
 library(mzID)
-cols. <- c()
 cols <- c("accession", "pepseq", "ms-gf:evalue")
-
 ```
 
-This document is to benchmark and as a sanity check to the iTRAQ4 method for the Portable Proteomics Pipelines (P3) containers.
+The purpose of this document is to benchmark the iTRAQ quantification on the Portable Proteomics Pipelines (P3) containers.
 
-## Results from PNNL
-For this first purpose, `r length(mzid.files)` first file TCGA calculated by PNNL used as the comparasion:
+# Input
+1. `r mzid.files` : The identification file (product of MSGF+)
+2. `r mzml.files` : The mass spectometry dataset
+3. `r mzml.sp`    : The quantification results used to benchmark (calcullated by PNNL)
+
+# Methods
+## Identification
 ```{r}
-show(mzml.sp)
-dim(msexp.sp) # The size of table
-head(msexp.sp)[1:3,]
+## The identification file
+mzids.raw
+head(mzid.flat[order(mzid.flat[,"ms-gf:evalue"]),])[1:3,]
 ```
 
-## Result from P3 container
-For comparation, `r length(mzml.files )` file were also loaded and then merged with the identification data using the MSnBase package.
-A similar filter also applied: (1) unidentified spectrum with msgf e-value < `e evalue_treshold` and (2) spectrum with multiple identification were removed
+Based on this data, peptide `r pep` was listed as a good quality of identification with lowest e-value.
+
+## Spectrum Objects
 ```{r}
+msexp.raw
+```
+The spectrum data consists of 1606 percursor ions and with features ranged from X1.1 to x9999.1.
+
+This data then paired with the identification file using `addIdentificationData` tool from MSnBase, resulting the table below:
+```{r}
+### The spectra objects enrinched with identification file
+msexp.id
 idSummary(msexp.id)
-dim(fData(msexp.id)) # before filter
-head(fData(msexp.id)[order(fData(msexp.id)[,"scan number(s)"]),])[1:3,cols]
-dim(fData(msexp.filter2)) # After Filter
-head(fData(msexp.id)[order(fData(msexp.filter2)[,"scan number(s)"]),])[1:3,cols]
+#head(fData(msexp.id))[1:3,]
 ```
 
-## Comparing the results
-Here is the results from the P3 container. Quantification used "MAX".
+Table focusing on the peptide `r pep`:
 ```{r}
-head(qnt.id[order(qnt.id$accession),])[1:3,cols.p3]
+zoomData <- fData(msexp.id)[fData(msexp.id)$pepseq==pep & !is.na(fData(msexp.id)$pepseq),]
+zoomData
 ```
 
-To put in contrast, the data aboved is merged with the data from PNNL. `iTRAQ4.114 - iTRAQ4.114` indicates results from P3, while `Ion_114 - Ion_117` indicate results from PNNL.
+From this table, we know that this peptide was identified from features `r rownames(zoomData)`.
+
+Using the `quantify` function from MSnBase, with parameters `mehod=max, verbose=FALSE, strict=FALSE`, resulting:
 
 ```{r}
-head(qnt.merged[,c(cols.p3, "Ion_114", "Ion_115", "Ion_116", "Ion_117")])[1:3,]
+## Features 
+zoomData[,cols]
+exprs(qnt)[row.names(exprs(qnt))==row.names(zoomData),]
+plot(msexp.id[["X15545.1"]],reporters=iTRAQ4, full=T)
 ```
 
-To see if the results coherence, correlation among each ions is computed:
+## Quantification
+This quantification then compared to the quantification data resulted from PNNL, by matching the scan number.
 ```{r}
-cor(qnt.merged$iTRAQ4.114, qnt.merged$Ion_114, method = "spearman", "pairwise.complete.obs")
-cor(qnt.merged$iTRAQ4.115, qnt.merged$Ion_115, method = "spearman", "pairwise.complete.obs")
-cor(qnt.merged$iTRAQ4.116, qnt.merged$Ion_116, method = "spearman", "pairwise.complete.obs")
-cor(qnt.merged$iTRAQ4.117, qnt.merged$Ion_117, method = "spearman", "pairwise.complete.obs")
+zoomData$`scan number(s)`
+msexp.sp[msexp.sp$ScanNumber==zoomData$`scan number(s)`,]
 ```
+
+## Comparasion and error
+The differences between the calculation by MSnBase and by PNNL:
+```{r}
+zoomData$`scan number(s)`
+from.msnbase  <- exprs(qnt)[row.names(zoomData),]
+from.pnnl     <- msexp.sp[msexp.sp$ScanNumber==zoomData$`scan number(s)`,c("Ion_114", "Ion_115","Ion_116", "Ion_117")]
+show(from.msnbase)
+show(from.pnnl)
+calc.error    <- from.msnbase - from.pnnl
+calc.error
+```
+
+Repeating the same process for all of peptides with e-value < 50
+
+```{r}
+# Original data
+dim(qnt.id)         # From MSXML File e-value < 50
+dim(msexp.sp)       # From PNNL (all)
+qnt.merged <- merge(qnt.id, msexp.sp, by.x = "scan number(s)", by.y = "ScanNumber", all.x = T, all.y = F)
+dim(qnt.merged)     # Merged Data (left Join)
+head(qnt.merged[,c(cols.sp, cols.p3)])
+```
+
+The error/differences (results from MsnBase - results from PNNL):
+```{r}
+q.Error <- qnt.merged[,c("scan number(s)", "pepseq", "ms-gf:evalue")]
+q.Error <- cbind(q.Error, "errIon114"= qnt.merged$iTRAQ4.114 - qnt.merged$Ion_114, "errIon115"=qnt.merged$iTRAQ4.115 - qnt.merged$Ion_115, "errIon116"=qnt.merged$iTRAQ4.116 - qnt.merged$Ion_116, "errIon117"=qnt.merged$iTRAQ4.117 - qnt.merged$Ion_117)
+
+head(q.Error[order(q.Error$`ms-gf:evalue`),])
+boxplot(q.Error[,c("errIon114","errIon115","errIon116","errIon117")])
+summary(q.Error[,c("errIon114","errIon115","errIon116","errIon117")])
+```
+# References

### 2016-05-04 itraquant/Benchmark/itraq-benchmark.R

@@ -8,9 +8,9 @@ library(stringr)
 library(dplyr)
 start.time = Sys.time()
 
-evalue_treshold = 75
+evalue_treshold = 50
 pNA = 0
-quant_method = trap
+quant_method = "max"
 combine_by = mean
 
 ####################################### READ FILE FROM PNNL ###################################################
@@ -44,6 +44,8 @@ msexp.sp.id       <- merge(msexp.sp, mzid.flat, by.x = "ScanNumber", by.y="scan 
 msexp.sp.filtered <- msexp.sp.id[!is.na(msexp.sp.id$accession),]
 msexp.sp.filtered <- msexp.sp.filtered[duplicated(msexp.sp.filtered$accession) & msexp.sp.filtered$`ms-gf:evalue` <evalue_treshold,]
 evalues           <- msexp.sp.filtered$`ms-gf:evalue`
+scan.no = head(mzid.flat[order(mzid.flat$`ms-gf:evalue`),])[1,"scan number(s)"]
+pep  = head(mzid.flat[order(mzid.flat$`ms-gf:evalue`),])[1,"pepseq"]
 ####################################### IDENTIFICATION & FILTERING ###################################################
 
 idSummary(msexp.id)
@@ -53,15 +55,14 @@ k[is.na(k)]       <- FALSE
 msexp.filter1     <- removeNoId(msexp.id, keep=k)
 msexp.filter2     <- removeMultipleAssignment(msexp.filter1)
 
-qnt               <- quantify(msexp.filter2, method="max", reporters=iTRAQ4, strict=F, verbose=F)
+qnt               <- quantify(msexp.filter1, method=quant_method, reporters=iTRAQ4, strict=T, verbose=T)
 
 qnt.id            <- merge(exprs(qnt),fData(qnt), by="row.names")
 
-cols.sp <- c(cols, "Ion_114", "Ion_115", "Ion_116", "Ion_117")
-cols.p3 <- c(cols, "iTRAQ4.114", "iTRAQ4.115", "iTRAQ4.116", "iTRAQ4.117")
+cols.sp <- c("Ion_114", "Ion_115", "Ion_116", "Ion_117")
+cols.p3 <- c("iTRAQ4.114", "iTRAQ4.115", "iTRAQ4.116", "iTRAQ4.117")
 
[…]

### 2016-05-04 itraquant/Benchmark/itraq-benchmark.Rmd
benchmark results

@@
 
-Using the `quantify` function from MSnBase, with parameters `mehod=max, verbose=FALSE, strict=FALSE`, resulting:
+Using the `quantify` function from MSnBase, with parameters `method=``r quant_method`, `verbose=FALSE, strict=FALSE`, resulting:
 
@@
 
-Repeating the same process for all of peptides with e-value < 50
+Repeating the same process for all of peptides with e-value < `r evalue_treshold`.
 

### 2016-05-15 itraquant/Benchmark/itraq-benchmark.R
revised benchmark

@@ -8,7 +8,7 @@ library(stringr)
 library(dplyr)
 start.time = Sys.time()
 
-evalue_treshold = 50
+evalue_treshold = 1e-10
 pNA = 0
 quant_method = "max"
 combine_by = mean
@@ -50,14 +50,15 @@ pep  = head(mzid.flat[order(mzid.flat$`ms-gf:evalue`),])[1,"pepseq"]
 
 idSummary(msexp.id)
 print("Filtering...")
-k                 <- (fData(msexp.id)$'ms-gf:evalue'< evalue_treshold)
+k                 <- ((fData(msexp.id)$'ms-gf:evalue')< evalue_treshold)
 k[is.na(k)]       <- FALSE
 msexp.filter1     <- removeNoId(msexp.id, keep=k)
 msexp.filter2     <- removeMultipleAssignment(msexp.filter1)
 
 qnt               <- quantify(msexp.filter1, method=quant_method, reporters=iTRAQ4, strict=T, verbose=T)
+qnt.f             <- filterNA(qnt, pNA = pNA)
 
-qnt.id            <- merge(exprs(qnt),fData(qnt), by="row.names")
+qnt.id           <- merge(exprs(qnt.f),fData(qnt.f), by="row.names")
 
 cols.sp <- c("Ion_114", "Ion_115", "Ion_116", "Ion_117")
 cols.p3 <- c("iTRAQ4.114", "iTRAQ4.115", "iTRAQ4.116", "iTRAQ4.117")

### 2016-05-15 _archieve_/itraquant/MANUAL/iTRAQ4_Quantification.Rmd
reorganize

--- 2016-04-11 itraquant/MANUAL/iTRAQ4_Quantification.Rmd
@@
 length(msexp.id)
+print(evalue_treshold)
 k                 <- (fData(msexp.id)$'ms-gf:evalue'< evalue_treshold)
 k[is.na(k)]       <- FALSE
+print(sum(k)) # Number of kept features
 msexp.filter1     <- removeNoId(msexp.id, keep=k)
+# Subsquent evalue filter
 length(msexp.filter1)
 msexp.filter2     <- removeMultipleAssignment(msexp.filter1)
+# Subsquent multiple assigment filter
 length(msexp.filter2)
@@
 head(exprs(qnt))
+print(pNA)
 qnt.filtered      <- filterNA(qnt, pNA = pNA)
@@
 ```{r}
-length(exprs(qnt))
-result  <- combineFeatures(qnt, groupBy = fData(qnt)$accession, fun=combine_by)
+length(exprs(qnt.filtered))
+result  <- combineFeatures(qnt.filtered, groupBy = fData(qnt.filtered)$accession, fun=combine_by)
 length(exprs(result))

### 2016-05-15 _archieve_/scquant/MANUAL/SpectrumCount_Quantification.Rmd
reorganize

--- 2016-04-11 scquant/MANUAL/squant-SOP.Rmd
@@
 output: pdf_document
-bibliography: ref.bib
-csl: biomed-central.csl
+bibliography: ../../media/ref.bib
+csl: ../../media/biomed-central.csl
 header-includes:
@@
   \setlength\headheight{28pt}
-  \rhead{\includegraphics[width = .2\textwidth]{pnnllogo.png}}
+  \rhead{\includegraphics[width = .2\textwidth]{../../media/pnnllogo.png}}
   \fancyfoot[LE,RO]{kristiyanto/p3:scquant}
@@
 This document discuss the ```kristiyanto/p3:scquant``` container, a spectrum count quantification pipeline for label-free mass spectrometry protein quantification.
-The pipeline is based on MSnID pipeline [@msnid].
+The pipeline is based on MSnID pipeline [@msnid, @MSnID31].
 
@@
 Filtering is done by using the parameter defined in the ```p3.config``` file.
-The filtering is including the error calculation (`variable: error_treshold`), scoring (`variable: score_treshold`), and filter optimization (`variable: iteration and fdr`).
+The filtering is including the error calculation (`variable: error_treshold`), scoring (`variable: score_treshold`), and filter optimization (`variable: iteration and fdr`) [@deutsch2010mass, @MSnID31].
 ```{r}

### 2016-05-15 Benchmark/iTRAQ4-Benchmark/itraq-benchmark.Rmd
benchmark

--- 2016-05-04 itraquant/Benchmark/itraq-benchmark.Rmd
@@
 
+Some peptides do not have complete (all ions) quantified. Only peptides with complete ions measurements are retained. 
+```{r}
+## Before filtered
+dim(exprs(qnt))
+summary(exprs(qnt))
+## After filtered
+dim(exprs(qnt.f))
+summary(exprs(qnt.f))
+```
+
 Repeating the same process for all of peptides with e-value < `r evalue_treshold`.
@@
 # Original data
-dim(qnt.id)         # From MSXML File e-value < 50
+dim(qnt.id)         # From MSXML File < e-value treshold
 dim(msexp.sp)       # From PNNL (all)
@@
 
-The error/differences (results from MsnBase - results from PNNL):
+The error/differences (results from MsnBase - results from PNNL) / results from PNNL:
+
 ```{r}
 q.Error <- qnt.merged[,c("scan number(s)", "pepseq", "ms-gf:evalue")]
-q.Error <- cbind(q.Error, "errIon114"= qnt.merged$iTRAQ4.114 - qnt.merged$Ion_114, "errIon115"=qnt.merged$iTRAQ4.115 - qnt.merged$Ion_115, "errIon116"=qnt.merged$iTRAQ4.116 - qnt.merged$Ion_116, "errIon117"=qnt.merged$iTRAQ4.117 - qnt.merged$Ion_117)
+q.Error <- cbind(q.Error, "errIon114"= abs(qnt.merged$iTRAQ4.114 - qnt.merged$Ion_114)/qnt.merged$Ion_114, "errIon115"=abs(qnt.merged$iTRAQ4.115 - qnt.merged$Ion_115)/qnt.merged$Ion_115, "errIon116"=abs(qnt.merged$iTRAQ4.116 - qnt.merged$Ion_116)/qnt.merged$Ion_116, "errIon117"=abs(qnt.merged$iTRAQ4.117 - qnt.merged$Ion_117)/qnt.merged$Ion_117)
+#q.Error <- cbind(q.Error, "errIon114"= apply(qnt.merged[,c("iTRAQ4.114","Ion_114") ],2,relError), "errIon115"=apply(qnt.merged[,c("iTRAQ4.115","Ion_115") ],2,relError), "errIon116"=apply(qnt.merged[,c("iTRAQ4.116","Ion_116") ],2,relError), "errIon117"=apply(qnt.merged[,c("iTRAQ4.117","Ion_117") ],2,relError))
 
 head(q.Error[order(q.Error$`ms-gf:evalue`),])
-boxplot(q.Error[,c("errIon114","errIon115","errIon116","errIon117")])
-summary(q.Error[,c("errIon114","errIon115","errIon116","errIon117")])
+boxplot(log10(q.Error[,c("errIon114","errIon115","errIon116","errIon117")]), main="Error (log10) scale.")
+## Error (Real Values)
+summary(log10(q.Error[,c("errIon114","errIon115","errIon116","errIon117")]))
 ```

### 2016-05-15 Benchmark/Spectrum-Count-Benchmark/Celegans-Aging.R

@@ -1,0 +1,118 @@
+# Derrived from PNNL-Comp-Mass-Spec/celegans.aging
+
+
+setwd("~/Documents/GITHUB/P3/scquant/Benchmark/")
+
+
+################################# ORIGINAL SCRIPT ######################################################
+library("rpx")
+id <- "PXD002161"
+px <- PXDataset(id)
+try(setInternet2(FALSE),silent=TRUE)
+library("jsonlite")
+addr <- "http://www.ebi.ac.uk:80/pride/ws/archive/%s/list/project/%s"
+files <- fromJSON(sprintf(addr, "file", id))$list
+assays <- fromJSON(sprintf(addr, "assay", id))$list
+files <- subset(files, grepl('mzid.gz', fileName),
+                select=c("assayAccession","fileName"))
+rownames(files) <- NULL
+assays <- assays[,c("assayAccession",
+                    "experimentalFactor",
+                    "proteinCount",
+                    "peptideCount",
+                    "uniquePeptideCount",
+                    "identifiedSpectrumCount",
+                    "totalSpectrumCount")]
+pttrn <- "Diet; fully fed, Mut: glp-4(bn2ts) daf-16(mgDf50); daf-2(e1370)"
+assays <- subset(assays, grepl(pttrn, experimentalFactor, fixed=T))
+assays <- with(assays, {data.frame(assayAccession,
+                                   phenotype=sub("Age:\\s([^,]*).*", "\\1",
+                                                 experimentalFactor),
+                                   sampleName=sub(".*Name:\\s(\\w)-ctrl-FF.(\\d)", "\\1.\\2",
+                                                  experimentalFactor),
+                                   stringsAsFactors=F)})
+files <- subset(files, assayAccession %in% assays$assayAccession)
+pxget(px, files$fileName) # fetch them from PRIDE
+files$datasetName <- sub('_msgfplus.mzid.gz','',files$fileName, fixed=T)
+meta <- merge(files[,c("assayAccession","datasetName")], assays)
+rownames(meta) <- meta$datasetName
+meta <- meta[order(meta$sampleName),]
+rownames(meta) <- NULL
+
+
+library("MSnID")
+prj <- MSnID()
+prj <- read_mzIDs(object = prj, mzids = files$fileName)
+prj <- assess_termini(prj)
[…]

### 2016-05-16 entry.py
bug fix, benchmark, biocparallel

@@ -46,7 +46,8 @@ def main():
 	unzip_files()
 
 	# Re-List the files
-	sp_files_ext = (".mzml",".mgf",".mzxml",".ms2",".pkl", ".mzXML")
+	sp_files_ext = (".mzXML", ".mzML", ".MZXML", ".mzml", ".MZML", ".mzml", ".mgf",".mzxml",".ms2",".pkl")
+
 	spectrum = scan_files(sp_files_ext)
 	
 	if (len(spectrum)!=0):
@@ -151,7 +152,7 @@ def msgf(spectrum, fasta, options, *opt):
 
 def itraq(mzid, options):
 	ext_set = (".mzXML", ".mzML", ".MZXML", ".mzml", ".MZML", ".mzml")
-	opts_set = ("EVALUE_TRESHOLD", "pNA", "QUANTIFICATION_METHOD")
+	opts_set = ("EVALUE_TRESHOLD", "pNA", "QUANTIFICATION_METHOD", "COMBINE_BY")
 	sp_files = scan_files(ext_set)
 	lock = mzid[:-5] + ".rda.tmp"
 	out = mzid[:-5]+".rda"
@@ -187,7 +188,8 @@ def itraq_folding(options):
 	try: c_by = options.get("ITRAQ4","COMBINE_BY").lower()
 	except: c_by = mean
 	finally:
-		cmd = ['Rscript', "fold.R", c_by]
+		print("")
+		#cmd = ['Rscript', "/root/fold.R", c_by]
 
 def get_pride(prideID):
 	cmd = ['Rscript', "/root/pride.R", prideID]
@@ -195,7 +197,7 @@ def get_pride(prideID):
 
 	
 def get_itraq_opts(options):
-	R_OPTS = dict(EVALUE_TRESHOLD= 1, pNA= 0, QUANTIFICATION_METHOD="count")
+	R_OPTS = dict(EVALUE_TRESHOLD= 1, pNA= 0, QUANTIFICATION_METHOD="sum", COMBINE_BY="mean")
 	for k,v in R_OPTS.items():
 		try:
 			x = options.get("ITRAQ4", k)
@@ -390,11 +392,12 @@ def write_blank_p3(config_file):
 	# Ignored if QUANTIFICATION METHOD is not ITRAQ4
 	# If left blank will be replaced with default
 	# Please check documentation for more detail
-	EVALUE_TRESHOLD = 75
[…]

### 2016-05-16 install.R

@@ -1,6 +1,7 @@
 source("https://bioconductor.org/biocLite.R")
 install.packages("RCurl")
 install.packages("XML")
+install.packages("stringr")
 biocLite("rpx")
 biocLite("mzID")
 biocLite("MSnID")

### 2016-05-16 itraq.R

@@ -1,25 +1,29 @@
 ## Labelled (iTRAQ4) Mass Spectometry Protein Quantification
 ## Docker Package: p3
 ## Daniel Kristiyanto (daniel.kristiyanto@pnnl.gov)
-
-library(MSnbase)
 library(mzID)
+library(MSnbase)
 library(stringr)
+library(BiocParallel)
+
+BiocParallel::register(BiocParallel::SnowParam(2))
+BiocParallel::register(BiocParallel::MulticoreParam(2))
 
 start.time = Sys.time()
 args = commandArgs(trailingOnly=TRUE)
 
 print(args)
 
-if (length(args)!=6) {
-  stop("Arguments ", call.=FALSE)
+if (length(args)!=7) {
+  stop("Arguments.", call.=FALSE)
 } else {
   mzml.files 		= args[1]
   mzid.files 		= args[2]
   evalue_treshold  	= as.double(args[3])
-  pNA 				= as.numeric(args[4])
-  quant_method		= args[5]
-  out_file 			= args[6]
+  pNA 				  = as.numeric(args[4])
+  quant_method	= args[5]
+  combine_by    = args[6]
+  out_file 			= args[7]
 }
 
 print("=======================================")
@@ -30,7 +34,7 @@ print("=======================================")
 print(paste("evalue_treshold:", evalue_treshold))
 print(paste("pNA:", pNA))
 print(paste("quant_method:", quant_method))
-
+print(paste("features combined using:", combine_by))
 
 setwd("/root/data")
 
@@ -71,17 +75,17 @@ rm(msexp.filter2)
 rm(qnt)
 gc(verbose = FALSE)
 save(qnt.filtered, file=out_file)
-#result            <- combineFeatures(qnt.filtered, groupBy = fData(qnt.filtered)$accession, fun=combine_by)
+result            <- combineFeatures(qnt.filtered, groupBy = fData(qnt.filtered)$accession, fun=combine_by)
 
 #head(exprs(result))
 ####################################### OUTPUT ###################################################
 print("Writing the output...")
 #evalue.table	  <- as.data.frame(merge(fData(qnt.filtered)[,c("accession","spectrum", "pepseq", "idFile", "ms-gf:evalue")], exprs(result), by.x ="accession", by.y ="row.names" ))
-#quantified		  <- as.data.frame(cbind(Accession_ID=row.names(result),exprs(result)))
[…]

### 2016-05-16 itraqfolding.R

@@ -7,21 +7,18 @@ library(MSnbase)
 
 
 setwd("/root/data")
-msnset.files        <- list.files(path = ".", pattern ="rda", all.files = F, 
+msnset.files        <- list.files(path = ".", pattern =".rda", all.files = F, 
                       full.names = F, recursive = F, ignore.case = T, include.dirs = F)
 
 for (i in 1:length(msnset.files))
 {
     load(msnset.files[i])
-    curr <- paste0(substr(msnset.files[i],1,4), i)
-    #sampleNames(qnt.filtered) <- curr
-    #qnt.filtered < updateFvarLabels(qnt.filtered, curr)
-    dim(qnt.filtered)
     if (i == 1 )
     {
       msn.set <- qnt.filtered
       qnt.filtered <- NULL
     } else {
+      qnt.filtered <- updateFeatureNames(qnt.filtered)
       msn.set <- combine(msn.set, qnt.filtered)
       qnt.filtered <- NULL
     }

### 2016-05-16 swarm/local/build-local-swarm.sh

@@ -22,7 +22,7 @@ do
 done	
 
 # List of exsisting swarm
-docker run swarm list token://$sid
+docker run --rm swarm list token://$sid
 # Get into the swarm environtment
 eval `docker-machine env --swarm swarm-master`
 docker ps

### 2016-05-19 entry.py
Script update

@@ -63,12 +63,7 @@ def main():
 	# Run MSGF 
 	if fasta and spectrum and RUN_MSGF:
 		print("Running MSGF") 
-
-		try:
-			msgf_opts = options.get("MSGF", "MSGF_OPTIONS").upper()
-			if (len_msgf_opts !=0): msgf(spectrum, fasta, options, msgf_opts)
-		except:
-			msgf(spectrum, fasta, options)
+		msgf(spectrum, fasta, options)
 	else:
 		print("Skipping MSGF identification...")
 
@@ -78,45 +73,47 @@ def main():
 	except:
 		pass
 
-	if Q_METHOD == "SPECTRUM_COUNT":
-		keep_waiting = True
-		wait = 0
-		lock = "SC_RESULT.txt.tmp"
-		if os.path.isfile(lock): sys.exit("Spectrum Count Quantification is already run by other container. Quitting.")
-		while keep_waiting:
-			mzid_set = scan_files((".mzid"))
-			if len(mzid_set) == 0:
-				sys.exit("No .mzid file found")
-			elif len(scan_files('.mzid.tmp')) != 0: 
-				#print("SCAN MZID TMP:" + scan_files('.mzid.tmp'))
-				print("MSGF identification is being run by other containers. Waiting...")
-				if wait > maxwait:
-					keep_waiting = False
-					sys.exit("Had waited for {}s. Quitting now. \n Perhaps remove .tmp files and rerun containers?".format(maxwait))
-				else: wait = wait + 5 
-				time.sleep(5)
-			else:
-				touch(lock)
-				scquant(mzid_set, options)
-				os.remove(lock)
-				keep_waiting = False
+	# if Q_METHOD == "SPECTRUM_COUNT":
+	# 	keep_waiting = True
+	# 	wait = 0
+	# 	lock = "SC_RESULT.txt.tmp"
+	# 	if os.path.isfile(lock): sys.exit("Spectrum Count Quantification is already run by other container. Quitting.")
+	# 	while keep_waiting:
+	# 		mzid_set = scan_files((".mzid"))
+	# 		if len(mzid_set) == 0:
+	# 			sys.exit("No .mzid file found")
+	# 		elif len(scan_files('.mzid.tmp')) != 0: 
+	# 			#print("SCAN MZID TMP:" + scan_files('.mzid.tmp'))
[…]

### 2016-05-19 itraq.R

@@ -1,10 +1,10 @@
 ## Labelled (iTRAQ4) Mass Spectometry Protein Quantification
 ## Docker Package: p3
 ## Daniel Kristiyanto (daniel.kristiyanto@pnnl.gov)
-library(mzID)
-library(MSnbase)
-library(stringr)
-library(BiocParallel)
+suppressMessages(library(mzID))
+suppressMessages(library(MSnbase))
+suppressMessages(library(stringr))
+suppressMessages(library(BiocParallel))
 
 BiocParallel::register(BiocParallel::SnowParam(2))
 BiocParallel::register(BiocParallel::MulticoreParam(2))
@@ -12,82 +12,96 @@ BiocParallel::register(BiocParallel::MulticoreParam(2))
 start.time = Sys.time()
 args = commandArgs(trailingOnly=TRUE)
 
-print(args)
-
 if (length(args)!=7) {
   stop("Arguments.", call.=FALSE)
 } else {
   mzml.files 		= args[1]
   mzid.files 		= args[2]
-  evalue_treshold  	= as.double(args[3])
+  specvalue_threshold  	= as.double(args[3])
   pNA 				  = as.numeric(args[4])
   quant_method	= args[5]
   combine_by    = args[6]
   out_file 			= args[7]
 }
 
-print("=======================================")
-print(" iTRAQ4 Quantification")
-print("=======================================")
 
-
-print(paste("evalue_treshold:", evalue_treshold))
-print(paste("pNA:", pNA))
-print(paste("quant_method:", quant_method))
-print(paste("features combined using:", combine_by))
+print("=======================================")
+print(" Quantification")
+if(quant_method=="count")
+{
+  print("Spectrum Count Quantification")
+  print(paste("Spec Value Threshold:", specvalue_threshold))
+  print(paste("features combined using:", combine_by))
+}else{
+  print("iTRAQ4 Quantification")
+  
+  print(paste("Spec Value Threshold:", specvalue_threshold))
+  print(paste("pNA:", pNA))
+  print(paste("quant_method:", quant_method))
+  print(paste("features combined using:", combine_by))
+}
+print("=======================================")
 
 setwd("/root/data")
 
 ####################################### READ FILE ###################################################
-print("Isobaric Tagging Quantification")
[…]

### 2016-05-19 Benchmark/Benchmark/itraq-benchmark.Rmd
benchmark

---
title: | 
  | Portable Proteomics Pipeline (P3) Benchmark
author: "Daniel Kristiyanto (daniel.kristiyanto@pnnl.gov)"
date: \today
fontsize: 11pt
output: pdf_document
# bibliography: ../../media/ref.bib
nocite: |
  @domon2006mass, @deutsch2010mass, @MSnba83
csl: ../../media/biomed-central.csl
header-includes:
  \usepackage{fancyhdr}
  \usepackage{graphicx}
  \usepackage{hyperref}
  \pagestyle{fancy}
  \setlength\headheight{28pt}
  \rhead{\includegraphics[width = .2\textwidth]{../../media/pnnllogo.png}}
  \fancyfoot[LE,RO]{kristiyanto/p3:benchmark}
---
\rule{\textwidth}{1pt}

```{r, warning=FALSE, echo=FALSE, include=FALSE, cache=T}
setwd("~/Dropbox/_SPACE/Benchmark/")
file_mzid        <- list.files(path = ".", pattern ="mzid", all.files = F, 
                      full.names = F, recursive = F, ignore.case = T, include.dirs = F)
file_mzml        <- list.files(path = ".", pattern ="mzML$|mzXML$", all.files = F, 
                      full.names = F, recursive = F, ignore.case = T, include.dirs = F)
file_fasta        <- list.files(path = ".", pattern ="fasta", all.files = F, 
                      full.names = F, recursive = F, ignore.case = T, include.dirs = F)

library(MSnbase)
library(mzID)
suppressMessages(library(BiocParallel))

mzid_pnnl <- read.table(file="TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11_msgfdb_fht.txt", sep="\t", header=T)
mzids_no_switch   <- mzID("TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11_no_switch.mzid")
mzid_p3           <- mzID("TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11.mzid")
msexp.raw         <- readMSData(file_mzml)
msexp_p3          <- addIdentificationData(msexp.raw, id = mzid_p3,verbose=F)
msexp_no_switch   <- addIdentificationData(msexp.raw, id = mzids_no_switch,verbose=F)

p3_table <- fData(msexp_p3)
ns_table <- fData(msexp_no_switch)
```

1. Files:

```{r, echo=F}
show(file_mzml)
show(file_fasta)
```

2. Identification:

`MSGFPlus.jar` was downloaded from \url{https://omics.pnl.gov/software/ms-gf}. Identification was run multiple times, using different computers (Linux, MacOS, within or without Docker), and resulted the same results.

Identification with different switches resulted different results.

```
# Command Line (Without Switch)
java -Xmx8000M -jar P3/MSGFPlus.jar -s \
TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11.mzML -o \
TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11_no_switch.mzid \
-d ID_003632_9011437E.fasta

# Command Line (2)
java -Xmx8000M -jar P3/MSGFPlus.jar -s \
TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11.mzML -o \
TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11.mzid \
-d ID_003632_9011437E.fasta  \
-t 10ppm -m 0 -inst 1 -e 1 -ti -1,2 -ntt 2 -tda 1 -minLength 6 \
-maxLength 50 -minCharge 2 -maxCharge 5 -n 1 -thread 7 \
-mod MSGFDB_Mods.txt -minNumPeaks 5 -addFeatures 1
```
```{r, echo=F}
# Identification Result
show(file_mzid)
```

3. Result from PNNL
```{r, echo=F}
head(mzid_pnnl)[1:2,c("ResultID", "Scan", "Peptide", "Protein", "MSGFDB_SpecEValue")]
```
4. Result from MSGF+ without any switches (sorted by SpecEValue)

```{r, echo=F}
tmp           <- ns_table
tmp           <- tmp[order(tmp$'ms-gf:specevalue'),]
show(head(tmp[,c("scan number(s)", "ms-gf:denovoscore", "ms-gf:specevalue", "accession", "pepseq")])[1:3,])

tmp[tmp$`scan number(s)`=="11612" &! is.na(tmp$`scan number(s)`),c("scan number(s)", "ms-gf:denovoscore", "ms-gf:specevalue", "accession", "pepseq")]
```

Reading the MZID file manually
```
java -Xmx2000M -XX:+UseConcMarkSweepGC -cp ../P3/MSGFPlus.jar edu.ucsd.msjava.ui.MzIDToTsv -i TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11_no_switch.mzid -showQValue 1 -showDecoy 1 -unroll 1
```
```{r, warning=FALSE, echo=FALSE, include=FALSE, cache=T}
setwd("~/Dropbox/_SPACE/Benchmark/")
tsv_ns <- read.table(file ="TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11_no_switch.tsv", sep="\t",header = T)

tsv <- read.table(file ="TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11.tsv", sep="\t",header = T)

```
```{r, echo=F}
head(tsv_ns)[1:3,c("ScanNum", "Peptide", "Protein", "SpecEValue")]
```

5. Result from with switches (2)
```{r, echo=F}
tmp           <- p3_table
tmp           <- tmp[order(tmp$'ms-gf:specevalue'),]
show(head(tmp[,c("scan number(s)", "ms-gf:denovoscore", "ms-gf:specevalue", "accession", "pepseq")])[1:3,])
tmp[tmp$`scan number(s)`=="11612" &! is.na(tmp$`scan number(s)`),c("scan number(s)", "ms-gf:denovoscore", "ms-gf:specevalue", "accession", "pepseq")]

```
Reading the MZID file manually
```{r, echo=}
head(tsv)[1:3,c("ScanNum", "Peptide", "Protein", "SpecEValue")]
```

### 2016-05-19 Benchmark/Benchmark/itraq-benchmark.R

@@ -1,0 +1,69 @@
+## Labelled (iTRAQ4) Mass Spectometry Protein Quantification
+## Benchmark for iTRAQ4 
+## Daniel Kristiyanto (daniel.kristiyanto@pnnl.gov)
+
+library(MSnbase)
+library(mzID)
+library(stringr)
+library(dplyr)
+start.time = Sys.time()
+
+evalue_treshold = 1e-10
+pNA = 0
+quant_method = "max"
+combine_by = mean
+
+####################################### READ FILE FROM PNNL ###################################################
+
+setwd("~/Documents/GITHUB/P3/itraquant/Benchmark/itraq-benchmark/PNNL")
+mzml.sp        <- list.files(path = ".", pattern ="txt", all.files = F, 
+                             full.names = F, recursive = F, ignore.case = T, include.dirs = F)[1]
+
+msexp.sp <- read.table(mzml.sp, sep="\t", header = T)
+
+
+####################################### READ FILE ###################################################
+print("Isobaric Tagging Quantification")
+setwd("~/Documents/GITHUB/P3/itraquant/Benchmark/itraq-benchmark/")
+
+mzid.files        <- list.files(path = ".", pattern ="mzid", all.files = F, 
+                                full.names = F, recursive = F, ignore.case = T, include.dirs = F)[1]
+mzml.files        <- list.files(path = ".", pattern ="mzML$|mzXML$", all.files = F, 
+                                full.names = F, recursive = F, ignore.case = T, include.dirs = F)[1]
+
+mzids.raw         <- mzID(mzid.files)
+msexp.raw         <- readMSData(mzml.files)
+mzid.flat         <- flatten(mzids.raw)
+
+
+####################################### IDENTIFICATION & FILTERING ###################################################
+print("Identifiying...")
+msexp.id          <- addIdentificationData(msexp.raw, id = mzids.raw)
+msexp.sp.id       <- merge(msexp.sp, mzid.flat, by.x = "ScanNumber", by.y="scan number(s)", all=T)
+
+msexp.sp.filtered <- msexp.sp.id[!is.na(msexp.sp.id$accession),]
[…]

### 2016-05-19 Benchmark/MSGF-Benchmark/itraq-benchmark.Rmd
MSGF Benchmark

--- 2016-05-19 Benchmark/Benchmark/itraq-benchmark.Rmd
@@
   | Portable Proteomics Pipeline (P3) Benchmark
+  | MSGF Benchmark
 author: "Daniel Kristiyanto (daniel.kristiyanto@pnnl.gov)"
@@
 
-1. Files:
+# 1. Files:
 
@@
 
-2. Identification:
+# 2. Identification:
 
@@
 
-3. Result from PNNL
+#3. Result from PNNL
 ```{r, echo=F}
@@
 ```
-4. Result from MSGF+ without any switches (sorted by SpecEValue)
 
+#4. Result from MSGF+ without any switches (sorted by SpecEValue)
 ```{r, echo=F}
@@
 
-5. Result from with switches (2)
+# 5. Results with switches
 ```{r, echo=F}
@@
 ```
+
 Reading the MZID file manually
-```{r, echo=}
+```{r, echo=F}
 head(tsv)[1:3,c("ScanNum", "Peptide", "Protein", "SpecEValue")]

### 2016-05-19 Benchmark/MSGF-Benchmark/msgf-benchmark.Rmd
benchmark

--- 2016-05-19 Benchmark/MSGF-Benchmark/itraq-benchmark.Rmd
@@
 title: | 
-  | Portable Proteomics Pipeline (P3) Benchmark
+  | Portable Proteomics Pipeline (P3) 
   | MSGF Benchmark
@@
 
-`MSGFPlus.jar` was downloaded from \url{https://omics.pnl.gov/software/ms-gf}.
-Identification was run multiple times, using different computers (Linux, MacOS, within or without Docker), and resulted the same results.
+`MSGFPlus.jar` was downloaded from \url{https://omics.pnl.gov/software/ms-gf}. Identification was run multiple times (within or without Docker), and resulted the same results.
 
@@
 show(head(tmp[,c("scan number(s)", "ms-gf:denovoscore", "ms-gf:specevalue", "accession", "pepseq")])[1:3,])
-
-tmp[tmp$`scan number(s)`=="11612" &! is.na(tmp$`scan number(s)`),c("scan number(s)", "ms-gf:denovoscore", "ms-gf:specevalue", "accession", "pepseq")]
+## Looking at Scan Number 11612 and 14441
+tmp[(tmp$`scan number(s)`=="11612" | tmp$`scan number(s)`=="14441")  &! is.na(tmp$`scan number(s)`),c("scan number(s)", "ms-gf:denovoscore", "ms-gf:specevalue", "accession", "pepseq")]
 ```
@@
 ```
-java -Xmx2000M -XX:+UseConcMarkSweepGC -cp ../P3/MSGFPlus.jar edu.ucsd.msjava.ui.MzIDToTsv -i TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11_no_switch.mzid -showQValue 1 -showDecoy 1 -unroll 1
+java -Xmx2000M -XX:+UseConcMarkSweepGC -cp \ 
+../P3/MSGFPlus.jar edu.ucsd.msjava.ui.MzIDToTsv -i \
+TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11_no_switch.mzid \
+-showQValue 1 -showDecoy 1 -unroll 1
 ```
@@
 show(head(tmp[,c("scan number(s)", "ms-gf:denovoscore", "ms-gf:specevalue", "accession", "pepseq")])[1:3,])
-tmp[tmp$`scan number(s)`=="11612" &! is.na(tmp$`scan number(s)`),c("scan number(s)", "ms-gf:denovoscore", "ms-gf:specevalue", "accession", "pepseq")]
+## Looking at Scan Number 11612 and 14441
+tmp[(tmp$`scan number(s)`=="11612" | tmp$`scan number(s)`=="14441") &! is.na(tmp$`scan number(s)`),c("scan number(s)", "ms-gf:denovoscore", "ms-gf:specevalue", "accession", "pepseq")]
 

### 2016-05-19 Benchmark/iTRAQ4-Benchmark/itraq-benchmark.Rmd
benchmark

--- 2016-05-04 itraquant/Benchmark/itraq-benchmark.Rmd
@@
   | Portable Proteomics Pipeline (P3) 
-  | Labelled (iTRAQ4) Benchmark
+  | MSGF Benchmark
+  | 
 author: "Daniel Kristiyanto (daniel.kristiyanto@pnnl.gov)"
@@
 output: pdf_document
-bibliography: ../../media/ref.bib
+# bibliography: ../../media/ref.bib
 nocite: |
@@
 
-```{r, warning=FALSE, echo=FALSE, include=FALSE}
-#setwd("~/Documents/GITHUB/P3/itraquant/Benchmark/itraq-benchmark/")
-load("~/Documents/GITHUB/P3/itraquant/Benchmark/itraq-benchmark/itraq-benchmark.RData")
+```{r, warning=FALSE, echo=FALSE, include=FALSE, cache=T}
+setwd("~/Dropbox/_SPACE/Benchmark/")
+file_mzid        <- list.files(path = ".", pattern ="mzid", all.files = F, 
+                      full.names = F, recursive = F, ignore.case = T, include.dirs = F)
+file_mzml        <- list.files(path = ".", pattern ="mzML$|mzXML$", all.files = F, 
+                      full.names = F, recursive = F, ignore.case = T, include.dirs = F)
+file_fasta        <- list.files(path = ".", pattern ="fasta", all.files = F, 
+                      full.names = F, recursive = F, ignore.case = T, include.dirs = F)
+
 library(MSnbase)
 library(mzID)
-cols <- c("accession", "pepseq", "ms-gf:evalue")
+suppressMessages(library(BiocParallel))
+
+mzid_pnnl <- read.table(file="TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11_msgfdb_fht.txt", sep="\t", header=T)
+mzids_no_switch   <- mzID("TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11_no_switch.mzid")
+mzid_p3           <- mzID("TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11.mzid")
+msexp.raw         <- readMSData(file_mzml)
+msexp_p3          <- addIdentificationData(msexp.raw, id = mzid_p3,verbose=F)
+msexp_no_switch   <- addIdentificationData(msexp.raw, id = mzids_no_switch,verbose=F)
+
+p3_table <- fData(msexp_p3)
+ns_table <- fData(msexp_no_switch)
 ```
 
-The purpose of this document is to benchmark the iTRAQ quantification on the Portable Proteomics Pipelines (P3) containers.
+# 1. Files:
 
-# Input
-1. `r mzid.files` : The identification file (product of MSGF+)
-2. `r mzml.files` : The mass spectometry dataset
-3. `r mzml.sp`    : The quantification results used to benchmark (calcullated by PNNL)
-
-# Methods
-## Identification
-```{r}
-## The identification file
-mzids.raw
-head(mzid.flat[order(mzid.flat[,"ms-gf:evalue"]),])[1:3,]
+```{r, echo=F}
+show(file_mzml)
+show(file_fasta)
 ```
 
-Based on this data, peptide `r pep` was listed as a good quality of identification with lowest e-value.
+# 2. Identification:
 
-## Spectrum Objects
-```{r}
-msexp.raw
+`MSGFPlus.jar` was downloaded from \url{https://omics.pnl.gov/software/ms-gf}.
+Identification was run multiple times, using different computers (Linux, MacOS, within or without Docker), and resulted the same results.
+
+Identification with different switches resulted different results.
+
 ```
-The spectrum data consists of 1606 percursor ions and with features ranged from X1.1 to x9999.1.
+# Command Line (Without Switch)
+java -Xmx8000M -jar P3/MSGFPlus.jar -s \
+TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11.mzML -o \
+TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11_no_switch.mzid \
+-d ID_003632_9011437E.fasta
 
-This data then paired with the identification file using `addIdentificationData` tool from MSnBase, resulting the table below:
-```{r}
-### The spectra objects enrinched with identification file
-msexp.id
-idSummary(msexp.id)
-#head(fData(msexp.id))[1:3,]
+# Command Line (2)
+java -Xmx8000M -jar P3/MSGFPlus.jar -s \
+TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11.mzML -o \
+TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11.mzid \
+-d ID_003632_9011437E.fasta  \
+-t 10ppm -m 0 -inst 1 -e 1 -ti -1,2 -ntt 2 -tda 1 -minLength 6 \
+-maxLength 50 -minCharge 2 -maxCharge 5 -n 1 -thread 7 \
+-mod MSGFDB_Mods.txt -minNumPeaks 5 -addFeatures 1
+```
+```{r, echo=F}
+# Identification Result
+show(file_mzid)
 ```
 
-Table focusing on the peptide `r pep`:
-```{r}
-zoomData <- fData(msexp.id)[fData(msexp.id)$pepseq==pep & !is.na(fData(msexp.id)$pepseq),]
-zoomData
+#3. Result from PNNL
+```{r, echo=F}
+head(mzid_pnnl)[1:2,c("ResultID", "Scan", "Peptide", "Protein", "MSGFDB_SpecEValue")]
 ```
 
-From this table, we know that this peptide was identified from features `r rownames(zoomData)`.
+#4. Result from MSGF+ without any switches (sorted by SpecEValue)
+```{r, echo=F}
+tmp           <- ns_table
+tmp           <- tmp[order(tmp$'ms-gf:specevalue'),]
+show(head(tmp[,c("scan number(s)", "ms-gf:denovoscore", "ms-gf:specevalue", "accession", "pepseq")])[1:3,])
 
-Using the `quantify` function from MSnBase, with parameters `mehod=max, verbose=FALSE, strict=FALSE`, resulting:
-
-```{r}
-## Features 
-zoomData[,cols]
-exprs(qnt)[row.names(exprs(qnt))==row.names(zoomData),]
-plot(msexp.id[["X15545.1"]],reporters=iTRAQ4, full=T)
+## Looking at Scan number 11612 and 14441
+tmp[(tmp$`scan number(s)`=="11612" | tmp$`scan number(s)`=="14441")  &! is.na(tmp$`scan number(s)`),c("scan number(s)", "ms-gf:denovoscore", "ms-gf:specevalue", "accession", "pepseq")]
 ```
 
-## Quantification
-This quantification then compared to the quantification data resulted from PNNL, by matching the scan number.
-```{r}
-zoomData$`scan number(s)`
-msexp.sp[msexp.sp$ScanNumber==zoomData$`scan number(s)`,]
+## Reading the MZID file manually
+```
+java -Xmx2000M -XX:+UseConcMarkSweepGC -cp ../P3/MSGFPlus.jar \ 
+edu.ucsd.msjava.ui.MzIDToTsv -i \
+TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11_no_switch.mzid \
+-showQValue 1 -showDecoy 1 -unroll 1
+```
+```{r, warning=FALSE, echo=FALSE, include=FALSE, cache=T}
+setwd("~/Dropbox/_SPACE/Benchmark/")
+tsv_ns <- read.table(file ="TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11_no_switch.tsv", sep="\t",header = T)
+
+tsv <- read.table(file ="TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11.tsv", sep="\t",header = T)
+
 ```
 
-## Comparasion and error
-The differences between the calculation by MSnBase and by PNNL:
-```{r}
-zoomData$`scan number(s)`
-from.msnbase  <- exprs(qnt)[row.names(zoomData),]
-from.pnnl     <- msexp.sp[msexp.sp$ScanNumber==zoomData$`scan number(s)`,c("Ion_114", "Ion_115","Ion_116", "Ion_117")]
-show(from.msnbase)
-show(from.pnnl)
-calc.error    <- from.msnbase - from.pnnl
-calc.error
+```{r, echo=F}
+head(tsv_ns)[1:3,c("ScanNum", "Peptide", "Protein", "SpecEValue")]
 ```
 
-Repeating the same process for all of peptides with e-value < 50
+# 5. Results with switches (2)
+```{r, echo=F}
+tmp           <- p3_table
+tmp           <- tmp[order(tmp$'ms-gf:specevalue'),]
+show(head(tmp[,c("scan number(s)", "ms-gf:denovoscore", "ms-gf:specevalue", "accession", "pepseq")])[1:3,])
 
-```{r}
-# Original data
-dim(qnt.id)         # From MSXML File e-value < 50
-dim(msexp.sp)       # From PNNL (all)
-qnt.merged <- merge(qnt.id, msexp.sp, by.x = "scan number(s)", by.y = "ScanNumber", all.x = T, all.y = F)
-dim(qnt.merged)     # Merged Data (left Join)
-head(qnt.merged[,c(cols.sp, cols.p3)])
+## Looking at Scan number 11612 and 14441
+tmp[(tmp$`scan number(s)`=="11612" | tmp$`scan number(s)`=="14441")  &! is.na(tmp$`scan number(s)`),c("scan number(s)", "ms-gf:denovoscore", "ms-gf:specevalue", "accession", "pepseq")]
 ```
 
-The error/differences (results from MsnBase - results from PNNL):
-```{r}
-q.Error <- qnt.merged[,c("scan number(s)", "pepseq", "ms-gf:evalue")]
-q.Error <- cbind(q.Error, "errIon114"= qnt.merged$iTRAQ4.114 - qnt.merged$Ion_114, "errIon115"=qnt.merged$iTRAQ4.115 - qnt.merged$Ion_115, "errIon116"=qnt.merged$iTRAQ4.116 - qnt.merged$Ion_116, "errIon117"=qnt.merged$iTRAQ4.117 - qnt.merged$Ion_117)
-
-head(q.Error[order(q.Error$`ms-gf:evalue`),])
-boxplot(q.Error[,c("errIon114","errIon115","errIon116","errIon117")])
-summary(q.Error[,c("errIon114","errIon115","errIon116","errIon117")])
+## Reading the MZID file manually
+```{r, echo=F}
+head(tsv)[1:3,c("ScanNum", "Peptide", "Protein", "SpecEValue")]
 ```
-# References

### 2016-05-19 Benchmark/MSGF-Benchmark/itraq-benchmark.R

@@ -1,69 +1,0 @@
-## Labelled (iTRAQ4) Mass Spectometry Protein Quantification
-## Benchmark for iTRAQ4 
-## Daniel Kristiyanto (daniel.kristiyanto@pnnl.gov)
-
-library(MSnbase)
-library(mzID)
-library(stringr)
-library(dplyr)
-start.time = Sys.time()
-
-evalue_treshold = 1e-10
-pNA = 0
-quant_method = "max"
-combine_by = mean
-
-####################################### READ FILE FROM PNNL ###################################################
-
-setwd("~/Documents/GITHUB/P3/itraquant/Benchmark/itraq-benchmark/PNNL")
-mzml.sp        <- list.files(path = ".", pattern ="txt", all.files = F, 
-                             full.names = F, recursive = F, ignore.case = T, include.dirs = F)[1]
-
-msexp.sp <- read.table(mzml.sp, sep="\t", header = T)
-
-
-####################################### READ FILE ###################################################
-print("Isobaric Tagging Quantification")
-setwd("~/Documents/GITHUB/P3/itraquant/Benchmark/itraq-benchmark/")
-
-mzid.files        <- list.files(path = ".", pattern ="mzid", all.files = F, 
-                                full.names = F, recursive = F, ignore.case = T, include.dirs = F)[1]
-mzml.files        <- list.files(path = ".", pattern ="mzML$|mzXML$", all.files = F, 
-                                full.names = F, recursive = F, ignore.case = T, include.dirs = F)[1]
-
-mzids.raw         <- mzID(mzid.files)
-msexp.raw         <- readMSData(mzml.files)
-mzid.flat         <- flatten(mzids.raw)
-
-
-####################################### IDENTIFICATION & FILTERING ###################################################
-print("Identifiying...")
-msexp.id          <- addIdentificationData(msexp.raw, id = mzids.raw)
-msexp.sp.id       <- merge(msexp.sp, mzid.flat, by.x = "ScanNumber", by.y="scan number(s)", all=T)
-
-msexp.sp.filtered <- msexp.sp.id[!is.na(msexp.sp.id$accession),]
[…]

### 2016-05-20 Benchmark/MSGF-Benchmark/msgf-benchmark.Rmd
Benchmark

@@
 \rule{\textwidth}{1pt}
+```{r, warning=FALSE, echo=FALSE, include=FALSE, cache=T}
+library(MSnbase)
+library(mzID)
+library(stringr)
+suppressMessages(library(BiocParallel))
+
+```
 
@@
 
-library(MSnbase)
-library(mzID)
-suppressMessages(library(BiocParallel))
-
 mzid_pnnl <- read.table(file="TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11_msgfdb_fht.txt", sep="\t", header=T)
@@
 mzid_p3           <- mzID("TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11.mzid")
+tsv_ns <- read.table(file ="TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11_no_switch.tsv", sep="\t",header = T)
+tsv <- read.table(file ="TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11.tsv", sep="\t",header = T)
+
 msexp.raw         <- readMSData(file_mzml)
@@
 
+```{r, echo = F, include=F}
+library(mzID)
+evalue = 1e-10
+pnnl <- mzid_pnnl[, c("Scan", "MSGFDB_SpecEValue", "Peptide", "Protein")]
+p3_flt <- flatten(mzid_p3)
+bigmzid <- merge(pnnl, p3_table[, c("scan number(s)", "ms-gf:specevalue", "pepseq", "accession")], by.x="Scan", by.y = "scan number(s)", all.x = T)
+```
+
 #3. Result from PNNL
 ```{r, echo=F}
-head(mzid_pnnl)[1:2,c("ResultID", "Scan", "Peptide", "Protein", "MSGFDB_SpecEValue")]
+# Nrow
+nrow(pnnl)
+head(pnnl,2)
+tail(pnnl,2)
 ```
@@
 ```
-```{r, warning=FALSE, echo=FALSE, include=FALSE, cache=T}
-setwd("~/Dropbox/_SPACE/Benchmark/")
-tsv_ns <- read.table(file ="TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11_no_switch.tsv", sep="\t",header = T)
 
-tsv <- read.table(file ="TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11.tsv", sep="\t",header = T)
-
-```
 ```{r, echo=F}
@@
 ```
+
+# 6. Filtering
+```{r, include=F}
+pnnl$Peptide <- substr(as.character(pnnl$Peptide),1,nchar(as.character(pnnl$Peptide))-2)
+pnnl$Peptide <- substr(as.character(pnnl$Peptide),3,nchar(as.character(pnnl$Peptide)))
+```
+
+# a Spec-Evalue `r evalue`
+### From PNNL
+```{r, echo =F}
+pnnl_tmp <- pnnl[pnnl$MSGFDB_SpecEValue<evalue,]
+print("==Head==")
+head(pnnl_tmp,2)
+print("==Tail==")
+tail(pnnl_tmp,2)
+```
+There are ```r nrow(pnnl_tmp)``` rows remained.
+
+### From Docker 
+```{r echo=F}
+tmp <- (p3_table[p3_table$'ms-gf:specevalue'<evalue & !is.na(p3_table$'ms-gf:specevalue'<evalue),c("scan number(s)", "ms-gf:specevalue", "pepseq", "accession")])
+tmp <- tmp[order(tmp$`ms-gf:specevalue`),]
+print("==Head==")
+head(tmp,2)
+print("==Tail==")
+tail(tmp,2)
+
+bt_tmp <- merge(x =  tmp, y=pnnl, by.y = "Scan", by.x  =  "scan number(s)", all.x = T)
+bt_tmp <- bt_tmp[order(bt_tmp$`ms-gf:specevalue`, decreasing = F),]
+```
+There are ```r nrow(tmp)``` rows remained.
+
+### Differences
+Data from Docker is matched with from PNNL using scan number as ID.
+`r names(bt_tmp)[2:4]` are values from Docker, `r names(bt_tmp)[5:7]` are the corresponding values from PNNL.
+There are `r nrow(bt_tmp)` of rows in total with  `r sum(is.na(bt_tmp$MSGFDB_SpecEValue))` of NULL/unmapped values.
+
+```{r, echo=F}
+tmp_nona <- tmp[!is.na(tmp),]
+```
+
+Aside from the `r sum(is.na(bt_tmp$MSGFDB_SpecEValue))` unmatched values, `r sum(tmp_nona$'ms-gf:specevalue'!=tmp_nona$MSGFDB_SpecEValue)` unmacthed spec-evalue, `r sum(tmp_nona$pepseq!=tmp_nona$Peptide)` of unmatched peptide identification.
+
+```{r echo=F}
+print("==Head==")
+head(bt_tmp,2)
+print("==Unmatched==")
+head(bt_tmp[is.na(bt_tmp$MSGFDB_SpecEValue),],3)
+print("==Tail==")
+tail(bt_tmp,2)
+```
+
+```{r include=F}
+evalue = 1e-15
+```
+
+# b. Spec-Evalue `r evalue`
+### From PNNL
+```{r, echo =F}
+pnnl_tmp <- pnnl[pnnl$MSGFDB_SpecEValue<evalue,]
+print("==Head==")
+head(pnnl_tmp,2)
+print("==Tail==")
+tail(pnnl_tmp,2)
+```
+There are ```r nrow(pnnl_tmp)``` rows remained.
+
+### From Docker 
+```{r echo=F}
+tmp <- (p3_table[p3_table$'ms-gf:specevalue'<evalue & !is.na(p3_table$'ms-gf:specevalue'<evalue),c("scan number(s)", "ms-gf:specevalue", "pepseq", "accession")])
+tmp <- tmp[order(tmp$`ms-gf:specevalue`),]
+print("==Head==")
+head(tmp,2)
+print("==Tail==")
+tail(tmp,2)
+
+bt_tmp <- merge(x =  tmp, y=pnnl, by.y = "Scan", by.x  =  "scan number(s)", all.x = T)
+bt_tmp <- bt_tmp[order(bt_tmp$`ms-gf:specevalue`, decreasing = F),]
+```
+There are ```r nrow(tmp)``` rows remained.
+
+### Differences:
+Data from Docker is matched with from PNNL using scan number as ID.
+`r names(bt_tmp)[2:4]` are values from Docker, `r names(bt_tmp)[5:7]` are the corresponding values from PNNL.
+There are `r nrow(bt_tmp)` of rows in total with  `r sum(is.na(bt_tmp$MSGFDB_SpecEValue))` of NULL/unmapped values.
+```{r, include=F}
+tmp_nona <- tmp[!is.na(tmp),]
+```
+Aside from the `r sum(is.na(bt_tmp$MSGFDB_SpecEValue))` unmatched values, ```r sum(tmp_nona$'ms-gf:specevalue'!=tmp_nona$MSGFDB_SpecEValue)``` unmacthed spec-evalue, ```r sum(tmp_nona$pepseq!=tmp_nona$Peptide)``` of unmatched peptide identification.
+
+```{r echo=F}
+print("==Head==")
+head(bt_tmp,2)
+print("==Unmatched==")
+head(bt_tmp[is.na(bt_tmp$MSGFDB_SpecEValue),],3)
+print("==Tail==")
+tail(bt_tmp,2)
+```
+
+```{r include=F}
+evalue = 1e-20
+```
+
+# c. Spec-Evalue `r evalue`
+### From PNNL
+```{r, echo =F}
+pnnl_tmp <- pnnl[pnnl$MSGFDB_SpecEValue<evalue,]
+print("==Head==")
+head(pnnl_tmp,2)
+print("==Tail==")
+tail(pnnl_tmp,2)
+```
+There are ```r nrow(pnnl_tmp)``` rows remained.
+
+### From Docker 
+```{r echo=F}
+tmp <- (p3_table[p3_table$'ms-gf:specevalue'<evalue & !is.na(p3_table$'ms-gf:specevalue'<evalue),c("scan number(s)", "ms-gf:specevalue", "pepseq", "accession")])
+tmp <- tmp[order(tmp$`ms-gf:specevalue`),]
+print("==Head==")
+head(tmp,2)
+print("==Tail==")
+tail(tmp,2)
+
+bt_tmp <- merge(x =  tmp, y=pnnl, by.y = "Scan", by.x  =  "scan number(s)", all.x = T)
+bt_tmp <- bt_tmp[order(bt_tmp$`ms-gf:specevalue`, decreasing = F),]
+```
+There are ```r nrow(tmp)``` rows remained.
+
+### Differences
+Data from Docker is matched with from PNNL using scan number as ID.
+`r names(bt_tmp)[2:4]` are values from Docker, `r names(bt_tmp)[5:7]` are the corresponding values from PNNL.
+There are `r nrow(bt_tmp)` of rows in total with  `r sum(is.na(bt_tmp$MSGFDB_SpecEValue))` of NULL/unmapped values.
+```{r, include=F}
+tmp_nona <- tmp[!is.na(tmp),]
+```
+Aside from the `r sum(is.na(bt_tmp$MSGFDB_SpecEValue))` unmatched values, ```r sum(tmp_nona$'ms-gf:specevalue'!=tmp_nona$MSGFDB_SpecEValue)``` unmacthed spec-evalue, ```r sum(tmp_nona$pepseq!=tmp_nona$Peptide)``` of unmatched peptide identification.
+
+```{r echo=F}
+print("==Head==")
+head(bt_tmp,2)
+print("==Unmatched==")
+head(bt_tmp[is.na(bt_tmp$MSGFDB_SpecEValue),],3)
+print("==Tail==")
+tail(bt_tmp,2)
+```

### 2016-05-23 Benchmark/MSGF-Benchmark/msgf-benchmark.Rmd
benchmark

@@
 evalue = 1e-10
-pnnl <- mzid_pnnl[, c("Scan", "MSGFDB_SpecEValue", "Peptide", "Protein")]
+pnnl <- mzid_pnnl[, c("Scan", "MSGFDB_SpecEValue", "Peptide")]
 p3_flt <- flatten(mzid_p3)
-bigmzid <- merge(pnnl, p3_table[, c("scan number(s)", "ms-gf:specevalue", "pepseq", "accession")], by.x="Scan", by.y = "scan number(s)", all.x = T)
+bigmzid <- merge(pnnl, p3_table[, c("scan number(s)", "ms-gf:specevalue", "pepseq")], by.x="Scan", by.y = "scan number(s)", all.x = T, all.y = T)
 ```
@@
 tmp           <- tmp[order(tmp$'ms-gf:specevalue'),]
-show(head(tmp[,c("scan number(s)", "ms-gf:denovoscore", "ms-gf:specevalue", "accession", "pepseq")])[1:3,])
+show(head(tmp[,c("scan number(s)", "ms-gf:denovoscore", "ms-gf:specevalue",  "pepseq")])[1:3,])
 ## Looking at Scan Number 11612 and 14441
-tmp[(tmp$`scan number(s)`=="11612" | tmp$`scan number(s)`=="14441")  &! is.na(tmp$`scan number(s)`),c("scan number(s)", "ms-gf:denovoscore", "ms-gf:specevalue", "accession", "pepseq")]
+tmp[(tmp$`scan number(s)`=="11612" | tmp$`scan number(s)`=="14441")  &! is.na(tmp$`scan number(s)`),c("scan number(s)", "ms-gf:denovoscore", "ms-gf:specevalue", "pepseq")]
 ```
@@
 tmp           <- tmp[order(tmp$'ms-gf:specevalue'),]
-show(head(tmp[,c("scan number(s)", "ms-gf:denovoscore", "ms-gf:specevalue", "accession", "pepseq")])[1:3,])
+show(head(tmp[,c("scan number(s)", "ms-gf:denovoscore", "ms-gf:specevalue", "pepseq")])[1:3,])
 ## Looking at Scan Number 11612 and 14441
@@
 ```{r, echo=F}
-head(tsv)[1:3,c("ScanNum", "Peptide", "Protein", "SpecEValue")]
+head(tsv)[1:3,c("ScanNum", "Peptide", "SpecEValue")]
 ```
@@
 ```{r echo=F}
-tmp <- (p3_table[p3_table$'ms-gf:specevalue'<evalue & !is.na(p3_table$'ms-gf:specevalue'<evalue),c("scan number(s)", "ms-gf:specevalue", "pepseq", "accession")])
+tmp <- (p3_table[p3_table$'ms-gf:specevalue'<evalue & !is.na(p3_table$'ms-gf:specevalue'<evalue),c("scan number(s)", "ms-gf:specevalue", "pepseq")])
 tmp <- tmp[order(tmp$`ms-gf:specevalue`),]
@@
 ```
+
+# 7. Filtering
+```{r, include=F}
+pnnl$Peptide <- substr(as.character(pnnl$Peptide),1,nchar(as.character(pnnl$Peptide))-2)
+pnnl$Peptide <- substr(as.character(pnnl$Peptide),3,nchar(as.character(pnnl$Peptide)))
+```
+
+# a Spec-Evalue `r evalue`
+### From PNNL
+```{r, echo =F}
+pnnl_tmp <- pnnl[pnnl$MSGFDB_SpecEValue<evalue,]
+print("==Head==")
+head(pnnl_tmp,2)
+print("==Tail==")
+tail(pnnl_tmp,2)
+```
+There are ```r nrow(pnnl_tmp)``` rows remained.
+
+### From Docker 
+```{r echo=F}
+tmp <- (p3_table[p3_table$'ms-gf:specevalue'<evalue & !is.na(p3_table$'ms-gf:specevalue'<evalue),c("scan number(s)", "ms-gf:specevalue", "pepseq")])
+tmp <- tmp[order(tmp$`ms-gf:specevalue`),]
+print("==Head==")
+head(tmp,2)
+print("==Tail==")
+tail(tmp,2)
+
+bt_tmp <- merge(y =  tmp, x=pnnl, by.x = "Scan", by.y  =  "scan number(s)", all.x = T)
+bt_tmp <- bt_tmp[order(bt_tmp$`ms-gf:specevalue`, decreasing = F),]
+```
+There are ```r nrow(tmp)``` rows remained.
+
+### Differences
+Data from Docker is matched with from PNNL using scan number as ID.
+`r names(bt_tmp)[2:4]` are values from Docker, `r names(bt_tmp)[5:7]` are the corresponding values from PNNL.
+There are `r nrow(bt_tmp)` of rows in total with  `r sum(is.na(bt_tmp$'ms-gf:specevalue'))` of NULL/unmapped values.
+
+```{r, echo=F}
+tmp_nona <- tmp[!is.na(tmp),]
+```
+
+Aside from the `r sum(is.na(bt_tmp$'ms-gf:specevalue'))` unmatched values, `r sum(tmp_nona$'ms-gf:specevalue'!=tmp_nona$MSGFDB_SpecEValue)` unmacthed spec-evalue, `r sum(tmp_nona$pepseq!=tmp_nona$Peptide)` of unmatched peptide identification.
+
+```{r echo=F}
+print("==Head==")
+head(bt_tmp,2)
+print("==Unmatched==")
+head(bt_tmp[is.na(bt_tmp$'ms-gf:specevalue'),],3)
+print("==Tail==")
+tail(bt_tmp,2)
+```

### 2016-05-23 Benchmark/MSGF-Benchmark/msgf-benchmark.Rmd
benchmark

@@
 ```{r echo=F}
-tmp <- (p3_table[p3_table$'ms-gf:specevalue'<evalue & !is.na(p3_table$'ms-gf:specevalue'<evalue),c("scan number(s)", "ms-gf:specevalue", "pepseq")])
+tmp <- (p3_table[!is.na(p3_table$'ms-gf:specevalue'<evalue),c("scan number(s)", "ms-gf:specevalue", "pepseq")])
 tmp <- tmp[order(tmp$`ms-gf:specevalue`),]
@@
 Data from Docker is matched with from PNNL using scan number as ID.
-`r names(bt_tmp)[2:4]` are values from Docker, `r names(bt_tmp)[5:7]` are the corresponding values from PNNL.
+`r names(bt_tmp)[2:3]` are values from Docker, `r names(bt_tmp)[4:5]` are the corresponding values from PNNL.
 There are `r nrow(bt_tmp)` of rows in total with  `r sum(is.na(bt_tmp$'ms-gf:specevalue'))` of NULL/unmapped values.

### 2016-05-25 Benchmark/MSGF-Benchmark/msgf-benchmark.Rmd
benchmark

--- 2016-05-23 Benchmark/MSGF-Benchmark/msgf-benchmark.Rmd
@@
 ns_table <- fData(msexp_no_switch)
+
+pnnl <- mzid_pnnl[, c("Scan", "MSGFDB_SpecEValue", "Peptide")]
+pnnl <- pnnl[!duplicated(pnnl$Scan),]
+p3_flt <- flatten(mzid_p3)
+bigmzid <- merge(pnnl, p3_table[, c("scan number(s)", "ms-gf:specevalue", "pepseq")], by.x="Scan", by.y = "scan number(s)", all.x = T, all.y = T)
+pnnl$Peptide <- substr(as.character(pnnl$Peptide),1,nchar(as.character(pnnl$Peptide))-2)
+pnnl$Peptide <- substr(as.character(pnnl$Peptide),3,nchar(as.character(pnnl$Peptide)))
+
 ```
@@
 ```{r, echo = F, include=F}
-library(mzID)
 evalue = 1e-10
-pnnl <- mzid_pnnl[, c("Scan", "MSGFDB_SpecEValue", "Peptide")]
-p3_flt <- flatten(mzid_p3)
-bigmzid <- merge(pnnl, p3_table[, c("scan number(s)", "ms-gf:specevalue", "pepseq")], by.x="Scan", by.y = "scan number(s)", all.x = T, all.y = T)
 ```
@@
 
-# 6. Filtering
-```{r, include=F}
-pnnl$Peptide <- substr(as.character(pnnl$Peptide),1,nchar(as.character(pnnl$Peptide))-2)
-pnnl$Peptide <- substr(as.character(pnnl$Peptide),3,nchar(as.character(pnnl$Peptide)))
+# 6. Filtering (Docker --> PNNL)
+
+```{r include=F}
+evalue = 1e-10
 ```
@@
 bt_tmp <- bt_tmp[order(bt_tmp$`ms-gf:specevalue`, decreasing = F),]
+tmp_nona <- bt_tmp[is.na(bt_tmp$MSGFDB_SpecEValue),]
+tmp_nona <- tmp_nona[order(tmp_nona$'ms-gf:specevalue', decreasing = F),]
+bt_tmp <- bt_tmp[!is.na(bt_tmp$Peptide),]
 ```
@@
 Data from Docker is matched with from PNNL using scan number as ID.
-`r names(bt_tmp)[2:4]` are values from Docker, `r names(bt_tmp)[5:7]` are the corresponding values from PNNL.
-There are `r nrow(bt_tmp)` of rows in total with  `r sum(is.na(bt_tmp$MSGFDB_SpecEValue))` of NULL/unmapped values.
+`r names(bt_tmp)[2:3]` are values from Docker.
+`r names(bt_tmp)[4:5]` are the corresponding values from PNNL.
+There are `r nrow(bt_tmp)` of rows in total with  `r nrow(bt_tmp[((bt_tmp$'ms-gf:specevalue'==bt_tmp$MSGFDB_SpecEValue) & (bt_tmp$pepseq==bt_tmp$Peptide)),])` exact match.
 
-```{r, echo=F}
-tmp_nona <- tmp[!is.na(tmp),]
-```
-
-Aside from the `r sum(is.na(bt_tmp$MSGFDB_SpecEValue))` unmatched values, `r sum(tmp_nona$'ms-gf:specevalue'!=tmp_nona$MSGFDB_SpecEValue)` unmacthed spec-evalue, `r sum(tmp_nona$pepseq!=tmp_nona$Peptide)` of unmatched peptide identification.
+Aside from the `r nrow(tmp_nona)` unmatched values, `r sum(bt_tmp$'ms-gf:specevalue'!=bt_tmp$MSGFDB_SpecEValue)` have different spec-evalue, `r sum(bt_tmp$pepseq!=bt_tmp$Peptide)` of different peptide identification.
 
@@
 head(bt_tmp,2)
-print("==Unmatched==")
-head(bt_tmp[is.na(bt_tmp$MSGFDB_SpecEValue),],3)
 print("==Tail==")
 tail(bt_tmp,2)
+
+print("==Unmatched==")
+head(tmp_nona,2)
+print("==Different Spec Values==")
+head(bt_tmp[(bt_tmp$'ms-gf:specevalue'!=bt_tmp$MSGFDB_SpecEValue),],2)
+print("==Different Peptides identification==")
+head(bt_tmp[(bt_tmp$pepseq!=bt_tmp$Peptide),],2)
+
 ```
@@
 
-### Differences:
+### Differences
 Data from Docker is matched with from PNNL using scan number as ID.
-`r names(bt_tmp)[2:4]` are values from Docker, `r names(bt_tmp)[5:7]` are the corresponding values from PNNL.
-There are `r nrow(bt_tmp)` of rows in total with  `r sum(is.na(bt_tmp$MSGFDB_SpecEValue))` of NULL/unmapped values.
-```{r, include=F}
-tmp_nona <- tmp[!is.na(tmp),]
-```
-Aside from the `r sum(is.na(bt_tmp$MSGFDB_SpecEValue))` unmatched values, ```r sum(tmp_nona$'ms-gf:specevalue'!=tmp_nona$MSGFDB_SpecEValue)``` unmacthed spec-evalue, ```r sum(tmp_nona$pepseq!=tmp_nona$Peptide)``` of unmatched peptide identification.
+`r names(bt_tmp)[2:3]` are values from Docker.
+`r names(bt_tmp)[4:5]` are the corresponding values from PNNL.
+There are `r nrow(bt_tmp)` of rows in total with  `r nrow(bt_tmp[((bt_tmp$'ms-gf:specevalue'==bt_tmp$MSGFDB_SpecEValue) & (bt_tmp$pepseq==bt_tmp$Peptide)),])` exact match.
+
+Aside from the `r nrow(tmp_nona)` unmatched values, `r sum(bt_tmp$'ms-gf:specevalue'!=bt_tmp$MSGFDB_SpecEValue)` have different spec-evalue, `r sum(bt_tmp$pepseq!=bt_tmp$Peptide)` of different peptide identification.
 
@@
 Data from Docker is matched with from PNNL using scan number as ID.
-`r names(bt_tmp)[2:4]` are values from Docker, `r names(bt_tmp)[5:7]` are the corresponding values from PNNL.
-There are `r nrow(bt_tmp)` of rows in total with  `r sum(is.na(bt_tmp$MSGFDB_SpecEValue))` of NULL/unmapped values.
-```{r, include=F}
-tmp_nona <- tmp[!is.na(tmp),]
-```
-Aside from the `r sum(is.na(bt_tmp$MSGFDB_SpecEValue))` unmatched values, ```r sum(tmp_nona$'ms-gf:specevalue'!=tmp_nona$MSGFDB_SpecEValue)``` unmacthed spec-evalue, ```r sum(tmp_nona$pepseq!=tmp_nona$Peptide)``` of unmatched peptide identification.
+`r names(bt_tmp)[2:3]` are values from Docker.
+`r names(bt_tmp)[4:5]` are the corresponding values from PNNL.
+There are `r nrow(bt_tmp)` of rows in total with  `r nrow(bt_tmp[((bt_tmp$'ms-gf:specevalue'==bt_tmp$MSGFDB_SpecEValue) & (bt_tmp$pepseq==bt_tmp$Peptide)),])` exact match.
+
+Aside from the `r nrow(tmp_nona)` unmatched values, `r sum(bt_tmp$'ms-gf:specevalue'!=bt_tmp$MSGFDB_SpecEValue)` have different spec-evalue, `r sum(bt_tmp$pepseq!=bt_tmp$Peptide)` of different peptide identification.
 
@@
 head(bt_tmp,2)
-print("==Unmatched==")
-head(bt_tmp[is.na(bt_tmp$MSGFDB_SpecEValue),],3)
 print("==Tail==")
 tail(bt_tmp,2)
+
+print("==Unmatched==")
+head(tmp_nona,2)
+print("==Different Spec Values==")
+head(bt_tmp[(bt_tmp$'ms-gf:specevalue'!=bt_tmp$MSGFDB_SpecEValue),],2)
+print("==Different Peptides identification==")
+head(bt_tmp[(bt_tmp$pepseq!=bt_tmp$Peptide),],2)
+
 ```
 
-# 7. Filtering
-```{r, include=F}
-pnnl$Peptide <- substr(as.character(pnnl$Peptide),1,nchar(as.character(pnnl$Peptide))-2)
-pnnl$Peptide <- substr(as.character(pnnl$Peptide),3,nchar(as.character(pnnl$Peptide)))
+```{r include=F}
+evalue = 1e-15
 ```
 
-# a Spec-Evalue `r evalue`
+# 7. Filtering (PNNL -> Docker)
+
+```{r include=F}
+evalue = 1e-10
+```
+
+# a. Spec-Evalue `r evalue`
 ### From PNNL
@@
 
-bt_tmp <- merge(y =  tmp, x=pnnl, by.x = "Scan", by.y  =  "scan number(s)", all.x = T)
+bt_tmp <- merge.data.frame(y =  p3_table[,c("scan number(s)", "ms-gf:specevalue", "pepseq")], x=pnnl_tmp, by.x = "Scan", by.y  =  "scan number(s)", all.x = T, all.y = F)
 bt_tmp <- bt_tmp[order(bt_tmp$`ms-gf:specevalue`, decreasing = F),]
+tmp_nona <- bt_tmp[is.na(bt_tmp$'ms-gf:specevalue'),]
+tmp_nona <- tmp_nona[order(tmp_nona$MSGFDB_SpecEValue, decreasing = F),]
+bt_tmp <- bt_tmp[!is.na(bt_tmp$'pepseq'),]
 ```
@@
 Data from Docker is matched with from PNNL using scan number as ID.
-`r names(bt_tmp)[2:4]` are values from Docker, `r names(bt_tmp)[5:7]` are the corresponding values from PNNL.
-There are `r nrow(bt_tmp)` of rows in total with  `r sum(is.na(bt_tmp$'ms-gf:specevalue'))` of NULL/unmapped values.
+`r names(bt_tmp)[2:3]` are values from PNNL.
+`r names(bt_tmp)[4:5]` are the corresponding values from Docker Container.
+There are `r nrow(bt_tmp)` of rows in total with   `r nrow(bt_tmp[((bt_tmp$'ms-gf:specevalue'==bt_tmp$MSGFDB_SpecEValue) & (bt_tmp$pepseq==bt_tmp$Peptide)),])` exact match.
 
-```{r, echo=F}
-tmp_nona <- tmp[!is.na(tmp),]
-```
-
-Aside from the `r sum(is.na(bt_tmp$'ms-gf:specevalue'))` unmatched values, `r sum(tmp_nona$'ms-gf:specevalue'!=tmp_nona$MSGFDB_SpecEValue)` unmacthed spec-evalue, `r sum(tmp_nona$pepseq!=tmp_nona$Peptide)` of unmatched peptide identification.
+Aside from the `r nrow(tmp_nona)` unmatched values, `r sum(bt_tmp$'ms-gf:specevalue'!=bt_tmp$MSGFDB_SpecEValue)` have different spec-evalue, `r sum(bt_tmp$pepseq!=bt_tmp$Peptide)` of different peptide identification.
 
@@
 print("==Unmatched==")
-head(bt_tmp[is.na(bt_tmp$'ms-gf:specevalue'),],3)
+head(tmp_nona,3)
 print("==Tail==")
 tail(bt_tmp,2)
+
+print("==Unmatched==")
+head(tmp_nona,2)
+print("==Different Spec Values==")
+head(bt_tmp[(bt_tmp$'ms-gf:specevalue'!=bt_tmp$MSGFDB_SpecEValue),],2)
+print("==Different Peptides identification==")
+head(bt_tmp[(bt_tmp$pepseq!=bt_tmp$Peptide),],2)
+
 ```
+
+```{r include=F}
+evalue = 1e-15
+```
+
+# b. Spec-Evalue `r evalue`
+
+### From PNNL
+```{r, echo =F}
+pnnl_tmp <- pnnl[pnnl$MSGFDB_SpecEValue<evalue,]
+head(pnnl_tmp,2)
+tail(pnnl_tmp,2)
+```
+There are ```r nrow(pnnl_tmp)``` rows remained.
+
+### From Docker 
+```{r echo=F}
+tmp <- (p3_table[p3_table$'ms-gf:specevalue'<evalue & !is.na(p3_table$'ms-gf:specevalue'<evalue),c("scan number(s)", "ms-gf:specevalue", "pepseq")])
+tmp <- tmp[order(tmp$`ms-gf:specevalue`),]
+print("==Head==")
+head(tmp,2)
+print("==Tail==")
+tail(tmp,2)
+
+bt_tmp <- merge.data.frame(y =  p3_table[,c("scan number(s)", "ms-gf:specevalue", "pepseq")], x=pnnl_tmp, by.x = "Scan", by.y  =  "scan number(s)", all.x = T, all.y = F)
+bt_tmp <- bt_tmp[order(bt_tmp$`ms-gf:specevalue`, decreasing = F),]
+tmp_nona <- bt_tmp[is.na(bt_tmp$'ms-gf:specevalue'),]
+tmp_nona <- tmp_nona[order(tmp_nona$MSGFDB_SpecEValue, decreasing = F),]
+bt_tmp <- bt_tmp[!is.na(bt_tmp$'pepseq'),]
+```
+There are ```r nrow(tmp)``` rows remained.
+
+### Differences
+Data from Docker is matched with from PNNL using scan number as ID.
+`r names(bt_tmp)[2:3]` are values from PNNL.
+`r names(bt_tmp)[4:5]` are the corresponding values from Docker Container.
+There are `r nrow(bt_tmp)` of rows in total with   `r nrow(bt_tmp[((bt_tmp$'ms-gf:specevalue'==bt_tmp$MSGFDB_SpecEValue) & (bt_tmp$pepseq==bt_tmp$Peptide)),])` exact match.
+
+Aside from the `r nrow(tmp_nona)` unmatched values, `r sum(bt_tmp$'ms-gf:specevalue'!=bt_tmp$MSGFDB_SpecEValue)` have different spec-evalue, `r sum(bt_tmp$pepseq!=bt_tmp$Peptide)` of different peptide identification.
+
+```{r echo=F}
+print("==Head==")
+head(bt_tmp,2)
+print("==Unmatched==")
+head(tmp_nona,3)
+print("==Tail==")
+tail(bt_tmp,2)
+
+print("==Unmatched==")
+head(tmp_nona,2)
+print("==Different Spec Values==")
+head(bt_tmp[(bt_tmp$'ms-gf:specevalue'!=bt_tmp$MSGFDB_SpecEValue),],2)
+print("==Different Peptides identification==")
+head(bt_tmp[(bt_tmp$pepseq!=bt_tmp$Peptide),],2)
+
+```
+
+```{r include=F}
+evalue = 1e-20
+```
+
+# c. Spec-Evalue `r evalue`
+
+### From PNNL
+```{r, echo =F}
+pnnl_tmp <- pnnl[pnnl$MSGFDB_SpecEValue<evalue,]
+head(pnnl_tmp,2)
+tail(pnnl_tmp,2)
+```
+There are ```r nrow(pnnl_tmp)``` rows remained.
+
+### From Docker 
+```{r echo=F}
+tmp <- (p3_table[p3_table$'ms-gf:specevalue'<evalue & !is.na(p3_table$'ms-gf:specevalue'<evalue),c("scan number(s)", "ms-gf:specevalue", "pepseq")])
+tmp <- tmp[order(tmp$`ms-gf:specevalue`),]
+print("==Head==")
+head(tmp,2)
+print("==Tail==")
+tail(tmp,2)
+
+bt_tmp <- merge.data.frame(y =  p3_table[,c("scan number(s)", "ms-gf:specevalue", "pepseq")], x=pnnl_tmp, by.x = "Scan", by.y  =  "scan number(s)", all.x = T, all.y = F)
+bt_tmp <- bt_tmp[order(bt_tmp$`ms-gf:specevalue`, decreasing = F),]
+tmp_nona <- bt_tmp[is.na(bt_tmp$'ms-gf:specevalue'),]
+tmp_nona <- tmp_nona[order(tmp_nona$MSGFDB_SpecEValue, decreasing = F),]
+bt_tmp <- bt_tmp[!is.na(bt_tmp$'pepseq'),]
+```
+There are ```r nrow(tmp)``` rows remained.
+
+### Differences
+Data from Docker is matched with from PNNL using scan number as ID.
+`r names(bt_tmp)[2:3]` are values from PNNL.
+`r names(bt_tmp)[4:5]` are the corresponding values from Docker Container.
+There are `r nrow(bt_tmp)` of rows in total with   `r nrow(bt_tmp[((bt_tmp$'ms-gf:specevalue'==bt_tmp$MSGFDB_SpecEValue) & (bt_tmp$pepseq==bt_tmp$Peptide)),])` exact match.
+
+Aside from the `r nrow(tmp_nona)` unmatched values, `r sum(bt_tmp$'ms-gf:specevalue'!=bt_tmp$MSGFDB_SpecEValue)` have different spec-evalue, `r sum(bt_tmp$pepseq!=bt_tmp$Peptide)` of different peptide identification.
+
+```{r echo=F}
+print("==Head==")
+head(bt_tmp,2)
+print("==Unmatched==")
+head(tmp_nona,3)
+print("==Tail==")
+tail(bt_tmp,2)
+
+print("==Unmatched==")
+head(tmp_nona,2)
+print("==Different Spec Values==")
+head(bt_tmp[(bt_tmp$'ms-gf:specevalue'!=bt_tmp$MSGFDB_SpecEValue),],2)
+print("==Different Peptides identification==")
+head(bt_tmp[(bt_tmp$pepseq!=bt_tmp$Peptide),],2)
+
+```

### 2016-05-25 Benchmark/MSGF-Benchmark/msgf-benchmark.Rmd
benchmark

@@
 
-# 6. Filtering (Docker --> PNNL)
+# 7. Filtering (PNNL -> Docker)
 
-```{r include=F}
+```{r no 7, echo=F}
+############# 7##########################
 evalue = 1e-10
@@
 
-# a Spec-Evalue `r evalue`
+# a. Spec-Evalue `r evalue`
 ### From PNNL
@@
 pnnl_tmp <- pnnl[pnnl$MSGFDB_SpecEValue<evalue,]
-print("==Head==")
-head(pnnl_tmp,2)
-print("==Tail==")
-tail(pnnl_tmp,2)
 ```
@@
 tmp <- tmp[order(tmp$`ms-gf:specevalue`),]
-print("==Head==")
-head(tmp,2)
-print("==Tail==")
-tail(tmp,2)
 
-bt_tmp <- merge(x =  tmp, y=pnnl, by.y = "Scan", by.x  =  "scan number(s)", all.x = T)
+bt_tmp <- merge.data.frame(y =  p3_table[,c("scan number(s)", "ms-gf:specevalue", "pepseq")], x=pnnl_tmp, by.x = "Scan", by.y  =  "scan number(s)", all.x = T, all.y = F)
 bt_tmp <- bt_tmp[order(bt_tmp$`ms-gf:specevalue`, decreasing = F),]
-tmp_nona <- bt_tmp[is.na(bt_tmp$MSGFDB_SpecEValue),]
-tmp_nona <- tmp_nona[order(tmp_nona$'ms-gf:specevalue', decreasing = F),]
-bt_tmp <- bt_tmp[!is.na(bt_tmp$Peptide),]
+tmp_nona <- bt_tmp[is.na(bt_tmp$'ms-gf:specevalue'),]
+tmp_nona <- tmp_nona[order(tmp_nona$MSGFDB_SpecEValue, decreasing = F),]
+bt_tmp <- bt_tmp[!is.na(bt_tmp$'pepseq'),]
+the_x = bt_tmp[((bt_tmp$'ms-gf:specevalue'==bt_tmp$MSGFDB_SpecEValue) & (bt_tmp$pepseq==bt_tmp$Peptide)),]
+the_y = bt_tmp[((bt_tmp$'ms-gf:specevalue'!=bt_tmp$MSGFDB_SpecEValue) & (bt_tmp$pepseq==bt_tmp$Peptide)),]
+the_z = bt_tmp[((bt_tmp$'ms-gf:specevalue'!=bt_tmp$MSGFDB_SpecEValue) & (bt_tmp$pepseq!=bt_tmp$Peptide)),]
+
 ```
 There are ```r nrow(tmp)``` rows remained.
-
-### Differences
-Data from Docker is matched with from PNNL using scan number as ID.
-`r names(bt_tmp)[2:3]` are values from Docker.
-`r names(bt_tmp)[4:5]` are the corresponding values from PNNL.
-There are `r nrow(bt_tmp)` of rows in total with  `r nrow(bt_tmp[((bt_tmp$'ms-gf:specevalue'==bt_tmp$MSGFDB_SpecEValue) & (bt_tmp$pepseq==bt_tmp$Peptide)),])` exact match.
-
-Aside from the `r nrow(tmp_nona)` unmatched values, `r sum(bt_tmp$'ms-gf:specevalue'!=bt_tmp$MSGFDB_SpecEValue)` have different spec-evalue, `r sum(bt_tmp$pepseq!=bt_tmp$Peptide)` of different peptide identification.
 
@@
 tail(bt_tmp,2)
-
-print("==Unmatched==")
-head(tmp_nona,2)
-print("==Different Spec Values==")
-head(bt_tmp[(bt_tmp$'ms-gf:specevalue'!=bt_tmp$MSGFDB_SpecEValue),],2)
-print("==Different Peptides identification==")
-head(bt_tmp[(bt_tmp$pepseq!=bt_tmp$Peptide),],2)
-
 ```
-
-```{r include=F}
-evalue = 1e-15
-```
-
-# b. Spec-Evalue `r evalue`
-### From PNNL
-```{r, echo =F}
-pnnl_tmp <- pnnl[pnnl$MSGFDB_SpecEValue<evalue,]
-print("==Head==")
-head(pnnl_tmp,2)
-print("==Tail==")
-tail(pnnl_tmp,2)
-```
-There are ```r nrow(pnnl_tmp)``` rows remained.
-
-### From Docker 
-```{r echo=F}
-tmp <- (p3_table[p3_table$'ms-gf:specevalue'<evalue & !is.na(p3_table$'ms-gf:specevalue'<evalue),c("scan number(s)", "ms-gf:specevalue", "pepseq")])
-tmp <- tmp[order(tmp$`ms-gf:specevalue`),]
-print("==Head==")
-head(tmp,2)
-print("==Tail==")
-tail(tmp,2)
-
-bt_tmp <- merge(x =  tmp, y=pnnl, by.y = "Scan", by.x  =  "scan number(s)", all.x = T)
-bt_tmp <- bt_tmp[order(bt_tmp$`ms-gf:specevalue`, decreasing = F),]
-tmp_nona <- bt_tmp[is.na(bt_tmp$MSGFDB_SpecEValue),]
-tmp_nona <- tmp_nona[order(tmp_nona$'ms-gf:specevalue', decreasing = F),]
-bt_tmp <- bt_tmp[!is.na(bt_tmp$Peptide),]
-```
-There are ```r nrow(tmp)``` rows remained.
-
-### Differences
-Data from Docker is matched with from PNNL using scan number as ID.
-`r names(bt_tmp)[2:3]` are values from Docker.
-`r names(bt_tmp)[4:5]` are the corresponding values from PNNL.
-There are `r nrow(bt_tmp)` of rows in total with  `r nrow(bt_tmp[((bt_tmp$'ms-gf:specevalue'==bt_tmp$MSGFDB_SpecEValue) & (bt_tmp$pepseq==bt_tmp$Peptide)),])` exact match.
-
-Aside from the `r nrow(tmp_nona)` unmatched values, `r sum(bt_tmp$'ms-gf:specevalue'!=bt_tmp$MSGFDB_SpecEValue)` have different spec-evalue, `r sum(bt_tmp$pepseq!=bt_tmp$Peptide)` of different peptide identification.
-
-```{r echo=F}
-print("==Head==")
-head(bt_tmp,2)
-print("==Tail==")
-tail(bt_tmp,2)
-
-print("==Unmatched==")
-head(tmp_nona,2)
-print("==Different Spec Values==")
-head(bt_tmp[(bt_tmp$'ms-gf:specevalue'!=bt_tmp$MSGFDB_SpecEValue),],2)
-print("==Different Peptides identification==")
-head(bt_tmp[(bt_tmp$pepseq!=bt_tmp$Peptide),],2)
-
-```
-
-```{r include=F}
-evalue = 1e-20
-```
-
-# c. Spec-Evalue `r evalue`
-### From PNNL
-```{r, echo =F}
-pnnl_tmp <- pnnl[pnnl$MSGFDB_SpecEValue<evalue,]
-print("==Head==")
-head(pnnl_tmp,2)
-print("==Tail==")
-tail(pnnl_tmp,2)
-```
-There are ```r nrow(pnnl_tmp)``` rows remained.
-
-### From Docker 
-```{r echo=F}
-tmp <- (p3_table[p3_table$'ms-gf:specevalue'<evalue & !is.na(p3_table$'ms-gf:specevalue'<evalue),c("scan number(s)", "ms-gf:specevalue", "pepseq")])
-tmp <- tmp[order(tmp$`ms-gf:specevalue`),]
-print("==Head==")
-head(tmp,2)
-print("==Tail==")
-tail(tmp,2)
-
-bt_tmp <- merge(x =  tmp, y=pnnl, by.y = "Scan", by.x  =  "scan number(s)", all.x = T)
-bt_tmp <- bt_tmp[order(bt_tmp$`ms-gf:specevalue`, decreasing = F),]
-tmp_nona <- bt_tmp[is.na(bt_tmp$MSGFDB_SpecEValue),]
-tmp_nona <- tmp_nona[order(tmp_nona$'ms-gf:specevalue', decreasing = F),]
-bt_tmp <- bt_tmp[!is.na(bt_tmp$Peptide),]
-```
-There are ```r nrow(tmp)``` rows remained.
-
-### Differences
-Data from Docker is matched with from PNNL using scan number as ID.
-`r names(bt_tmp)[2:3]` are values from Docker.
-`r names(bt_tmp)[4:5]` are the corresponding values from PNNL.
-There are `r nrow(bt_tmp)` of rows in total with  `r nrow(bt_tmp[((bt_tmp$'ms-gf:specevalue'==bt_tmp$MSGFDB_SpecEValue) & (bt_tmp$pepseq==bt_tmp$Peptide)),])` exact match.
-
-Aside from the `r nrow(tmp_nona)` unmatched values, `r sum(bt_tmp$'ms-gf:specevalue'!=bt_tmp$MSGFDB_SpecEValue)` have different spec-evalue, `r sum(bt_tmp$pepseq!=bt_tmp$Peptide)` of different peptide identification.
-
-```{r echo=F}
-print("==Head==")
-head(bt_tmp,2)
-print("==Tail==")
-tail(bt_tmp,2)
-
-print("==Unmatched==")
-head(tmp_nona,2)
-print("==Different Spec Values==")
-head(bt_tmp[(bt_tmp$'ms-gf:specevalue'!=bt_tmp$MSGFDB_SpecEValue),],2)
-print("==Different Peptides identification==")
-head(bt_tmp[(bt_tmp$pepseq!=bt_tmp$Peptide),],2)
-
-```
-
-```{r include=F}
-evalue = 1e-15
-```
-
-# 7. Filtering (PNNL -> Docker)
-
-```{r include=F}
-evalue = 1e-10
-```
-
-# a. Spec-Evalue `r evalue`
-### From PNNL
-```{r, echo =F}
-pnnl_tmp <- pnnl[pnnl$MSGFDB_SpecEValue<evalue,]
-print("==Head==")
-head(pnnl_tmp,2)
-print("==Tail==")
-tail(pnnl_tmp,2)
-```
-There are ```r nrow(pnnl_tmp)``` rows remained.
-
-### From Docker 
-```{r echo=F}
-tmp <- (p3_table[p3_table$'ms-gf:specevalue'<evalue & !is.na(p3_table$'ms-gf:specevalue'<evalue),c("scan number(s)", "ms-gf:specevalue", "pepseq")])
-tmp <- tmp[order(tmp$`ms-gf:specevalue`),]
-print("==Head==")
-head(tmp,2)
-print("==Tail==")
-tail(tmp,2)
-
-bt_tmp <- merge.data.frame(y =  p3_table[,c("scan number(s)", "ms-gf:specevalue", "pepseq")], x=pnnl_tmp, by.x = "Scan", by.y  =  "scan number(s)", all.x = T, all.y = F)
-bt_tmp <- bt_tmp[order(bt_tmp$`ms-gf:specevalue`, decreasing = F),]
-tmp_nona <- bt_tmp[is.na(bt_tmp$'ms-gf:specevalue'),]
-tmp_nona <- tmp_nona[order(tmp_nona$MSGFDB_SpecEValue, decreasing = F),]
-bt_tmp <- bt_tmp[!is.na(bt_tmp$'pepseq'),]
-```
-There are ```r nrow(tmp)``` rows remained.
 
@@
 `r names(bt_tmp)[4:5]` are the corresponding values from Docker Container.
-There are `r nrow(bt_tmp)` of rows in total with   `r nrow(bt_tmp[((bt_tmp$'ms-gf:specevalue'==bt_tmp$MSGFDB_SpecEValue) & (bt_tmp$pepseq==bt_tmp$Peptide)),])` exact match.
+There are `r nrow(bt_tmp)` of rows in total with   `r nrow(the_x)` exact match.
 
-Aside from the `r nrow(tmp_nona)` unmatched values, `r sum(bt_tmp$'ms-gf:specevalue'!=bt_tmp$MSGFDB_SpecEValue)` have different spec-evalue, `r sum(bt_tmp$pepseq!=bt_tmp$Peptide)` of different peptide identification.
+Aside from the `r nrow(tmp_nona)` unmatched values, `r nrow(the_y)` with the same peptide identification and different spec-evalue, `r nrow(the_z)` of different peptide identification as well different spec-evalues.
 
 ```{r echo=F}
-print("==Head==")
-head(bt_tmp,2)
-print("==Unmatched==")
-head(tmp_nona,3)
-print("==Tail==")
-tail(bt_tmp,2)
-
 print("==Unmatched==")
 head(tmp_nona,2)
-print("==Different Spec Values==")
-head(bt_tmp[(bt_tmp$'ms-gf:specevalue'!=bt_tmp$MSGFDB_SpecEValue),],2)
-print("==Different Peptides identification==")
-head(bt_tmp[(bt_tmp$pepseq!=bt_tmp$Peptide),],2)
+print("==Different Spec eValues==")
+head(the_y,2)
+print("==Different Peptides identification and different Spec Evalues==")
+head(the_z,2)
 
 ```
-
-```{r include=F}
-evalue = 1e-15
-```
-
-# b. Spec-Evalue `r evalue`
-
-### From PNNL
-```{r, echo =F}
-pnnl_tmp <- pnnl[pnnl$MSGFDB_SpecEValue<evalue,]
-head(pnnl_tmp,2)
-tail(pnnl_tmp,2)
-```
-There are ```r nrow(pnnl_tmp)``` rows remained.
-
-### From Docker 
-```{r echo=F}
-tmp <- (p3_table[p3_table$'ms-gf:specevalue'<evalue & !is.na(p3_table$'ms-gf:specevalue'<evalue),c("scan number(s)", "ms-gf:specevalue", "pepseq")])
-tmp <- tmp[order(tmp$`ms-gf:specevalue`),]
-print("==Head==")
-head(tmp,2)
-print("==Tail==")
-tail(tmp,2)
-
-bt_tmp <- merge.data.frame(y =  p3_table[,c("scan number(s)", "ms-gf:specevalue", "pepseq")], x=pnnl_tmp, by.x = "Scan", by.y  =  "scan number(s)", all.x = T, all.y = F)
-bt_tmp <- bt_tmp[order(bt_tmp$`ms-gf:specevalue`, decreasing = F),]
-tmp_nona <- bt_tmp[is.na(bt_tmp$'ms-gf:specevalue'),]
-tmp_nona <- tmp_nona[order(tmp_nona$MSGFDB_SpecEValue, decreasing = F),]
-bt_tmp <- bt_tmp[!is.na(bt_tmp$'pepseq'),]
-```
-There are ```r nrow(tmp)``` rows remained.
-
-### Differences
-Data from Docker is matched with from PNNL using scan number as ID.
-`r names(bt_tmp)[2:3]` are values from PNNL.
-`r names(bt_tmp)[4:5]` are the corresponding values from Docker Container.
-There are `r nrow(bt_tmp)` of rows in total with   `r nrow(bt_tmp[((bt_tmp$'ms-gf:specevalue'==bt_tmp$MSGFDB_SpecEValue) & (bt_tmp$pepseq==bt_tmp$Peptide)),])` exact match.
-
-Aside from the `r nrow(tmp_nona)` unmatched values, `r sum(bt_tmp$'ms-gf:specevalue'!=bt_tmp$MSGFDB_SpecEValue)` have different spec-evalue, `r sum(bt_tmp$pepseq!=bt_tmp$Peptide)` of different peptide identification.
-
-```{r echo=F}
-print("==Head==")
-head(bt_tmp,2)
-print("==Unmatched==")
-head(tmp_nona,3)
-print("==Tail==")
-tail(bt_tmp,2)
-
-print("==Unmatched==")
-head(tmp_nona,2)
-print("==Different Spec Values==")
-head(bt_tmp[(bt_tmp$'ms-gf:specevalue'!=bt_tmp$MSGFDB_SpecEValue),],2)
-print("==Different Peptides identification==")
-head(bt_tmp[(bt_tmp$pepseq!=bt_tmp$Peptide),],2)
-
-```
-
-```{r include=F}
-evalue = 1e-20
-```
-
-# c. Spec-Evalue `r evalue`
-
-### From PNNL
-```{r, echo =F}
-pnnl_tmp <- pnnl[pnnl$MSGFDB_SpecEValue<evalue,]
-head(pnnl_tmp,2)
-tail(pnnl_tmp,2)
-```
-There are ```r nrow(pnnl_tmp)``` rows remained.
-
-### From Docker 
-```{r echo=F}
-tmp <- (p3_table[p3_table$'ms-gf:specevalue'<evalue & !is.na(p3_table$'ms-gf:specevalue'<evalue),c("scan number(s)", "ms-gf:specevalue", "pepseq")])
-tmp <- tmp[order(tmp$`ms-gf:specevalue`),]
-print("==Head==")
-head(tmp,2)
-print("==Tail==")
-tail(tmp,2)
-
-bt_tmp <- merge.data.frame(y =  p3_table[,c("scan number(s)", "ms-gf:specevalue", "pepseq")], x=pnnl_tmp, by.x = "Scan", by.y  =  "scan number(s)", all.x = T, all.y = F)
-bt_tmp <- bt_tmp[order(bt_tmp$`ms-gf:specevalue`, decreasing = F),]
-tmp_nona <- bt_tmp[is.na(bt_tmp$'ms-gf:specevalue'),]
-tmp_nona <- tmp_nona[order(tmp_nona$MSGFDB_SpecEValue, decreasing = F),]
-bt_tmp <- bt_tmp[!is.na(bt_tmp$'pepseq'),]
-```
-There are ```r nrow(tmp)``` rows remained.
-
-### Differences
-Data from Docker is matched with from PNNL using scan number as ID.
-`r names(bt_tmp)[2:3]` are values from PNNL.
-`r names(bt_tmp)[4:5]` are the corresponding values from Docker Container.
-There are `r nrow(bt_tmp)` of rows in total with   `r nrow(bt_tmp[((bt_tmp$'ms-gf:specevalue'==bt_tmp$MSGFDB_SpecEValue) & (bt_tmp$pepseq==bt_tmp$Peptide)),])` exact match.
-
-Aside from the `r nrow(tmp_nona)` unmatched values, `r sum(bt_tmp$'ms-gf:specevalue'!=bt_tmp$MSGFDB_SpecEValue)` have different spec-evalue, `r sum(bt_tmp$pepseq!=bt_tmp$Peptide)` of different peptide identification.
-
-```{r echo=F}
-print("==Head==")
-head(bt_tmp,2)
-print("==Unmatched==")
-head(tmp_nona,3)
-print("==Tail==")
-tail(bt_tmp,2)
-
-print("==Unmatched==")
-head(tmp_nona,2)
-print("==Different Spec Values==")
-head(bt_tmp[(bt_tmp$'ms-gf:specevalue'!=bt_tmp$MSGFDB_SpecEValue),],2)
-print("==Different Peptides identification==")
-head(bt_tmp[(bt_tmp$pepseq!=bt_tmp$Peptide),],2)
-
-```

### 2016-05-25 Benchmark/MSGF-Benchmark/msgf-benchmark.Rmd
benchmark

@@
 
-Aside from the `r nrow(tmp_nona)` unmatched values, `r nrow(the_y)` with the same peptide identification and different spec-evalue, `r nrow(the_z)` of different peptide identification as well different spec-evalues.
+`r nrow(the_y)` with the same peptide identification and different spec-evalue, `r nrow(the_z)` of different peptide identification as well different spec-evalues (`r nrow(tmp_nona)` of them are unmatched values).
 

### 2016-05-27 Benchmark/MSGF-Benchmark/msgf-benchmark2.Rmd
benchmark

---
title: | 
  | Portable Proteomics Pipeline (P3) 
  | MSGF Benchmark
author: "Daniel Kristiyanto (daniel.kristiyanto@pnnl.gov)"
date: \today
fontsize: 10pt
output: pdf_document
# bibliography: ../../media/ref.bib
nocite: |
  @domon2006mass, @deutsch2010mass, @MSnba83
csl: ../../media/biomed-central.csl
header-includes:
  \usepackage{fancyhdr}
  \usepackage{graphicx}
  \usepackage{hyperref}
  \pagestyle{fancy}
  \setlength\headheight{28pt}
  \rhead{\includegraphics[width = .2\textwidth]{../../media/pnnllogo.png}}
  \fancyfoot[LE,RO]{kristiyanto/p3:benchmark}
---
\rule{\textwidth}{1pt}
```{r, warning=FALSE, echo=FALSE, include=FALSE, cache=T}
library(MSnbase)
library(mzID)
library(stringr)
```

```{r, warning=FALSE, echo=FALSE, include=FALSE, cache=T}
setwd("~/Dropbox/_SPACE/Benchmark/11")
file_mzid        <- list.files(path = ".", pattern ="mzid", all.files = F, 
                      full.names = F, recursive = F, ignore.case = T, include.dirs = F)
file_mzml        <- list.files(path = ".", pattern ="mzML$|mzXML$", all.files = F, 
                      full.names = F, recursive = F, ignore.case = T, include.dirs = F)
file_fasta        <- list.files(path = ".", pattern ="fasta", all.files = F, 
                      full.names = F, recursive = F, ignore.case = T, include.dirs = F)

mzid_pnnl         <- read.table(file="TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11_msgfdb_fht.txt", sep="\t", header=T)
frm_docker        <- read.table(file="TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11.txt", sep="\t", header = T)

pnnl <- mzid_pnnl[, c("Scan", "MSGFDB_SpecEValue", "Peptide")]
pnnl <- pnnl[!duplicated(pnnl$Scan),]
pnnl$Peptide <- substr(as.character(pnnl$Peptide),1,nchar(as.character(pnnl$Peptide))-2)
pnnl$Peptide <- substr(as.character(pnnl$Peptide),3,nchar(as.character(pnnl$Peptide)))
docker       <- frm_docker[,c("Scan","Spec_Evalue","PepSeq")]
```

# 1. Files:

```{r, echo=F}
print("From PNNL: TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11_msgfdb_fht.txt")
print("From Docker: TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11.txt")
```

# 2. Identification:
Identification used the following switches:
```
# Command Line (2)
java -Xmx8000M -jar P3/MSGFPlus.jar -s \
TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11.mzML -o \
TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11.mzid \
-d ID_003632_9011437E.fasta  \
-t 10ppm -m 0 -inst 1 -e 1 -ti -1,2 -ntt 2 -tda 1 -minLength 6 \
-maxLength 50 -minCharge 2 -maxCharge 5 -n 1 -thread 7 \
-mod MSGFDB_Mods.txt -minNumPeaks 5 -addFeatures 1
```

```{r, echo = F, include=F}
evalue = 1e-10
```

#3. Differences. Spec eValue = `r evalue` 
### a. From PNNL
```{r, echo=F}
c_pnnl = pnnl[pnnl$MSGFDB_SpecEValue<evalue,]
# No of remaining scans 
nrow(c_pnnl)
head(c_pnnl,2)
tail(c_pnnl,2)

```

### a. From Docker
```{r, echo=F}
c_docker = docker[docker$Spec_Evalue<evalue,]
# No of remaining scans 
nrow(c_docker)
head(c_docker,2)
tail(c_docker,2)
```

### 2016-05-27 Benchmark/MSGF-Benchmark/msgf-benchmark2.Rmd
skip filtering option

@@
 c_pnnl = pnnl[pnnl$MSGFDB_SpecEValue<evalue,]
-# No of remaining scans 
-nrow(c_pnnl)
+print(paste("Remaining peptides:",nrow(c_pnnl)))
+print("====== head ======")
 head(c_pnnl,2)
+print("====== tail ======")
 tail(c_pnnl,2)
@@
 c_docker = docker[docker$Spec_Evalue<evalue,]
-# No of remaining scans 
-nrow(c_docker)
+print(paste("Remaining peptides:",nrow(c_docker)))
+print("====== head ======")
 head(c_docker,2)
+print("====== tail ======")
 tail(c_docker,2)

### 2016-05-27 entry.py

@@ -226,7 +226,7 @@ def get_msgf_opts(options):
 	return MSGF_OPTS
 
 def get_count_opts(options):
-	R_OPTS = dict(SPECEVALUE_TRESHOLD= 0.01, pNA= 4, QUANTIFICATION_METHOD="count", COMBINE_BY="mean")
+	R_OPTS = dict(SPECEVALUE_TRESHOLD= 0, pNA= 4, QUANTIFICATION_METHOD="count", COMBINE_BY="mean")
 	for k,v in R_OPTS.items():
 		try:
 			x = options.get("ITRAQ4", k)
@@ -238,7 +238,7 @@ def get_count_opts(options):
 
 			
 def scquant(mzid_set, options):
-	R_OPTS = dict(SPEC_EVALUE_TRESHOLD= 1e-10)
+	R_OPTS = dict(SPEC_EVALUE_TRESHOLD= 0)
 	opts_set = ("SPEC_EVALUE_TRESHOLD")
 	for k,v in R_OPTS.items():
 		try: 
@@ -426,8 +426,7 @@ def write_blank_p3(config_file):
 	
 	[SPECTRUM_COUNT]
 	# Ignored if QUANTIFICATION METHOD is not SPECTRUM_COUNT
-	# If left blank will be replaced with default
-	# Please check documentation for more detail
+	# If left blank filtering will not be performed
 	SPEC_EVALUE_TRESHOLD = 1e-10
 	# COMBINE_BY will perform feature folding with the specified function. If "SKIP" is given, this task will not be performed.
 	# COMBINE_BY: SKIP / mean / median / weighted.mean / sum / medpolish
@@ -435,8 +434,7 @@ def write_blank_p3(config_file):
 
 	[ITRAQ4]
 	# Ignored if QUANTIFICATION METHOD is not ITRAQ4
-	# If left blank will be replaced with default
-	# Please check documentation for more detail
+	# If left blank filtering will not be performed
 	SPEC_EVALUE_TRESHOLD = 1e-10
 	pNA = 4
 	# QUANTIFICATION_METHOD: / trapezoidation / max / sum / SI / SIgi / SIn / SAF / NSAF  

### 2016-05-27 itraq.R

@@ -59,14 +59,18 @@ msexp.id          <- addIdentificationData(msexp.raw, id = mzid.files,verbose=F)
 idSummary(msexp.id)
 rm(mzid.files)
 rm(mzml.files)
-#rm(mzids.raw)
 rm(msexp.raw)
 gc(verbose = FALSE)
 
-print("Filtering...")
-k                 <- (fData(msexp.id)$'ms-gf:specevalue'< specvalue_threshold)
-k[is.na(k)]       <- FALSE
-msexp.filter1     <- removeNoId(msexp.id, keep=k)
+if(specvalue_threshold==0)
+{
+  msexp.filter1     <- msexp.id
+} else {
+  print("Filtering...")
+  k                 <- (fData(msexp.id)$'ms-gf:specevalue'< specvalue_threshold)
+  k[is.na(k)]       <- FALSE
+  msexp.filter1     <- removeNoId(msexp.id, keep=k)
+} 
 
 rm(msexp.id)
 gc(verbose = FALSE)

### 2016-05-27 Benchmark/MSGF-Benchmark/msgf-benchmark2.Rmd
benchmark

--- 2016-05-27 Benchmark/MSGF-Benchmark/msgf-benchmark2.Rmd
@@
 
-```{r, warning=FALSE, echo=FALSE, include=FALSE, cache=T}
+```{r, warning=FALSE, echo=FALSE, include=FALSE, cache=F}
 setwd("~/Dropbox/_SPACE/Benchmark/11")
@@
 c_pnnl = pnnl[pnnl$MSGFDB_SpecEValue<evalue,]
-# No of remaining scans 
-nrow(c_pnnl)
-head(c_pnnl,2)
-tail(c_pnnl,2)
+print(paste("Remaining peptides:",nrow(c_pnnl)))
+# print("====== head ======")
+# head(c_pnnl,2)
+# print("====== tail ======")
+# tail(c_pnnl,2)
 
@@
 
-### a. From Docker
+### b. From Docker
 ```{r, echo=F}
 c_docker = docker[docker$Spec_Evalue<evalue,]
-# No of remaining scans 
-nrow(c_docker)
-head(c_docker,2)
-tail(c_docker,2)
+c_docker = c_docker[!is.na(c_docker$Scan),]
+c_docker = c_docker[order(c_docker$Spec_Evalue, decreasing = F),]
+print(paste("Remaining peptides:",nrow(c_docker)))
+# print("====== head ======")
+# head(c_docker,2)
+# print("====== tail ======")
+# tail(c_docker,2)
 ```
+
+### c. Differences
+```{r echo=F}
+m_table   <- merge(x=c_pnnl,y=docker,by="Scan", all=T)
+same      <- m_table[(m_table$MSGFDB_SpecEValue==m_table$Spec_Evalue) & (m_table$Peptide==m_table$PepSeq),]
+same      <- same[!is.na(same$Scan),]
+print(paste("Exact match:", nrow(same)))
+print(head(same,2))
+diff_spec <- m_table[(m_table$MSGFDB_SpecEValue!=m_table$Spec_Evalue) & (m_table$Peptide==m_table$PepSeq),]
+diff_spec <- diff_spec[!is.na(diff_spec$Scan),]
+print(paste("Different Spec eValue:", nrow(diff_spec)))
+tail(diff_spec,3)
+diff_pep  <- m_table[(m_table$MSGFDB_SpecEValue!=m_table$Spec_Evalue) & (m_table$Peptide!=m_table$PepSeq),]
+diff_pep  <- diff_pep[!is.na(diff_pep$Scan),]
+print(paste("Different ID and Spec eValue:", nrow(diff_pep)))
+tail(diff_pep,3)
+```
+
+```{r, echo = F, include=F}
+evalue = 1e-15
+```
+
+#3. Differences. Spec eValue = `r evalue` 
+### a. From PNNL
+```{r, echo=F}
+c_pnnl = pnnl[pnnl$MSGFDB_SpecEValue<evalue,]
+print(paste("Remaining peptides:",nrow(c_pnnl)))
+# print("====== head ======")
+# head(c_pnnl,2)
+# print("====== tail ======")
+# tail(c_pnnl,2)
+
+```
+
+### b. From Docker
+```{r, echo=F}
+c_docker = docker[docker$Spec_Evalue<evalue,]
+c_docker = c_docker[!is.na(c_docker$Scan),]
+c_docker = c_docker[order(c_docker$Spec_Evalue, decreasing = F),]
+print(paste("Remaining peptides:",nrow(c_docker)))
+# print("====== head ======")
+# head(c_docker,2)
+# print("====== tail ======")
+# tail(c_docker,2)
+```
+
+### c. Differences
+```{r echo=F}
+m_table   <- merge(x=c_pnnl,y=docker,by="Scan", all=T)
+same      <- m_table[(m_table$MSGFDB_SpecEValue==m_table$Spec_Evalue) & (m_table$Peptide==m_table$PepSeq),]
+same      <- same[!is.na(same$Scan),]
+print(paste("Exact match:", nrow(same)))
+print(head(same,2))
+diff_spec <- m_table[(m_table$MSGFDB_SpecEValue!=m_table$Spec_Evalue) & (m_table$Peptide==m_table$PepSeq),]
+diff_spec <- diff_spec[!is.na(diff_spec$Scan),]
+print(paste("Different Spec eValue:", nrow(diff_spec)))
+tail(diff_spec,3)
+diff_pep  <- m_table[(m_table$MSGFDB_SpecEValue!=m_table$Spec_Evalue) & (m_table$Peptide!=m_table$PepSeq),]
+diff_pep  <- diff_pep[!is.na(diff_pep$Scan),]
+print(paste("Different ID and Spec eValue:", nrow(diff_pep)))
+tail(diff_pep,3)
+```
+
+```{r, echo = F, include=F}
+evalue = 1e-20
+```
+
+#3. Differences. Spec eValue = `r evalue` 
+### a. From PNNL
+```{r, echo=F}
+c_pnnl = pnnl[pnnl$MSGFDB_SpecEValue<evalue,]
+print(paste("Remaining peptides:",nrow(c_pnnl)))
+# print("====== head ======")
+# head(c_pnnl,2)
+# print("====== tail ======")
+# tail(c_pnnl,2)
+
+```
+
+### b. From Docker
+```{r, echo=F}
+c_docker = docker[docker$Spec_Evalue<evalue,]
+c_docker = c_docker[!is.na(c_docker$Scan),]
+c_docker = c_docker[order(c_docker$Spec_Evalue, decreasing = F),]
+print(paste("Remaining peptides:",nrow(c_docker)))
+# print("====== head ======")
+# head(c_docker,2)
+# print("====== tail ======")
+# tail(c_docker,2)
+```
+
+### c. Differences
+```{r echo=F}
+m_table   <- merge(x=c_pnnl,y=docker,by="Scan", all=T)
+same      <- m_table[(m_table$MSGFDB_SpecEValue==m_table$Spec_Evalue) & (m_table$Peptide==m_table$PepSeq),]
+same      <- same[!is.na(same$Scan),]
+print(paste("Exact match:", nrow(same)))
+print(head(same,2))
+diff_spec <- m_table[(m_table$MSGFDB_SpecEValue!=m_table$Spec_Evalue) & (m_table$Peptide==m_table$PepSeq),]
+diff_spec <- diff_spec[!is.na(diff_spec$Scan),]
+print(paste("Different Spec eValue:", nrow(diff_spec)))
+tail(diff_spec,3)
+diff_pep  <- m_table[(m_table$MSGFDB_SpecEValue!=m_table$Spec_Evalue) & (m_table$Peptide!=m_table$PepSeq),]
+diff_pep  <- diff_pep[!is.na(diff_pep$Scan),]
+print(paste("Different ID and Spec eValue:", nrow(diff_pep)))
+tail(diff_pep,3)
+```

### 2016-05-27 entry.py

@@ -156,7 +156,7 @@ def itraq(mzid, options):
 	lock = mzid[:-5] + ".rda.tmp"
 	out = mzid[:-5]+".rda"
 	if os.path.isfile(out) or os.path.isfile(lock):
-		print("{} ... next.".format(lock))
+		print("{} already exists... next.".format(lock))
 	else:
 		cmd = ['Rscript', "/root/itraq.R"]
 		mzml = ""
@@ -199,7 +199,7 @@ def get_pride(prideID):
 
 	
 def get_itraq_opts(options):
-	R_OPTS = dict(SPECEVALUE_TRESHOLD= 0.01, pNA= 4, QUANTIFICATION_METHOD="sum", COMBINE_BY="mean")
+	R_OPTS = dict(SPECEVALUE_TRESHOLD= 0, pNA= 4, QUANTIFICATION_METHOD="sum", COMBINE_BY="mean")
 	for k,v in R_OPTS.items():
 		try:
 			x = options.get("ITRAQ4", k)

### 2016-05-27 Benchmark/MSGF-Benchmark/msgf-benchmark2.Rmd
benchmark

@@
 \rule{\textwidth}{1pt}
-```{r, warning=FALSE, echo=FALSE, include=FALSE, cache=T}
+```{r, warning=FALSE, echo=FALSE, include=FALSE, cache=F}
 library(MSnbase)
@@
 print(paste("Exact match:", nrow(same)))
+print(paste("From PNNL:", names(same)[2],names(same)[3],". From Docker:", names(same)[4],names(same)[5]))
 print(head(same,2))
@@
 
-#3. Differences. Spec eValue = `r evalue` 
+#4. Differences. Spec eValue = `r evalue` 
 ### a. From PNNL
@@
 
-#3. Differences. Spec eValue = `r evalue` 
+#5. Differences. Spec eValue = `r evalue` 
 ### a. From PNNL

### 2016-05-31 Benchmark/MSGF-Benchmark/msgf-benchmark2.Rmd
benchmark

@@
 pnnl <- mzid_pnnl[, c("Scan", "MSGFDB_SpecEValue", "Peptide")]
-pnnl <- pnnl[!duplicated(pnnl$Scan),]
+#pnnl <- pnnl[!duplicated(pnnl$Scan),]
 pnnl$Peptide <- substr(as.character(pnnl$Peptide),1,nchar(as.character(pnnl$Peptide))-2)
@@
 
-#3. Differences. Spec eValue = `r evalue` 
+#3. Differences. Spec eValue Threshold= `r evalue` 
 ### a. From PNNL
@@
 
-#4. Differences. Spec eValue = `r evalue` 
+#4. Differences. Spec eValue Threshold = `r evalue` 
 ### a. From PNNL
@@
 
-#5. Differences. Spec eValue = `r evalue` 
+#5. Differences. Spec eValue Threshold = `r evalue` 
 ### a. From PNNL
@@
 ```
+
+#6. Differences between results from PNNL and DTA file from PNNL.
+
+MSGF+ was run against `TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11_dta.txt` using the same command (10 ppm, without Docker). 
+```{r echo=F, cache=T, warning=F}
+setwd("~/Dropbox/_SPACE/Benchmark/11")
+dta_mzid  <- mzID(file="TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11_msgfplus.mzid")
+#dta_mzml  <- readMSData(files = file_mzml[2])
+#dta       <- read.table("TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11_msgfdb.tsv", sep="\t", header = T)
+dta       <- flatten(dta_mzid)
+colnames(dta)[2] <- "Scan"
+
+```
+```{r echo=F}
+dta_merge <- merge(x=dta[,c("Scan","ms-gf:specevalue","pepseq")], y=pnnl, by="Scan", all=T)
+
+same      <- dta_merge[(dta_merge$MSGFDB_SpecEValue==dta_merge$'ms-gf:specevalue') & (dta_merge$Peptide==dta_merge$pepseq),]
+
+same      <- same[!is.na(same$Scan),]
+print(paste("Exact match:", nrow(same)))
+print(paste("From PNNL:", names(same)[2],names(same)[3],". From Docker:", names(same)[4],names(same)[5]))
+print(head(same,2))
+diff_spec      <- dta_merge[(dta_merge$MSGFDB_SpecEValue!=dta_merge$'ms-gf:specevalue') & (dta_merge$Peptide==dta_merge$pepseq),]
+
+diff_spec <- diff_spec[!is.na(diff_spec$Scan),]
+print(paste("Different Spec eValue:", nrow(diff_spec)))
+tail(diff_spec,3)
+diff_pep      <- dta_merge[(dta_merge$MSGFDB_SpecEValue!=dta_merge$'ms-gf:specevalue') & (dta_merge$Peptide!=dta_merge$pepseq),]
+
+diff_pep  <- diff_pep[!is.na(diff_pep$Scan),]
+print(paste("Different ID and Spec eValue:", nrow(diff_pep)))
+tail(diff_pep,3)
+```

### 2016-06-01 Benchmark/MSGF-Benchmark/msgf-benchmark2.Rmd
benchmark

@@
 print(paste("Exact match:", nrow(same)))
-print(paste("From PNNL:", names(same)[2],names(same)[3],". From Docker:", names(same)[4],names(same)[5]))
-print(head(same,2))
+print(paste("From Docker:", names(same)[2],names(same)[3],". From PNNL:", names(same)[4],names(same)[5]))
+print(head(same[order(same$`ms-gf:specevalue`, decreasing = T),],2))
 diff_spec      <- dta_merge[(dta_merge$MSGFDB_SpecEValue!=dta_merge$'ms-gf:specevalue') & (dta_merge$Peptide==dta_merge$pepseq),]
@@
 print(paste("Different Spec eValue:", nrow(diff_spec)))
-tail(diff_spec,3)
+tail(diff_spec[order(diff_spec$`ms-gf:specevalue`, decreasing = T),],3)
 diff_pep      <- dta_merge[(dta_merge$MSGFDB_SpecEValue!=dta_merge$'ms-gf:specevalue') & (dta_merge$Peptide!=dta_merge$pepseq),]
@@
 diff_pep  <- diff_pep[!is.na(diff_pep$Scan),]
-print(paste("Different ID and Spec eValue:", nrow(diff_pep)))
-tail(diff_pep,3)
+diff_scan <- nlevels(as.factor(diff_pep$Scan))
+print(paste("Different ID and Spec eValue:", nrow(diff_pep), "with", diff_scan, "distict Scan numbers."))
+tail(diff_pep[order(diff_pep$`ms-gf:specevalue`, decreasing = T),],3)
 ```

### 2016-06-02 Benchmark/MSGF-Benchmark/msgf-benchmark2.Rmd
benchmark

--- 2016-05-27 Benchmark/MSGF-Benchmark/msgf-benchmark2.Rmd
@@
 ```{r echo=F}
-m_table   <- merge(x=c_pnnl,y=docker,by="Scan", all=T)
+m_table   <- merge(x=c_pnnl,y=docker,by="Scan", all.x=T)
 same      <- m_table[(m_table$MSGFDB_SpecEValue==m_table$Spec_Evalue) & (m_table$Peptide==m_table$PepSeq),]
@@
 diff_spec <- m_table[(m_table$MSGFDB_SpecEValue!=m_table$Spec_Evalue) & (m_table$Peptide==m_table$PepSeq),]
+
 diff_spec <- diff_spec[!is.na(diff_spec$Scan),]
@@
 tail(diff_spec,3)
-diff_pep  <- m_table[(m_table$MSGFDB_SpecEValue!=m_table$Spec_Evalue) & (m_table$Peptide!=m_table$PepSeq),]
+diff_pep  <- m_table[(m_table$Peptide!=m_table$PepSeq),]
+
 diff_pep  <- diff_pep[!is.na(diff_pep$Scan),]
@@
 tail(diff_pep,3)
+
+unmatched <- m_table[is.na(m_table$Spec_Evalue),]
+print(paste("There are",nrow(unmatched),"of unmatched peptides"))
+head(unmatched)
+
 ```
@@
 tail(diff_pep,3)
+
+unmatched <- m_table[is.na(m_table$Spec_Evalue),]
+print(paste("There are",nrow(unmatched),"of unmatched peptides"))
+head(unmatched)
 ```
@@
 tail(diff_pep,3)
+
+unmatched <- m_table[is.na(m_table$Spec_Evalue),]
+print(paste("There are",nrow(unmatched),"of unmatched peptides"))
+head(unmatched)
+
 ```
+
+#6. Differences between results from PNNL and DTA file from PNNL.
+
+```{r echo=F, cache=T, warning=F, include=F}
+setwd("~/Dropbox/_SPACE/Benchmark/11")
+dta_mzid  <- mzID(file="TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11_msgfplus.mzid")
+#dta_mzml  <- readMSData(files = file_mzml[2])
+#dta       <- read.table("TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11_msgfdb.tsv", sep="\t", header = T)
+dta       <- flatten(dta_mzid)
+colnames(dta)[2] <- "Scan"
+
+```
+MSGF+ was run against `TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11_dta.txt` using the same command (10 ppm, without Docker).
+From `r nrow(dta)` rows, `r sum(duplicated(dta$Scan))` duplicated scan numbers were removed.
+
+```{r echo=F}
+dta <- dta[,c("Scan","ms-gf:specevalue","pepseq")]
+names(dta) <- c("Scan","MSGFDB_SpecEValue","Peptide_dta")
+dta_merge <- merge(x=pnnl, y=dta, by=c("Scan","MSGFDB_SpecEValue"), all.x=T)
+
+same      <- dta_merge[(dta_merge$Peptide_dta==dta_merge$Peptide),]
+same      <- same[!is.na(same$Scan),]
+print(paste("Exact match:", nrow(same),"out of", nrow(pnnl)))
+
+diff_pep <- dta_merge[(dta_merge$Peptide_dta!=dta_merge$Peptide),]
+print(paste("Diff peptide:", nrow(diff_pep)))
+head(diff_pep)
+```

### 2016-06-02 Benchmark/MSGF-Benchmark/msgf-benchmark2.Rmd
benchmark

@@
 
-mzid_pnnl         <- read.table(file="TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11_msgfdb_fht.txt", sep="\t", header=T)
+mzid_pnnl         <- read.table(file="TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11_groundtruth_fht.txt", sep="\t", header=T)
 frm_docker        <- read.table(file="TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11.txt", sep="\t", header = T)
@@
 setwd("~/Dropbox/_SPACE/Benchmark/11")
-dta_mzid  <- mzID(file="TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11_msgfplus.mzid")
+dta_mzid  <- mzID(file="TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11_dta.mzid")
 #dta_mzml  <- readMSData(files = file_mzml[2])
-#dta       <- read.table("TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11_msgfdb.tsv", sep="\t", header = T)
-dta       <- flatten(dta_mzid)
-colnames(dta)[2] <- "Scan"
+#dta       <- read.table("TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11_dta.tsv", sep="\t", header = T)
+dta_flt    <- flatten(dta_mzid)
+colnames(dta_flt)[2] <- "Scan"
 
@@
 MSGF+ was run against `TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11_dta.txt` using the same command (10 ppm, without Docker).
-From `r nrow(dta)` rows, `r sum(duplicated(dta$Scan))` duplicated scan numbers were removed.
 
 ```{r echo=F}
-dta <- dta[,c("Scan","ms-gf:specevalue","pepseq")]
-names(dta) <- c("Scan","MSGFDB_SpecEValue","Peptide_dta")
-dta_merge <- merge(x=pnnl, y=dta, by=c("Scan","MSGFDB_SpecEValue"), all.x=T)
+dta <- dta_flt[,c("Scan","ms-gf:specevalue","pepseq")]
+print(paste("Peptides:",nrow(dta),"with",sum(duplicated(dta$Scan)), "duplicated scan numbers."))
+names(dta) <- c("Scan","MSGFDB_SpecEValue","Peptide")
+dta <- dta[!duplicated(dta$Scan),]
+print(paste("After removing duplicates",nrow(dta), "peptides remained."))
 
-same      <- dta_merge[(dta_merge$Peptide_dta==dta_merge$Peptide),]
-same      <- same[!is.na(same$Scan),]
-print(paste("Exact match:", nrow(same),"out of", nrow(pnnl)))
+pnnl <- mzid_pnnl[, c("Scan", "MSGFDB_SpecEValue", "Peptide")]
+pnnl <- pnnl[!duplicated(pnnl$Scan),]
+pnnl$Peptide <- substr(as.character(pnnl$Peptide),1,nchar(as.character(pnnl$Peptide))-2)
+pnnl$Peptide <- substr(as.character(pnnl$Peptide),3,nchar(as.character(pnnl$Peptide)))
 
-diff_pep <- dta_merge[(dta_merge$Peptide_dta!=dta_merge$Peptide),]
-print(paste("Diff peptide:", nrow(diff_pep)))
-head(diff_pep)
+m_table <- merge(x=pnnl, y=dta, by=c("Scan"), all=T)
+
+same <- m_table[(m_table$MSGFDB_SpecEValue.x ==m_table$MSGFDB_SpecEValue.y) & (m_table$Peptide.x == m_table$Peptide.y),]
+
+diff_spec <- m_table[(m_table$MSGFDB_SpecEValue.x !=m_table$MSGFDB_SpecEValue.y) & (m_table$Peptide.x == m_table$Peptide.y),]
+
+diff_pep <- m_table[(m_table$Peptide.x != m_table$Peptide.y),]
 ```

### 2016-06-03 Benchmark/MSGF-Benchmark/msgf-benchmark2.Rmd
Benchmark

@@
 diff_pep  <- diff_pep[!is.na(diff_pep$Scan),]
-print(paste("Different ID and Spec eValue:", nrow(diff_pep)))
+print(paste("Different ID:", nrow(diff_pep)))
 tail(diff_pep,3)
@@
 diff_pep  <- diff_pep[!is.na(diff_pep$Scan),]
-print(paste("Different ID and Spec eValue:", nrow(diff_pep)))
+print(paste("Different ID", nrow(diff_pep)))
 tail(diff_pep,3)
@@
 m_table <- merge(x=pnnl, y=dta, by=c("Scan"), all=T)
-
 same <- m_table[(m_table$MSGFDB_SpecEValue.x ==m_table$MSGFDB_SpecEValue.y) & (m_table$Peptide.x == m_table$Peptide.y),]
@@
 diff_pep <- m_table[(m_table$Peptide.x != m_table$Peptide.y),]
+print(paste("Exact same:",nrow(same), "Different Spec eValue:", nrow(diff_spec), "Different Peptides:", nrow(diff_pep)))
+print("Different Spec eValue")
+#head(diff_spec)
+
+print("Different Peptides")
+head(diff_pep)
 ```
+
+#7. Quantification Benchmark
+
+```{r, echo=F}
+setwd("~/Dropbox/_SPACE/Benchmark/11")
+q_pnnl <- read.table(file="TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11_ReporterIons.txt",sep="\t", header = T)
+names(q_pnnl)[2] <- "Scan"
+q_merge <- merge(frm_docker[,c("Scan","Spec_Evalue", "iTRAQ4.114", "iTRAQ4.115", "iTRAQ4.116", "iTRAQ4.117")], y=q_pnnl[,c("Scan","Ion_114","Ion_115","Ion_116","Ion_117")], by="Scan")
+
+print(paste("No of rows",nrow(q_merge),". Error measured by = |rslt_docker - rslt_pnnl|/rslt_docker"))
+err_114 <- abs(q_merge$iTRAQ4.114-q_merge$Ion_114)/q_merge$iTRAQ4.114
+print("Ion 114")
+summary(err_114)
+
+err_115 <- abs(q_merge$iTRAQ4.115-q_merge$Ion_115)/q_merge$iTRAQ4.115
+print("Ion 115")
+summary(err_115)
+
+err_116 <- abs(q_merge$iTRAQ4.116-q_merge$Ion_116)/q_merge$iTRAQ4.116
+print("Ion 116")
+summary(err_116)
+
+err_117 <- abs(q_merge$iTRAQ4.117-q_merge$Ion_117)/q_merge$iTRAQ4.117
+print("Ion 117")
+summary(err_117)
+
+boxplot(cbind(Ion114=log2(err_114),Ion115=log2(err_115),Ion115=log2(err_116),Ion116=log2(err_117)),main="Log2 relative error")
+```

### 2016-06-03 Benchmark/MSGF-Benchmark/msgf-benchmark3.Rmd
benchmark

--- 2016-06-03 Benchmark/MSGF-Benchmark/msgf-benchmark2.Rmd
@@
 ```{r, warning=FALSE, echo=FALSE, include=FALSE, cache=F}
-setwd("~/Dropbox/_SPACE/Benchmark/11")
+setwd("~/Dropbox/_SPACE/Benchmark/11copy")
 file_mzid        <- list.files(path = ".", pattern ="mzid", all.files = F, 
@@
 -d ID_003632_9011437E.fasta  \
--t 10ppm -m 0 -inst 1 -e 1 -ti -1,2 -ntt 2 -tda 1 -minLength 6 \
+-t 30ppm -m 0 -inst 1 -e 1 -ti -1,2 -ntt 2 -tda 1 -minLength 6 \
 -maxLength 50 -minCharge 2 -maxCharge 5 -n 1 -thread 7 \
@@
 ```{r echo=F, cache=T, warning=F, include=F}
-setwd("~/Dropbox/_SPACE/Benchmark/11")
+setwd("~/Dropbox/_SPACE/Benchmark/11copy")
 dta_mzid  <- mzID(file="TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11_dta.mzid")
@@
 MSGF+ was run against `TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11_dta.txt` using the same command (10 ppm, without Docker).
+
+### a.
+
+```{r echo=F}
+dta <- dta_flt[,c("Scan","ms-gf:specevalue","pepseq")]
+print(paste("Peptides:",nrow(dta),"with",sum(duplicated(dta$Scan)), "duplicated scan numbers."))
+names(dta) <- c("Scan","MSGFDB_SpecEValue","Peptide")
+#dta <- dta[!duplicated(dta$Scan),]
+#print(paste("After removing duplicates",nrow(dta), "peptides remained."))
+
+pnnl <- mzid_pnnl[, c("Scan", "MSGFDB_SpecEValue", "Peptide")]
+pnnl <- pnnl[!duplicated(pnnl$Scan),]
+pnnl$Peptide <- substr(as.character(pnnl$Peptide),1,nchar(as.character(pnnl$Peptide))-2)
+pnnl$Peptide <- substr(as.character(pnnl$Peptide),3,nchar(as.character(pnnl$Peptide)))
+
+m_table <- merge(x=pnnl, y=dta, by=c("Scan"), all=T)
+print("x = PNNL y=MSGF+")
+same <- m_table[(m_table$MSGFDB_SpecEValue.x ==m_table$MSGFDB_SpecEValue.y) & (m_table$Peptide.x == m_table$Peptide.y),]
+
+diff_spec <- m_table[(m_table$MSGFDB_SpecEValue.x !=m_table$MSGFDB_SpecEValue.y) & (m_table$Peptide.x == m_table$Peptide.y),]
+
+diff_pep <- m_table[(m_table$Peptide.x != m_table$Peptide.y),]
+print(paste("Exact same:",nrow(same), "Different Spec eValue:", nrow(diff_spec), "Different Peptides:", nrow(diff_pep)))
+print("Different Spec eValue")
+#head(diff_spec)
+
+print("Different Peptides")
+tail(diff_pep)
+```
+
+### a. Duplicates removed
 
@@
 m_table <- merge(x=pnnl, y=dta, by=c("Scan"), all=T)
+print("x = PNNL y=MSGF+")
 same <- m_table[(m_table$MSGFDB_SpecEValue.x ==m_table$MSGFDB_SpecEValue.y) & (m_table$Peptide.x == m_table$Peptide.y),]
@@
 ```{r, echo=F}
-setwd("~/Dropbox/_SPACE/Benchmark/11")
+setwd("~/Dropbox/_SPACE/Benchmark/11copy")
 q_pnnl <- read.table(file="TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11_ReporterIons.txt",sep="\t", header = T)

### 2016-06-23 Manuals/PrideID/Manual-PrideID.Rmd
archive

--- 2016-06-03 Benchmark/MSGF-Benchmark/msgf-benchmark3.Rmd
@@
 ```{r, warning=FALSE, echo=FALSE, include=FALSE, cache=F}
-setwd("~/Dropbox/_SPACE/Benchmark/11copy")
+setwd("~/Desktop/11copy")
 file_mzid        <- list.files(path = ".", pattern ="mzid", all.files = F, 
@@
 ```{r echo=F, cache=T, warning=F, include=F}
-setwd("~/Dropbox/_SPACE/Benchmark/11copy")
+setwd("~/Desktop/11copy")
 dta_mzid  <- mzID(file="TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11_dta.mzid")
@@
 ```{r, echo=F}
-setwd("~/Dropbox/_SPACE/Benchmark/11copy")
+setwd("~/Desktop/11copy")
 q_pnnl <- read.table(file="TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11_ReporterIons.txt",sep="\t", header = T)

### 2016-06-23 _archieve_/itraq/_functions.py

@@ -1,113 +1,0 @@
-# DANIEL.KRISTIYANTO@PNNL.GOV
-
-import os
-import sys
-import subprocess
-import re
-from os.path import isfile, join
-from urlparse import urlparse
-from ftplib import FTP
-
-######################## SUB PROCESSES ###########################
-
-def msgf(spectrum, db, out):
-	#print(spectrum, db, out)
-	if not os.path.isfile(out):
-		try:
-			subprocess.call(['java', '-Xmx3500M', '-jar', 'MSGFPlus.jar', '-s', spectrum, '-d', db, '-o', out])
-		except:
-			print("MZID conversion failed.")
-
-def rscript():
-	print("Filtering.")
-	runr = subprocess.call(['Rscript','itraq.R'])
-
-######################## SCAN FILES ###########################
-
-def scan_spectrum(working_dir):
-	spectrum = []
-	for file in os.listdir(working_dir):
-		if file.lower().endswith((".mzml",".mgf", ".mzxml", ".ms2", ".pkl")):
-			spectrum.append(join(working_dir, file))
-			if (len(spectrum)==0):
-				print("Missing spectrum files.")
-				exit()
-			#print("Spectrum: ", file)
-	return spectrum
-
-def scan_mzid(working_dir):
-	mzid = []
-	for file in os.listdir(working_dir):
-		if file.lower().endswith((".mzid")):
-			mzid.append(join(working_dir, file))
-			if (len(mzid)==0):
-				print("No MZID file found.")
-				exit()
-			#print("MZID: ", file)
-	return mzid
-
-
-def scan_dir(working_dir):
-	db 			= None
-	module 		= None
-	input_csv	= None
-	for file in os.listdir(working_dir):
-		if file.lower().endswith(".fasta"):
-			db 			= join(working_dir, file)
-			if (db == None):
-				print("Missing database file.")
-				exit()
-			#print("Database: ", file)
-		if file.lower().endswith(".mod"):
-			module		= join(working_dir, file)
-			if (module == None):
-				print("Missing module file.")
-			#print("Module:", file)
-		if file.lower().endswith(".csv"):
-			input_csv 	= join(working_dir, file)
-			if (input_csv != None):
-				print(input_csv)
[…]

### 2016-06-23 _archieve_/itraq/entry.py

@@ -1,77 +1,0 @@
-# THIS SCRIPT WILL SCAN FOR THE FILES IN A FOLDER
-# EXTRACT, IF NECESSARY, AND RUN MGSF PLUS TO 
-# NORMALIZE THE DATA
-# DANIEL.KRISTIYANTO@PNNL.GOV
-# Docker container: itraq
-
-######################## ENV ###########################
-import gzip
-import os
-import glob
-import os.path
-import subprocess
-import re
-import csv
-from ftplib import FTP
-from _functions import *
-from datetime import timedelta
-import time
-
-working_dir = os.getcwd() +"/data/"
-
-spectrum 	= []
-out 		= []
-db 			= None
-module 		= None
-input_csv	= None
-start_time = time.time()
-
-######################## DECOMPRESS ###########################
-spectrum_tmp = []
-for src_name in glob.glob(os.path.join(working_dir, '*.gz')):
-    base = os.path.basename(src_name)
-    print("Extracting", src_name)
-    dest_name = os.path.join(working_dir, base[:-3])
-    if not os.path.isfile(dest_name):
-    	spectrum_tmp.append(dest_name)
-    	with gzip.open(src_name, 'rb') as infile:
-	        with open(dest_name, 'wb') as outfile:
-	            for line in infile:
-	                outfile.write(line)
-	                
-spectrum 				= scan_spectrum(working_dir)
-db, input_csv 			= scan_dir(working_dir)
-#module 		= dir_content['module']
-
-######################## DOWNLOAD FTP ###########################
-if (input_csv != None):
-	with open(input_csv, 'rb') as f:
-	    reader = csv.reader(f)
-	    header = reader.next()
-	    for row in reader:
-	        for src in row:
-	        	print(src)
-	        	if (check_url(src)):
-	        		get_ftp(src)
-
-######################## CHECK FILES ###########################
-spectrum 				= scan_spectrum(working_dir)
-db, input_csv 			= scan_dir(working_dir)
-for s in spectrum:
-	out = os.path.splitext(s)[0]+'.mzid'
-	msgf(s,db,out)
-
-if len(scan_mzid(working_dir)) != 0:
-	try:
-		print("Filtering.")
-		rscript()
-		print("Done.")
-	except:
-		print("Filtering failed.")
-else:
-	print("Missing MZID Files.")
-	print("Windows/Mac Users:")
[…]

### 2016-06-23 _archieve_/itraq/itraq.R

@@ -1,45 +1,0 @@
-library(MSnbase)
-library(mzID)
-library(stringr)
-
-setwd("/root/data")
-
-####################################### READ FILE ###################################################
-print("Isobaric Tagging Quantification")
-mzid.files        <- list.files(path = ".", pattern ="mzid", all.files = F, 
-                       full.names = F, recursive = F, ignore.case = T, include.dirs = F)
-mzml.files        <- list.files(path = ".", pattern ="mzML$|mzXML$", all.files = F, 
-                       full.names = F, recursive = F, ignore.case = T, include.dirs = F)
-
-mzids.raw         <- mzID(mzid.files)
-msexp.raw         <- readMSData(mzml.files)
-
-####################################### IDENTIFICATION ###################################################
-print("Identifiying...")
-msexp             <- addIdentificationData(msexp.raw, id = mzids.raw)
-idSummary(msexp)
-msexp             <- removeNoId(msexp)
-msexp             <- removeMultipleAssignment(msexp)
-
-####################################### CLEAN UP ###################################################
-rm(mzid.files)
-rm(mzml.files)
-rm(msexp.raw)
-rm(mzids.raw)
-
-####################################### QUANTIFICATION ###################################################
-print("Quantifying...")
-qnt               <- quantify(msexp, method="max", reporters=iTRAQ4, strict=F, verbose=F)
-qnt               <- filterNA(qnt, pNA = 0)
-agg               <- combineFeatures(qnt, groupBy = fData(qnt)$accession, fun="mean")
-
-head(exprs(agg))
-####################################### OUTPUT ###################################################
-print("Writing the output...")
-spectrum.count  <- as.data.frame(merge(fData(qnt)[,c("spectrum", "pepseq", "idFile", "ms-gf:evalue")], exprs(qnt), by="row.names"))
-quantified      <- as.data.frame(cbind(Accession_ID=str_replace(row.names(agg),"ref\\|",""),exprs(agg)))
-write.table(spectrum.count, quote=F, row.names=T, file="evalue.txt", sep ="\t")
-write.table(quantified, row.names = F, quote=F, file="LabelledQuant.txt", sep = "\t")
-#save.image(file="LabelledQuant.Rdata")
-
-

### 2016-06-23 _archieve_/itraquant/_functions.py

@@ -1,159 +1,0 @@
-# DANIEL.KRISTIYANTO@PNNL.GOV
-# Container: itraquant
-
-import os
-import sys
-import subprocess
-import re
-from os.path import isfile, join
-from urlparse import urlparse
-from ftplib import FTP
-from urlparse import urlparse
-from ConfigParser import SafeConfigParser
-
-######################## SUB PROCESSES ###########################
-def get_sc_opts(cfg_file):
-	r_options = []
-	parser = SafeConfigParser()
-	try: 
-		parser.read(cfg_file)
-		sc_options = ["score_treshold","error_treshold", "fdr", "iteration"]
-		for o in sc_options:
-			print(o +": "+parser.get("spectrum_count",o))
-			r_options.append(parser.get("spectrum_count",o))
-		return r_options
-	except:
-		print("Configuration File Error.")
-
-
-def get_itraq_opts(cfg_file):
-	r_options = []
-	parser = SafeConfigParser()
-	try: 
-		parser.read(cfg_file)
-		sc_options = ["evalue_treshold","pNA", "quant_method", "combine_by"]
-		for o in sc_options:
-			print(o +": "+parser.get("itraq4",o))
-			r_options.append(parser.get("itraq4",o))
-		return r_options
-	except:
-		print("Configuration File Error.")
-		raise SystemExit
-
-
-def msgf(spectrum, db, out):
-	#print(spectrum, db, out)
-	if not os.path.isfile(out):
-		try:
-			subprocess.call(['java', '-Xmx3500M', '-jar', 'MSGFPlus.jar', '-s', spectrum, '-d', db, '-o', out])
-		except:
-			print("MZID conversion failed.")
-
-def rscript(r_options):
-	cmd = ['Rscript','itraq.R']
-	cmd.extend([str(x) for x in r_options])
-	runr = subprocess.call(cmd)
-
-######################## SCAN FILES ###########################
-
-def scan_spectrum(working_dir):
-	spectrum = []
-	for file in os.listdir(working_dir):
-		if file.lower().endswith((".mzml",".mgf", ".mzxml", ".ms2", ".pkl")):
-			spectrum.append(join(working_dir, file))
-			if (len(spectrum)==0):
-				print("Missing spectrum files.")
-				exit()
-			#print("Spectrum: ", file)
-	return spectrum
-
-def scan_mzid(working_dir):
[…]

### 2016-06-23 _archieve_/itraquant/entry.py

@@ -1,82 +1,0 @@
-# THIS SCRIPT WILL SCAN FOR THE FILES IN A FOLDER
-# EXTRACT, IF NECESSARY, AND RUN MGSF PLUS TO 
-# NORMALIZE THE DATA
-# DANIEL.KRISTIYANTO@PNNL.GOV
-# Docker Container: itraquant
-
-######################## ENV ###########################
-import gzip
-import os
-import glob
-import os.path
-import subprocess
-import re
-import csv
-from ftplib import FTP
-from _functions import *
-from datetime import timedelta
-import time
-
-working_dir = os.getcwd() +"/data/"
-
-spectrum 	= []
-out 		= []
-db 			= None
-module 		= None
-input_csv	= None
-start_time = time.time()
-
-######################## READ CONFIG FILES ###########################
-
-working_dir = os.getcwd() +"/data/"
-#working_dir = "/Users/Daniel/Desktop/t/"
-cfg_file = os.path.join(working_dir, "p3.config")
-if os.path.isfile(cfg_file):
-	r_options = get_itraq_opts(cfg_file)
-else:
-	write_config(working_dir)
-	r_options = get_itraq_opts(cfg_file)
-
-######################## DECOMPRESS ###########################
-spectrum_tmp = []
-for src_name in glob.glob(os.path.join(working_dir, '*.gz')):
-    base = os.path.basename(src_name)
-    # print("Extracting", src_name)
-    dest_name = os.path.join(working_dir, base[:-3])
-    if not os.path.isfile(dest_name):
-    	spectrum_tmp.append(dest_name)
-    	with gzip.open(src_name, 'rb') as infile:
-	        with open(dest_name, 'wb') as outfile:
-	            for line in infile:
-	                outfile.write(line)
-	                
-spectrum 				= scan_spectrum(working_dir)
-db, input_csv 			= scan_dir(working_dir)
-
-######################## DOWNLOAD FTP ###########################
-if (input_csv != None):
-	with open(input_csv, 'rb') as f:
-	    reader = csv.reader(f)
-	    header = reader.next()
-	    for row in reader:
-	        for src in row:
-	        	print(src)
-	        	if (check_url(src)):
-	        		get_ftp(src)
-
-######################## CHECK FILES ###########################
-spectrum 				= scan_spectrum(working_dir)
-db, input_csv 			= scan_dir(working_dir)
-
-if len(scan_mzid(working_dir)) != 0:
[…]

### 2016-06-23 _archieve_/itraquant/itraq.R

@@ -1,81 +1,0 @@
-## Labelled (iTRAQ4) Mass Spectometry Protein Quantification
-## Docker Package: p3:itraquant
-## Daniel Kristiyanto (daniel.kristiyanto@pnnl.gov)
-
-library(MSnbase)
-library(mzID)
-library(stringr)
-
-start.time = Sys.time()
-args = commandArgs(trailingOnly=TRUE)
-
-print(args)
-
-if (length(args)!=4) {
-  stop("Arguments ", call.=FALSE)
-} else {
-  evalue_treshold  	= as.double(args[1])
-  pNA 				= as.numeric(args[2])
-  quant_method		= args[3]
-  combine_by		= args[4]
-}
-
-print(paste("evalue_treshold:", evalue_treshold))
-print(paste("pNA:", pNA))
-print(paste("quant_method:", quant_method))
-print(paste("combine_by:", combine_by))
-
-setwd("/root/data")
-
-####################################### READ FILE ###################################################
-print("Isobaric Tagging Quantification")
-mzid.files        <- list.files(path = ".", pattern ="mzid", all.files = F, 
-                       full.names = F, recursive = F, ignore.case = T, include.dirs = F)
-mzml.files        <- list.files(path = ".", pattern ="mzML$|mzXML$", all.files = F, 
-                       full.names = F, recursive = F, ignore.case = T, include.dirs = F)
-
-mzids.raw         <- mzID(mzid.files)
-msexp.raw         <- readMSData(mzml.files)
-
-####################################### IDENTIFICATION & FILTERING ###################################################
-print("Identifiying...")
-msexp.id          <- addIdentificationData(msexp.raw, id = mzids.raw)
-idSummary(msexp.id)
-rm(mzid.files)
-rm(mzml.files)
-rm(mzids.raw)
-rm(msexp.raw)
-gc(verbose = FALSE)
-
-print("Filtering...")
-k                 <- (fData(msexp.id)$'ms-gf:evalue'< evalue_treshold)
-k[is.na(k)]       <- FALSE
-msexp.filter1     <- removeNoId(msexp.id, keep=k)
-msexp.filter2     <- removeMultipleAssignment(msexp.filter1)
-
-rm(msexp.id)
-rm(msexp.filter1)
-gc(verbose = FALSE)
-####################################### QUANTIFICATION ###################################################
-print("Quantifying...")
[…]

### 2016-06-23 _archieve_/msgf/_functions.py

@@ -1,127 +1,0 @@
-# DANIEL.KRISTIYANTO@PNNL.GOV
-# MSGF
-
-import os
-import sys
-import subprocess
-import re
-from os.path import isfile, join
-from urllib.parse import urlparse
-from ftplib import FTP
-
-######################## SUB PROCESSES ###########################
-
-def touch(fname, times=None):
-	with open(fname, 'a'):
-		os.utime(fname, times)
-
-######################## SUB PROCESSES ###########################
-
-def msgf(spectrum, db, out):
-	#print(spectrum, db, out)
-	lock = out+".lock"
-	if (not os.path.isfile(out)) and (not os.path.isfile(lock)) :
-		try:
-			touch(lock)
-			subprocess.call(['java', '-Xmx3500M', '-jar', 'MSGFPlus.jar', '-s', spectrum, '-d', db, '-o', out])			
-			os.remove(lock)
-		except:
-			print("MZID conversion failed.")
-
-def rscript():
-	print("Filtering.")
-	runr = subprocess.call(['Rscript','itraq.R'])
-
-######################## SCAN FILES ###########################
-
-def scan_spectrum(working_dir):
-	spectrum = []
-	for file in os.listdir(working_dir):
-		if file.lower().endswith((".mzml",".mgf", ".mzxml", ".ms2", ".pkl")):
-			spectrum.append(join(working_dir, file))
-			if (len(spectrum)==0):
-				print("Missing spectrum files.")
-				exit()
-			#print("Spectrum: ", file)
-	return spectrum
-
-def scan_mzid(working_dir):
-	mzid = []
-	for file in os.listdir(working_dir):
-		if file.lower().endswith((".mzid")):
-			mzid.append(join(working_dir, file))
-			if (len(mzid)==0):
-				print("No MZID file found.")
-				exit()
-			#print("MZID: ", file)
-	return mzid
-
-
-def scan_dir(working_dir):
-	db 			= None
-	module 		= None
-	input_csv	= None
-	for file in os.listdir(working_dir):
-		if file.lower().endswith(".fasta"):
-			db 			= join(working_dir, file)
-			if (db == None):
-				print("Missing database file.")
-				exit()
-			#print("Database: ", file)
-		if file.lower().endswith(".mod"):
[…]

### 2016-06-23 _archieve_/msgf/entry.py

@@ -1,72 +1,0 @@
-# THIS SCRIPT WILL SCAN FOR THE FILES IN A FOLDER
-# EXTRACT, IF NECESSARY, AND RUN MGSF PLUS TO 
-# NORMALIZE THE DATA
-# DANIEL.KRISTIYANTO@PNNL.GOV
-# Docker container: msgf
-
-######################## ENV ###########################
-import gzip
-import os
-import glob
-import os.path
-import subprocess
-import re
-import csv
-from ftplib import FTP
-from _functions import *
-from datetime import timedelta
-from datetime import datetime
-import time
-
-working_dir = os.getcwd() +"/data/"
-
-spectrum 	= []
-out 		= []
-db 			= None
-module 		= None
-input_csv	= None
-start_time = time.time()
-print("Start at:", str(datetime.now()))
-
-db, input_csv 			= scan_dir(working_dir)
-######################## DOWNLOAD FTP ###########################
-if (input_csv != None):
-	with open(input_csv) as f:
-	    reader = csv.reader(f)
-	    header = next(reader)
-	    for row in reader:
-	        for src in row:
-	        	print(src)
-	        	if (check_url(src)):
-	        		get_ftp(src)
-
-######################## DECOMPRESS ###########################
-spectrum_tmp = []
-for src_name in glob.glob(os.path.join(working_dir, '*.gz')):
-    base = os.path.basename(src_name)
-    #print("Extracting", src_name)
-    dest_name = os.path.join(working_dir, base[:-3])
-    if not os.path.isfile(dest_name):
-    	spectrum_tmp.append(dest_name)
-    	with gzip.open(src_name, 'rb') as infile:
-	        with open(dest_name, 'wb') as outfile:
-	            for line in infile:
-	                outfile.write(line)
-
-spectrum 				= scan_spectrum(working_dir)
-db, input_csv 			= scan_dir(working_dir)
-#module 		= dir_content['module']
-
-
-######################## CHECK FILES ###########################
-spectrum 				= scan_spectrum(working_dir)
-db, input_csv 			= scan_dir(working_dir)
-
-for s in spectrum:
-	out = os.path.splitext(s)[0]+'.mzid'
-	msgf(s,db,out)
-	print("Done.")
-
-elapsed_time = time.time() - start_time
-print("Finished at:", str(datetime.now()))
-print("Elapsed time:", str(timedelta(seconds=elapsed_time)))

### 2016-06-23 _archieve_/msgf/install.R

@@ -1,6 +1,0 @@
-source("https://bioconductor.org/biocLite.R")
-install.packages("RCurl")
-install.packages("XML")
-biocLite("rpx")
-biocLite("mzID")
-biocLite("MSnID")

### 2016-06-23 _archieve_/scquant/Benchmark/Celegans-Aging.R

@@ -1,118 +1,0 @@
-# Derrived from PNNL-Comp-Mass-Spec/celegans.aging
-
-
-setwd("~/Documents/GITHUB/P3/scquant/Benchmark/")
-
-
-################################# ORIGINAL SCRIPT ######################################################
-library("rpx")
-id <- "PXD002161"
-px <- PXDataset(id)
-try(setInternet2(FALSE),silent=TRUE)
-library("jsonlite")
-addr <- "http://www.ebi.ac.uk:80/pride/ws/archive/%s/list/project/%s"
-files <- fromJSON(sprintf(addr, "file", id))$list
-assays <- fromJSON(sprintf(addr, "assay", id))$list
-files <- subset(files, grepl('mzid.gz', fileName),
-                select=c("assayAccession","fileName"))
-rownames(files) <- NULL
-assays <- assays[,c("assayAccession",
-                    "experimentalFactor",
-                    "proteinCount",
-                    "peptideCount",
-                    "uniquePeptideCount",
-                    "identifiedSpectrumCount",
-                    "totalSpectrumCount")]
-pttrn <- "Diet; fully fed, Mut: glp-4(bn2ts) daf-16(mgDf50); daf-2(e1370)"
-assays <- subset(assays, grepl(pttrn, experimentalFactor, fixed=T))
-assays <- with(assays, {data.frame(assayAccession,
-                                   phenotype=sub("Age:\\s([^,]*).*", "\\1",
-                                                 experimentalFactor),
-                                   sampleName=sub(".*Name:\\s(\\w)-ctrl-FF.(\\d)", "\\1.\\2",
-                                                  experimentalFactor),
-                                   stringsAsFactors=F)})
-files <- subset(files, assayAccession %in% assays$assayAccession)
-pxget(px, files$fileName) # fetch them from PRIDE
-files$datasetName <- sub('_msgfplus.mzid.gz','',files$fileName, fixed=T)
-meta <- merge(files[,c("assayAccession","datasetName")], assays)
-rownames(meta) <- meta$datasetName
-meta <- meta[order(meta$sampleName),]
-rownames(meta) <- NULL
-
-
-library("MSnID")
-prj <- MSnID()
-prj <- read_mzIDs(object = prj, mzids = files$fileName)
-prj <- assess_termini(prj)
[…]

### 2016-06-23 _archieve_/scquant/_functions.py

@@ -1,157 +1,0 @@
-# DANIEL.KRISTIYANTO@PNNL.GOV
-# container: scquant
-
-import os
-import sys
-import subprocess
-import re
-from os.path import isfile, join
-from ftplib import FTP
-from urlparse import urlparse
-from ConfigParser import SafeConfigParser
-
-
-
-######################## CHECK CONFIG FILE ###########################
-def get_sc_opts(cfg_file):
-	r_options = []
-	parser = SafeConfigParser()
-	try: 
-		parser.read(cfg_file)
-		sc_options = ["score_treshold","error_treshold", "fdr", "iteration"]
-		for o in sc_options:
-			print(o +": "+parser.get("spectrum_count",o))
-			r_options.append(parser.get("spectrum_count",o))
-		return r_options
-	except:
-		print("Configuration File Error.")
-
-
-def get_itraq_opts(cfg_file):
-	r_options = []
-	parser = SafeConfigParser()
-	try: 
-		parser.read(cfg_file)
-		sc_options = ["evalue_treshold","pNA", "quant_method", "combine_by"]
-		for o in sc_options:
-			print(o +": "+parser.get("itraq4",o))
-			r_options.append(parser.get("itraq4",o))
-		return r_options
-	except:
-		print("Configuration File Error.")
-
-######################## SUB PROCESSES ###########################
-
-def msgf(spectrum, db, out):
-	if not os.path.isfile(out):
-		try:
-			subprocess.call(['java', '-Xmx3500M', '-jar', 'MSGFPlus.jar', '-s', spectrum, '-d', db, '-o', out])
-		except:
-			print("MZID conversion failed.")
-
-def rscript(r_options):
-	cmd = ['Rscript','filter.R']
-	cmd.extend([str(x) for x in r_options])
-	runr = subprocess.call(cmd)
-
-######################## SCAN FILES ###########################
-
-def scan_spectrum(working_dir):
-	spectrum = []
-	for file in os.listdir(working_dir):
-		if file.lower().endswith((".mzml",".mgf", ".mzxml", ".ms2", ".pkl")):
-			spectrum.append(join(working_dir, file))
-			if (len(spectrum)==0):
-				print("Missing spectrum files.")
-				exit()
-	return spectrum
-
-def scan_mzid(working_dir):
-	mzid = []
-	for file in os.listdir(working_dir):
[…]

### 2016-06-23 _archieve_/scquant/entry.py

@@ -1,87 +1,0 @@
-# THIS SCRIPT WILL SCAN FOR THE FILES IN A FOLDER
-# EXTRACT, IF NECESSARY, AND RUN MGSF PLUS TO 
-# NORMALIZE THE DATA
-# DANIEL.KRISTIYANTO@PNNL.GOV
-# Docker Container: scquant
-
-######################## ENV ###########################
-import gzip
-import os
-import glob
-import os.path
-import subprocess
-import re
-import csv
-from ftplib import FTP
-from _functions import *
-from datetime import timedelta
-import time
-
-
-spectrum 	= []
-out 		= []
-db 			= None
-module 		= None
-input_csv	= None
-
-
-######################## READ CONFIG FILES ###########################
-
-working_dir = os.getcwd() +"/data/"
-#working_dir = "/Users/Daniel/Desktop/t/"
-cfg_file = os.path.join(working_dir, "p3.config")
-if os.path.isfile(cfg_file):
-	r_options = get_sc_opts(cfg_file)
-else:
-	write_config(working_dir)
-	r_options = get_sc_opts(cfg_file)
-
-
-######################## DECOMPRESS ###########################
-spectrum_tmp = []
-for src_name in glob.glob(os.path.join(working_dir, '*.gz')):
-    base = os.path.basename(src_name)
-    print("Extracting", src_name)
-    dest_name = os.path.join(working_dir, base[:-3])
-    if not os.path.isfile(dest_name):
-    	spectrum_tmp.append(dest_name)
-    	with gzip.open(src_name, 'rb') as infile:
-	        with open(dest_name, 'wb') as outfile:
-	            for line in infile:
-	                outfile.write(line)
-
-spectrum 				= scan_spectrum(working_dir)
-db, input_csv 			= scan_dir(working_dir)
-#module 		= dir_content['module']
-
-######################## DOWNLOAD FTP ###########################
-if (input_csv != None):
-	with open(input_csv, 'rb') as f:
-	    reader = csv.reader(f)
-	    header = reader.next()
-	    for row in reader:
-	        for src in row:
-	        	print(src)
-	        	if (check_url(src)):
-	        		get_ftp(src)
-
-######################## CHECK FILES ###########################
-spectrum 				= scan_spectrum(working_dir)
-db, input_csv 			= scan_dir(working_dir)
-
-for s in spectrum:
-	out = os.path.splitext(s)[0]+'.mzid'
[…]

### 2016-06-23 _archieve_/scquant/filter.R

@@ -1,65 +1,0 @@
-library("rpx")
-library("mzID")
-library("MSnID")
-library("MSnbase")
-
-args = commandArgs(trailingOnly=TRUE)
-
-print(args)
-
-if (length(args)!=4) {
-  stop("Areguments ", call.=FALSE)
-} else {
-  score.treshold  = as.numeric(args[1])
-  error.treshold  = as.numeric(args[2])
-  fdr             = as.double(args[3])
-  iteration       = as.numeric(args[4])
-}
-
-print(paste("score_treshold:", score.treshold))
-print(paste("error_treshold:", error.treshold))
-print(paste("fdr:", fdr))
-print(paste("iteration:", iteration))
-
-setwd("/root/data/")
-
-mz.files <- list.files(path = ".", pattern ="mzid", all.files = F, 
-                       full.names = F, recursive = F, ignore.case = T, include.dirs = F)
-
-####################################### FILTERING ###################################################
-
-prj               <- MSnID(".")
-mzid              <- read_mzIDs(object = prj, mzids = mz.files)
-mzid              <- assess_termini(mzid)
-mzid              <- assess_missed_cleavages(mzid)
-show(mzid)
-#print(paste("Before Filtering:",length(accessions(prj))))
-prj               <- apply_filter(mzid, "numIrregCleavages == 0")
-rm(mzid)
-gc()
-prj               <- apply_filter(prj, "numMissCleavages < 2")
-prj$msmsScore     <- -log10(prj$`MS-GF:SpecEValue`)
-prj               <- correct_peak_selection(prj)
-prj$massError     <- abs(mass_measurement_error(prj)) # ppm
-fObj              <- MSnIDFilter(prj)
-fObj$msmsScore    <- list(comparison=">", threshold=score.treshold)
-fObj$massError    <- list(comparison="<", threshold=error.treshold)
-fObj.grid         <- optimize_filter(fObj, prj, fdr.max=fdr,
-                                     method="Grid", level="peptide", n.iter=iteration)
-set.seed(0)
-fObj.sann         <- optimize_filter(fObj.grid, prj, fdr.max=fdr,
-                                     method="SANN", level="peptide", n.iter=iteration)
-prj               <- apply_filter(prj, fObj.sann)
-
-prj <- apply_filter(prj, "!grepl('Contaminant', accession)")
-prj <- apply_filter(prj, "!grepl('XXX_', accession)")
-
[…]

### 2016-06-23 _archieve_/scquant/install.R

@@ -1,4 +1,0 @@
-source("https://bioconductor.org/biocLite.R")
-biocLite("mzID")
-biocLite("MSnbase")
-install.packages("stringr")

### 2016-06-23 _archieve_/scquant/labelfreequant.R

@@ -1,44 +1,0 @@
-library(MSnbase)
-library(mzID)
-library(stringr)
-
-setwd("/root/data")
-
-####################################### READ FILE ###################################################
-
-mzid.files        <- list.files(path = ".", pattern ="mzid", all.files = F, 
-                                full.names = F, recursive = F, ignore.case = T, include.dirs = F)
-mzml.files        <- list.files(path = ".", pattern ="mzML$|MzXML", all.files = F, 
-                                full.names = F, recursive = F, ignore.case = T, include.dirs = F)
-
-mzids.raw         <- mzID(mzid.files)
-msexp.raw         <- readMSData(mzml.files)
-
-####################################### IDENTIFICATION ###################################################
-print("Identifiying...")
-msexp             <- addIdentificationData(msexp.raw, id = mzids.raw)
-idSummary(msexp)
-msexp             <- removeNoId(msexp)
-msexp             <- removeMultipleAssignment(msexp)
-
-####################################### CLEAN UP ###################################################
-rm(mzid.files)
-rm(mzml.files)
-rm(msexp.raw)
-rm(mzids.raw)
-
-####################################### QUANTIFICATION ###################################################
-print("Quantifying...")
-qnt               <- quantify(msexp, method="count", verbose=T)
-colnames(qnt)     <- "Count"
-agg               <- combineFeatures(qnt, groupBy = fData(qnt)$accession, fun="sum")
-head(exprs(agg))
-
-####################################### OUTPUT ###################################################
-print("Writing the output...")
-spectrum.count  <- as.data.frame(merge(fData(qnt)[,c("spectrum", "pepseq", "idFile", "ms-gf:evalue")], exprs(qnt), by="row.names"))
-quantified      <- as.data.frame(cbind(Accession_ID=str_replace(row.names(agg),"ref\\|",""),exprs(agg)))
-write.table(spectrum.count, quote=F, row.names=T, file="evalue.txt", sep ="\t")
-write.table(quantified, row.names = F, quote=F, file="LabelFreeQuant.txt", sep = "\t")
-#save.image(file="LabelFreeQuant.Data")
-

### 2016-06-23 _archieve_/spectrumcount/_functions.py

@@ -1,113 +1,0 @@
-# DANIEL.KRISTIYANTO@PNNL.GOV
-
-import os
-import sys
-import subprocess
-import re
-from os.path import isfile, join
-from urlparse import urlparse
-from ftplib import FTP
-
-######################## SUB PROCESSES ###########################
-
-def msgf(spectrum, db, out):
-	#print(spectrum, db, out)
-	if not os.path.isfile(out):
-		try:
-			subprocess.call(['java', '-Xmx3500M', '-jar', 'MSGFPlus.jar', '-s', spectrum, '-d', db, '-o', out])
-		except:
-			print("MZID conversion failed.")
-
-def rscript():
-	print("Filtering.")
-	runr = subprocess.call(['Rscript','labelfreequant.R'])
-
-######################## SCAN FILES ###########################
-
-def scan_spectrum(working_dir):
-	spectrum = []
-	for file in os.listdir(working_dir):
-		if file.lower().endswith((".mzml",".mgf", ".mzxml", ".ms2", ".pkl")):
-			spectrum.append(join(working_dir, file))
-			if (len(spectrum)==0):
-				print("Missing spectrum files.")
-				exit()
-			#print("Spectrum: ", file)
-	return spectrum
-
-def scan_mzid(working_dir):
-	mzid = []
-	for file in os.listdir(working_dir):
-		if file.lower().endswith((".mzid")):
-			mzid.append(join(working_dir, file))
-			if (len(mzid)==0):
-				print("No MZID file found.")
-				exit()
-			#print("MZID: ", file)
-	return mzid
-
-
-def scan_dir(working_dir):
-	db 			= None
-	module 		= None
-	input_csv	= None
-	for file in os.listdir(working_dir):
-		if file.lower().endswith(".fasta"):
-			db 			= join(working_dir, file)
-			if (db == None):
-				print("Missing database file.")
-				exit()
-			#print("Database: ", file)
-		if file.lower().endswith(".mod"):
-			module		= join(working_dir, file)
-			if (module == None):
-				print("Missing module file.")
-			#print("Module:", file)
-		if file.lower().endswith(".csv"):
-			input_csv 	= join(working_dir, file)
-			if (input_csv != None):
-				print(input_csv)
[…]

### 2016-06-23 _archieve_/spectrumcount/entry.py

@@ -1,75 +1,0 @@
-# THIS SCRIPT WILL SCAN FOR THE FILES IN A FOLDER
-# EXTRACT, IF NECESSARY, AND RUN MGSF PLUS TO 
-# NORMALIZE THE DATA
-# DANIEL.KRISTIYANTO@PNNL.GOV
-# Docker Container: spectrumcount
-
-######################## ENV ###########################
-import gzip
-import os
-import glob
-import os.path
-import subprocess
-import re
-import csv
-from ftplib import FTP
-from _functions import *
-from datetime import timedelta
-import time
-
-working_dir = os.getcwd() +"/data/"
-
-spectrum 	= []
-out 		= []
-db 			= None
-module 		= None
-input_csv	= None
-
-######################## DECOMPRESS ###########################
-spectrum_tmp = []
-for src_name in glob.glob(os.path.join(working_dir, '*.gz')):
-    base = os.path.basename(src_name)
-    print("Extracting", src_name)
-    dest_name = os.path.join(working_dir, base[:-3])
-    if not os.path.isfile(dest_name):
-    	spectrum_tmp.append(dest_name)
-    	with gzip.open(src_name, 'rb') as infile:
-	        with open(dest_name, 'wb') as outfile:
-	            for line in infile:
-	                outfile.write(line)
-
-spectrum 				= scan_spectrum(working_dir)
-db, input_csv 			= scan_dir(working_dir)
-#module 		= dir_content['module']
-
-######################## DOWNLOAD FTP ###########################
-if (input_csv != None):
-	with open(input_csv, 'rb') as f:
-	    reader = csv.reader(f)
-	    header = reader.next()
-	    for row in reader:
-	        for src in row:
-	        	print(src)
-	        	if (check_url(src)):
-	        		get_ftp(src)
-
-######################## CHECK FILES ###########################
-spectrum 				= scan_spectrum(working_dir)
-db, input_csv 			= scan_dir(working_dir)
-
-for s in spectrum:
-	out = os.path.splitext(s)[0]+'.mzid'
-	msgf(s,db,out)
-
-if len(scan_mzid(working_dir)) != 0:
-	try:
-		print("Filtering.")
-		rscript()
-		print("Done.")
-	except:
-		print("Filtering failed.")
-else:
-	print("Missing MZID Files.")
-	print("Windows/Mac Users:")
-	print("Hint for java heap memory space error: increase VM/Virtualbox Base Memory allocation.")
-

### 2016-06-23 pride.R
pride.R

@@ -10,7 +10,7 @@ print(args)
 args = commandArgs(trailingOnly=TRUE)
 
 px    <- PXDataset(args)
-files  <- grep("mzXML|fasta|mzml", pxfiles(px), value = TRUE)
+files  <- grep("mzXML|fasta|mzml|mzML", pxfiles(px), value = TRUE)
 
 for(f in files)
 {

### 2016-06-23 Manuals/PrideID/Manual-PrideID.Rmd
slides

--- 2016-06-03 Benchmark/MSGF-Benchmark/msgf-benchmark2.Rmd
@@
   | Portable Proteomics Pipeline (P3) 
-  | MSGF Benchmark
+  | Use Case: PrideID
 author: "Daniel Kristiyanto (daniel.kristiyanto@pnnl.gov)"
@@
 fontsize: 10pt
-output: pdf_document
+output: 
+  pdf_document: 
+    highlight: monochrome
 # bibliography: ../../media/ref.bib
@@
 \rule{\textwidth}{1pt}
-```{r, warning=FALSE, echo=FALSE, include=FALSE, cache=F}
-library(MSnbase)
-library(mzID)
-library(stringr)
+
+### Pride ID
+
+This is a use case/manual for a P3 pipeline with files retrieved from Pride database.
+
+1. Make sure [Docker engine](https://docs.docker.com/engine/installation/) is installed and running.
 ```
-
-```{r, warning=FALSE, echo=FALSE, include=FALSE, cache=F}
-setwd("~/Dropbox/_SPACE/Benchmark/11")
-file_mzid        <- list.files(path = ".", pattern ="mzid", all.files = F, 
-                      full.names = F, recursive = F, ignore.case = T, include.dirs = F)
-file_mzml        <- list.files(path = ".", pattern ="mzML$|mzXML$", all.files = F, 
-                      full.names = F, recursive = F, ignore.case = T, include.dirs = F)
-file_fasta        <- list.files(path = ".", pattern ="fasta", all.files = F, 
-                      full.names = F, recursive = F, ignore.case = T, include.dirs = F)
-
-mzid_pnnl         <- read.table(file="TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11_groundtruth_fht.txt", sep="\t", header=T)
-frm_docker        <- read.table(file="TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11.txt", sep="\t", header = T)
-
-pnnl <- mzid_pnnl[, c("Scan", "MSGFDB_SpecEValue", "Peptide")]
-pnnl <- pnnl[!duplicated(pnnl$Scan),]
-pnnl$Peptide <- substr(as.character(pnnl$Peptide),1,nchar(as.character(pnnl$Peptide))-2)
-pnnl$Peptide <- substr(as.character(pnnl$Peptide),3,nchar(as.character(pnnl$Peptide)))
-docker       <- frm_docker[,c("Scan","Spec_Evalue","PepSeq")]
+docker ps
 ```
-
-# 1. Files:
-
-```{r, echo=F}
-print("From PNNL: TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11_msgfdb_fht.txt")
-print("From Docker: TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11.txt")
-```
-
-# 2. Identification:
-Identification used the following switches:
-```
-# Command Line (2)
-java -Xmx8000M -jar P3/MSGFPlus.jar -s \
-TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11.mzML -o \
-TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11.mzid \
--d ID_003632_9011437E.fasta  \
--t 10ppm -m 0 -inst 1 -e 1 -ti -1,2 -ntt 2 -tda 1 -minLength 6 \
--maxLength 50 -minCharge 2 -maxCharge 5 -n 1 -thread 7 \
--mod MSGFDB_Mods.txt -minNumPeaks 5 -addFeatures 1
-```
-
-```{r, echo = F, include=F}
-evalue = 1e-10
-```
-
-#3. Differences. Spec eValue Threshold= `r evalue` 
-### a. From PNNL
-```{r, echo=F}
-c_pnnl = pnnl[pnnl$MSGFDB_SpecEValue<evalue,]
-print(paste("Remaining peptides:",nrow(c_pnnl)))
-# print("====== head ======")
-# head(c_pnnl,2)
-# print("====== tail ======")
-# tail(c_pnnl,2)
+2. Download a sample [p3.config](p3.config) and [MSGFDB_Mods.txt](MSGFDB_Mods.txt) file and put it to a directory. e.g.
 
 ```
+cd ~/Desktop/PXD001468
+ls
+```
+If other PrideID is desired, change the PRIDEID option on the p3.config. Ensure that the corresponding PrideID have the required files (\*.fasta, \*.mzml, etc.).
 
-### b. From Docker
-```{r, echo=F}
-c_docker = docker[docker$Spec_Evalue<evalue,]
-c_docker = c_docker[!is.na(c_docker$Scan),]
-c_docker = c_docker[order(c_docker$Spec_Evalue, decreasing = F),]
-print(paste("Remaining peptides:",nrow(c_docker)))
-# print("====== head ======")
-# head(c_docker,2)
-# print("====== tail ======")
-# tail(c_docker,2)
-```
-
-### c. Differences
-```{r echo=F}
-m_table   <- merge(x=c_pnnl,y=docker,by="Scan", all.x=T)
-same      <- m_table[(m_table$MSGFDB_SpecEValue==m_table$Spec_Evalue) & (m_table$Peptide==m_table$PepSeq),]
-same      <- same[!is.na(same$Scan),]
-print(paste("Exact match:", nrow(same)))
-print(paste("From PNNL:", names(same)[2],names(same)[3],". From Docker:", names(same)[4],names(same)[5]))
-print(head(same,2))
-diff_spec <- m_table[(m_table$MSGFDB_SpecEValue!=m_table$Spec_Evalue) & (m_table$Peptide==m_table$PepSeq),]
-
-diff_spec <- diff_spec[!is.na(diff_spec$Scan),]
-print(paste("Different Spec eValue:", nrow(diff_spec)))
-tail(diff_spec,3)
-diff_pep  <- m_table[(m_table$Peptide!=m_table$PepSeq),]
-
-diff_pep  <- diff_pep[!is.na(diff_pep$Scan),]
-print(paste("Different ID:", nrow(diff_pep)))
-tail(diff_pep,3)
-
-unmatched <- m_table[is.na(m_table$Spec_Evalue),]
-print(paste("There are",nrow(unmatched),"of unmatched peptides"))
-head(unmatched)
+3. Download / update p3 from Dockerhub, and run the image.
 
 ```
+docker pull kristiyanto/p3
+docker run --rm -v ~/Desktop:/root/data kristiyanto/p3
+```
+if necessary, another image can be run simultaneously (in a different terminal windows).
 
-```{r, echo = F, include=F}
-evalue = 1e-15
-```
-
-#4. Differences. Spec eValue Threshold = `r evalue` 
-### a. From PNNL
-```{r, echo=F}
-c_pnnl = pnnl[pnnl$MSGFDB_SpecEValue<evalue,]
-print(paste("Remaining peptides:",nrow(c_pnnl)))
-# print("====== head ======")
-# head(c_pnnl,2)
-# print("====== tail ======")
-# tail(c_pnnl,2)
-
-```
-
-### b. From Docker
-```{r, echo=F}
-c_docker = docker[docker$Spec_Evalue<evalue,]
-c_docker = c_docker[!is.na(c_docker$Scan),]
-c_docker = c_docker[order(c_docker$Spec_Evalue, decreasing = F),]
-print(paste("Remaining peptides:",nrow(c_docker)))
-# print("====== head ======")
-# head(c_docker,2)
-# print("====== tail ======")
-# tail(c_docker,2)
-```
-
-### c. Differences
-```{r echo=F}
-m_table   <- merge(x=c_pnnl,y=docker,by="Scan", all.x=T)
-same      <- m_table[(m_table$MSGFDB_SpecEValue==m_table$Spec_Evalue) & (m_table$Peptide==m_table$PepSeq),]
-same      <- same[!is.na(same$Scan),]
-print(paste("Exact match:", nrow(same)))
-print(paste("From PNNL:", names(same)[2],names(same)[3],". From Docker:", names(same)[4],names(same)[5]))
-print(head(same,2))
-diff_spec <- m_table[(m_table$MSGFDB_SpecEValue!=m_table$Spec_Evalue) & (m_table$Peptide==m_table$PepSeq),]
-
-diff_spec <- diff_spec[!is.na(diff_spec$Scan),]
-print(paste("Different Spec eValue:", nrow(diff_spec)))
-tail(diff_spec,3)
-diff_pep  <- m_table[(m_table$Peptide!=m_table$PepSeq),]
-
-diff_pep  <- diff_pep[!is.na(diff_pep$Scan),]
-print(paste("Different ID", nrow(diff_pep)))
-tail(diff_pep,3)
-
-unmatched <- m_table[is.na(m_table$Spec_Evalue),]
-print(paste("There are",nrow(unmatched),"of unmatched peptides"))
-head(unmatched)
-```
-
-```{r, echo = F, include=F}
-evalue = 1e-20
-```
-
-#5. Differences. Spec eValue Threshold = `r evalue` 
-### a. From PNNL
-```{r, echo=F}
-c_pnnl = pnnl[pnnl$MSGFDB_SpecEValue<evalue,]
-print(paste("Remaining peptides:",nrow(c_pnnl)))
-# print("====== head ======")
-# head(c_pnnl,2)
-# print("====== tail ======")
-# tail(c_pnnl,2)
-
-```
-
-### b. From Docker
-```{r, echo=F}
-c_docker = docker[docker$Spec_Evalue<evalue,]
-c_docker = c_docker[!is.na(c_docker$Scan),]
-c_docker = c_docker[order(c_docker$Spec_Evalue, decreasing = F),]
-print(paste("Remaining peptides:",nrow(c_docker)))
-# print("====== head ======")
-# head(c_docker,2)
-# print("====== tail ======")
-# tail(c_docker,2)
-```
-
-### c. Differences
-```{r echo=F}
-m_table   <- merge(x=c_pnnl,y=docker,by="Scan", all.x=T)
-same      <- m_table[(m_table$MSGFDB_SpecEValue==m_table$Spec_Evalue) & (m_table$Peptide==m_table$PepSeq),]
-same      <- same[!is.na(same$Scan),]
-print(paste("Exact match:", nrow(same)))
-print(paste("From PNNL:", names(same)[2],names(same)[3],". From Docker:", names(same)[4],names(same)[5]))
-print(head(same,2))
-diff_spec <- m_table[(m_table$MSGFDB_SpecEValue!=m_table$Spec_Evalue) & (m_table$Peptide==m_table$PepSeq),]
-
-diff_spec <- diff_spec[!is.na(diff_spec$Scan),]
-print(paste("Different Spec eValue:", nrow(diff_spec)))
-tail(diff_spec,3)
-diff_pep  <- m_table[(m_table$Peptide!=m_table$PepSeq),]
-
-diff_pep  <- diff_pep[!is.na(diff_pep$Scan),]
-print(paste("Different ID:", nrow(diff_pep)))
-tail(diff_pep,3)
-
-unmatched <- m_table[is.na(m_table$Spec_Evalue),]
-print(paste("There are",nrow(unmatched),"of unmatched peptides"))
-head(unmatched)
-
-```
-
-#6. Differences between results from PNNL and DTA file from PNNL.
-
-```{r echo=F, cache=T, warning=F, include=F}
-setwd("~/Dropbox/_SPACE/Benchmark/11")
-dta_mzid  <- mzID(file="TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11_dta.mzid")
-#dta_mzml  <- readMSData(files = file_mzml[2])
-#dta       <- read.table("TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11_dta.tsv", sep="\t", header = T)
-dta_flt    <- flatten(dta_mzid)
-colnames(dta_flt)[2] <- "Scan"
-
-```
-MSGF+ was run against `TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11_dta.txt` using the same command (10 ppm, without Docker).
-
-```{r echo=F}
-dta <- dta_flt[,c("Scan","ms-gf:specevalue","pepseq")]
-print(paste("Peptides:",nrow(dta),"with",sum(duplicated(dta$Scan)), "duplicated scan numbers."))
-names(dta) <- c("Scan","MSGFDB_SpecEValue","Peptide")
-dta <- dta[!duplicated(dta$Scan),]
-print(paste("After removing duplicates",nrow(dta), "peptides remained."))
-
-pnnl <- mzid_pnnl[, c("Scan", "MSGFDB_SpecEValue", "Peptide")]
-pnnl <- pnnl[!duplicated(pnnl$Scan),]
-pnnl$Peptide <- substr(as.character(pnnl$Peptide),1,nchar(as.character(pnnl$Peptide))-2)
-pnnl$Peptide <- substr(as.character(pnnl$Peptide),3,nchar(as.character(pnnl$Peptide)))
-
-m_table <- merge(x=pnnl, y=dta, by=c("Scan"), all=T)
-same <- m_table[(m_table$MSGFDB_SpecEValue.x ==m_table$MSGFDB_SpecEValue.y) & (m_table$Peptide.x == m_table$Peptide.y),]
-
-diff_spec <- m_table[(m_table$MSGFDB_SpecEValue.x !=m_table$MSGFDB_SpecEValue.y) & (m_table$Peptide.x == m_table$Peptide.y),]
-
-diff_pep <- m_table[(m_table$Peptide.x != m_table$Peptide.y),]
-print(paste("Exact same:",nrow(same), "Different Spec eValue:", nrow(diff_spec), "Different Peptides:", nrow(diff_pep)))
-print("Different Spec eValue")
-#head(diff_spec)
-
-print("Different Peptides")
-head(diff_pep)
-```
-
-#7. Quantification Benchmark
-
-```{r, echo=F}
-setwd("~/Dropbox/_SPACE/Benchmark/11")
-q_pnnl <- read.table(file="TCGA_13-1489_42-2590_36-2529_117C_W_PNNL_B2S5_f11_ReporterIons.txt",sep="\t", header = T)
-names(q_pnnl)[2] <- "Scan"
-q_merge <- merge(frm_docker[,c("Scan","Spec_Evalue", "iTRAQ4.114", "iTRAQ4.115", "iTRAQ4.116", "iTRAQ4.117")], y=q_pnnl[,c("Scan","Ion_114","Ion_115","Ion_116","Ion_117")], by="Scan")
-
-print(paste("No of rows",nrow(q_merge),". Error measured by = |rslt_docker - rslt_pnnl|/rslt_docker"))
-err_114 <- abs(q_merge$iTRAQ4.114-q_merge$Ion_114)/q_merge$iTRAQ4.114
-print("Ion 114")
-summary(err_114)
-
-err_115 <- abs(q_merge$iTRAQ4.115-q_merge$Ion_115)/q_merge$iTRAQ4.115
-print("Ion 115")
-summary(err_115)
-
-err_116 <- abs(q_merge$iTRAQ4.116-q_merge$Ion_116)/q_merge$iTRAQ4.116
-print("Ion 116")
-summary(err_116)
-
-err_117 <- abs(q_merge$iTRAQ4.117-q_merge$Ion_117)/q_merge$iTRAQ4.117
-print("Ion 117")
-summary(err_117)
-
-boxplot(cbind(Ion114=log2(err_114),Ion115=log2(err_115),Ion115=log2(err_116),Ion116=log2(err_117)),main="Log2 relative error")
-```
+4. Once processes completed, the directory will be populated with:
+- Mass Spectometry files downloaded from Pride repository (\*.mzid, \*.mzml)
+- Peptide Sequence file (\*.fasta)
+- MSGF+ output files (\*.mzid, \*.canno, \*.revCat.cnlcp, *.revCat.csarr, \*.revCat.cseq)
+- Output table (\*.txt)
+- Output file as R objects (\*.rda)

### 2016-06-24 Manuals/PrideID/Manual-PrideID.Rmd
manual

@@
 ```
-If other PrideID is desired, change the PRIDEID option on the p3.config. Ensure that the corresponding PrideID have the required files (\*.fasta, \*.mzml, etc.).
+in this case, ```p3.config``` must have the following fields:
+```
+REPO = PRIDE
+PRIDEID = (e.g: PXD001468) 
+RUN_MSGF = (e.g: YES)
+METHOD = (e.g: SPECTRUM_COUNT)
+```
+
+If other PrideID is desired, change the PRIDEID option in the p3.config. Ensure that the corresponding PrideID have the required files (\*.fasta, \*.mzml, etc.).
 

### 2016-06-24 Manuals/PrideID/Manual-PrideID.Rmd
pride fix slow download

--- 2016-06-23 Manuals/PrideID/Manual-PrideID.Rmd
@@
 
-### Pride ID
-
 This is a use case/manual for a P3 pipeline with files retrieved from Pride database.
@@
 cd ~/Desktop/PXD001468
-ls
 ```
-If other PrideID is desired, change the PRIDEID option on the p3.config. Ensure that the corresponding PrideID have the required files (\*.fasta, \*.mzml, etc.).
+in this case, ```p3.config``` must have the following fields:
+```
+REPO = PRIDE
+PRIDEID = (e.g: PXD001468) 
+RUN_MSGF = (e.g: YES)
+METHOD = (e.g: SPECTRUM_COUNT)
+```
+
+If other PrideID is desired, change the PRIDEID option in the p3.config. Ensure that the corresponding PrideID have the required files (\*.fasta, \*.mzml, etc.).
 

### 2016-06-24 entry.py

@@ -302,11 +302,18 @@ def get_files(options):
 	elif src == "PRIDE":
 		prideID = options.get("SOURCE", "PRIDEID").upper()
 		if len(prideID) != 0:
-			print("Reading from PRIDE REPOSITORY. Pride ID: {}".format(prideID))
-			get_pride(prideID)
-
+			if not os.path.isfile("pride_url.txt")
+				print("Reading from PRIDE REPOSITORY. Pride ID: {}".format(prideID))
+				get_pride(prideID)
+			with open('pride_url.txt', 'r') as f:
+    			ftp1 = f.readline().rstrip()
+    			fetch_ftp(ftp1)
 		else:
 			sys.exit("Reading from PRIDE REPOSITORY. \n Error: Pride Repository is not defined. Check p3.config.")
+		try:
+			os.remove("pride.txt")
+		except:
+			pass
 	else: 
 		sys.exit("Error reading p3.config.")
 
@@ -387,6 +394,7 @@ def write_blank_p3(config_file):
 	# FTP_2 = ftp://massive.ucsd.edu/MSV000079527/peak/mgf/
 	FTP_1 = ftp://massive.ucsd.edu/MSV000079527/sequence/
 	FTP_2 = ftp://massive.ucsd.edu/MSV000079527/peak/mgf/
+
 	# if REPO = PRIDEID, PRIDEID must be defined
 	# e.g 
 	# PRIDEID = PXD000001
@@ -397,10 +405,10 @@ def write_blank_p3(config_file):
 	# e.g:
 	# RUN_MSGF = YES
 	RUN_MSGF = YES
+
 	# MSGF_OPTIONS: OPTIONAL. Additional options for identification other than -s -d and -o
 	# Check https://omics.pnl.gov/software/ms-gf for more detail
 	# e.g
-
 	# -t = 10ppm 
 	# -m = 0 
 	# -inst = 1 
@@ -422,24 +430,28 @@ def write_blank_p3(config_file):
 	# METHOD = SPECTRUM_COUNT / ITRAQ4 / NONE 
 	# If "NONE", quantification will not be run.
 	# e.g
+	# METHOD = SPECTRUM_COUNT
 	METHOD = SPECTRUM_COUNT
 	
 	[SPECTRUM_COUNT]
-	# Ignored if QUANTIFICATION METHOD is not SPECTRUM_COUNT
+	# This section is ignored if QUANTIFICATION METHOD is not SPECTRUM_COUNT
 	# If left blank filtering will not be performed
[…]

### 2016-06-24 pride.R

@@ -5,18 +5,21 @@
 
 
 library("rpx")
-print(args)
-
 args = commandArgs(trailingOnly=TRUE)
 
 px    <- PXDataset(args)
-files  <- grep("mzXML|fasta|mzml|mzML", pxfiles(px), value = TRUE)
-
-for(f in files)
-{
-  if(!file.exists(f)){
-    file.create(paste0(f,".tmp"), showWarnings = F)
-    pxget(px, f)
-    file.remove(paste0(f,".tmp"))
-  }
-}
+print(paste("Species:",pxtax(px)))
+strwrap(pxref(px))
+pxurl(px)
+cat(pxurl(px),file="pride_url.txt")
+# 
+# files  <- grep("mzXML|fasta|mzml|mzML", pxfiles(px), value = TRUE)
+# 
+# for(f in files)
+# {
+#   if(!file.exists(f)){
+#     file.create(paste0(f,".tmp"), showWarnings = F)
+#     pxget(px, f)
+#     file.remove(paste0(f,".tmp"))
+#   }
+# }

### 2016-06-24 entry.py
entry

@@ -302,7 +302,7 @@ def get_files(options):
 	elif src == "PRIDE":
 		prideID = options.get("SOURCE", "PRIDEID").upper()
 		if len(prideID) != 0:
-			if not os.path.isfile("pride_url.txt")
+			if not os.path.isfile("pride_url.txt"):
 				print("Reading from PRIDE REPOSITORY. Pride ID: {}".format(prideID))
 				get_pride(prideID)
 			with open('pride_url.txt', 'r') as f:

### 2016-06-24 entry.py
entry

@@ -306,8 +306,8 @@ def get_files(options):
 				print("Reading from PRIDE REPOSITORY. Pride ID: {}".format(prideID))
 				get_pride(prideID)
 			with open('pride_url.txt', 'r') as f:
-    			ftp1 = f.readline().rstrip()
-    			fetch_ftp(ftp1)
+				ftp1 = f.readline().rstrip()
+				fetch_ftp(ftp1)
 		else:
 			sys.exit("Reading from PRIDE REPOSITORY. \n Error: Pride Repository is not defined. Check p3.config.")
 		try:

### 2016-06-24 entry.py
faster ftp

@@ -46,7 +46,7 @@ def main():
 	unzip_files()
 
 	# Re-List the files
-	sp_files_ext = (".mzXML", ".mzML", ".MZXML", ".mzml", ".MZML", ".mzml", ".mgf",".mzxml",".ms2",".pkl")
+	sp_files_ext = (".mzXML", ".mzML", ".MZXML", ".mzml", ".MZML", ".mzml",".mzxml")
 
 	spectrum = scan_files(sp_files_ext)
 	
@@ -59,7 +59,7 @@ def main():
 	RUN_MSGF = (options.get("MSGF", "RUN_MSGF").upper() == "YES")
 	fasta = scan_fasta()
 
-
+	sys.stdout.flush()
 	# Run MSGF 
 	if fasta and spectrum and RUN_MSGF:
 		print("Running MSGF") 
@@ -280,7 +280,6 @@ def get_files(options):
 	except:
 		sys.exit("Configuration file error. Check p3.config.")
 
-	global_o = ["REPO", "FTP_1", "FTP_2", "PRIDE"]
 	if src == "LOCAL":
 		print("Reading local files.")
 
@@ -298,22 +297,24 @@ def get_files(options):
 			print("Reading from {}.".format(ftp1))
 			fetch_ftp(ftp1)
 
-		
+			
 	elif src == "PRIDE":
 		prideID = options.get("SOURCE", "PRIDEID").upper()
+		print(prideID)
 		if len(prideID) != 0:
 			if not os.path.isfile("pride_url.txt"):
 				print("Reading from PRIDE REPOSITORY. Pride ID: {}".format(prideID))
 				get_pride(prideID)
-			with open('pride_url.txt', 'r') as f:
+			with open("pride_url.txt", "r") as f:
 				ftp1 = f.readline().rstrip()
-				fetch_ftp(ftp1)
+			fetch_ftp(ftp1)
 		else:
 			sys.exit("Reading from PRIDE REPOSITORY. \n Error: Pride Repository is not defined. Check p3.config.")
 		try:
-			os.remove("pride.txt")
+			os.remove("pride_url.txt")
 		except:
 			pass
+
 	else: 
 		sys.exit("Error reading p3.config.")
 
@@ -325,23 +326,28 @@ def fetch_ftp(ftp_url):
 	ftp = FTP(url_host)
 	ftp.login()
 	ftp.cwd(url_path)
-	ftp.retrlines('LIST')
[…]

### 2016-06-24 pride.R

@@ -12,14 +12,14 @@ print(paste("Species:",pxtax(px)))
 strwrap(pxref(px))
 pxurl(px)
 cat(pxurl(px),file="pride_url.txt")
-# 
-# files  <- grep("mzXML|fasta|mzml|mzML", pxfiles(px), value = TRUE)
-# 
-# for(f in files)
-# {
-#   if(!file.exists(f)){
-#     file.create(paste0(f,".tmp"), showWarnings = F)
-#     pxget(px, f)
-#     file.remove(paste0(f,".tmp"))
-#   }
-# }
+
+files  <- grep("fasta", pxfiles(px), value = TRUE)
+
+for(f in files)
+{
+  if(!file.exists(f)){
+    file.create(paste0(f,".tmp"), showWarnings = F)
+    pxget(px, f)
+    file.remove(paste0(f,".tmp"))
+  }
+}

### 2016-06-24 SAMPLES/PrideID/command.sh
manual

@@ -1,0 +1,1 @@
+docker run --rm -v ~/Desktop/Pride:/root/data kristiyanto/p3

### 2016-06-24 SAMPLES/PrideID/command.sh
command

@@ -1,1 +1,2 @@
+eval $(docker-machine env default)
 docker run --rm -v ~/Desktop/Pride:/root/data kristiyanto/p3

### 2016-06-24 SAMPLES/FTP/Manual-FTP.Rmd
manuals

--- 2016-06-23 Manuals/PrideID/Manual-PrideID.Rmd
@@
 ```
-2. Download a sample [p3.config](p3.config) and [MSGFDB_Mods.txt](MSGFDB_Mods.txt) file and put it to a directory. e.g.
+2. Download a sample [p3.config](p3.config) and [MSGFDB_Mods.txt](MSGFDB_Mods.txt) file and put it to a directory. e.g. `~/Desktop/PXD001468`
 
@@
 cd ~/Desktop/PXD001468
-ls
 ```
-If other PrideID is desired, change the PRIDEID option on the p3.config. Ensure that the corresponding PrideID have the required files (\*.fasta, \*.mzml, etc.).
+in this case, ```p3.config``` must have the following fields:
+```
+REPO = FTP
+FTP1 = (e.g: ftp://ftp.pride.ebi.ac.uk/pride/data/archive/2015/06/PXD001468) 
+RUN_MSGF = (e.g: YES)
+METHOD = (e.g: SPECTRUM_COUNT)
+```
 
-3. Download / update p3 from Dockerhub, and run the image.
+If other PrideID is desired, change the PRIDEID option in the p3.config. Ensure that the corresponding PrideID have the required files (\*.fasta, \*.mzml, etc.).
+
+3. Download / update P3 from Dockerhub, and run the image.
 
 ```
+eval $(docker-machine env default)
 docker pull kristiyanto/p3
-docker run --rm -v ~/Desktop:/root/data kristiyanto/p3
+docker run --rm -v ~/Desktop/PXD001468:/root/data kristiyanto/p3
 ```
 if necessary, another image can be run simultaneously (in a different terminal windows).
+```
+docker run --rm -v ~/Desktop/PXD001468:/root/data kristiyanto/p3
+```
 
 4. Once processes completed, the directory will be populated with:
-- Mass Spectometry files downloaded from Pride repository (\*.mzid, \*.mzml)
-- Peptide Sequence file (\*.fasta)
-- MSGF+ output files (\*.mzid, \*.canno, \*.revCat.cnlcp, *.revCat.csarr, \*.revCat.cseq)
-- Output table (\*.txt)
-- Output file as R objects (\*.rda)
++ Mass Spectometry files downloaded from Pride repository (\*.mzid, \*.mzml)
++ MSGF+ output files (\*.mzid, \*.canno, \*.revCat.cnlcp, *.revCat.csarr, \*.revCat.cseq)
++ Output table (\*.txt)
++ Output file as R objects (\*.rda)
+
+***
+
+If the process stop returning error:
+* Make sure all the required files are in the folder. E.g: Fasta files sometimes are not provided in the FTP/Pride repository and must be provided manually. 
+* Remove all \*.tmp files before re-run the containers.

### 2016-06-24 SAMPLES/PrideID/command.sh

@@ -1,2 +1,2 @@
 eval $(docker-machine env default)
-docker run --rm -v ~/Desktop/Pride:/root/data kristiyanto/p3
+docker run --rm -v ~/Desktop/PXD001468:/root/data kristiyanto/p3

### 2016-06-24 itraq.R

@@ -30,12 +30,12 @@ print(" Quantification")
 if(quant_method=="count")
 {
   print("Spectrum Count Quantification")
-  print(paste("Spec Value Threshold:", specvalue_threshold))
+  print(paste("Spec E-Value Threshold:", specvalue_threshold))
   print(paste("features combined using:", combine_by))
 }else{
   print("iTRAQ4 Quantification")
   
-  print(paste("Spec Value Threshold:", specvalue_threshold))
+  print(paste("Spec E-Value Threshold:", specvalue_threshold))
   print(paste("pNA:", pNA))
   print(paste("quant_method:", quant_method))
   print(paste("features combined using:", combine_by))

### 2016-06-24 SAMPLES/FTP/Manual-FTP.Rmd
manual

@@
   | Portable Proteomics Pipeline (P3) 
-  | Use Case: PrideID
+  | Use Case: FTP
 author: "Daniel Kristiyanto (daniel.kristiyanto@pnnl.gov)"
@@
   \rhead{\includegraphics[width = .2\textwidth]{../../media/pnnllogo.png}}
-  \fancyfoot[LE,RO]{kristiyanto/p3:benchmark}
+  \fancyfoot[LE,RO]{kristiyanto/p3  -- source:FTP --}
 ---
@@
 ```
+![docker PS](../../media/docker-ps.png)
 2. Download a sample [p3.config](p3.config) and [MSGFDB_Mods.txt](MSGFDB_Mods.txt) file and put it to a directory. e.g. `~/Desktop/PXD001468`
@@
 ```
+![Required Files in directory](../../media/ls.png)
+
 in this case, ```p3.config``` must have the following fields:
@@
 
+![docker pull](../../media/docker-pull.png)
 ```
@@
 ```
+
+![docker run](../../media/docker-run.png)
+
 if necessary, another image can be run simultaneously (in a different terminal windows).

### 2016-06-24 SAMPLES/PrideID/Manual-PrideID.Rmd
manual

--- 2016-06-24 SAMPLES/FTP/Manual-FTP.Rmd
@@
   \rhead{\includegraphics[width = .2\textwidth]{../../media/pnnllogo.png}}
-  \fancyfoot[LE,RO]{kristiyanto/p3:benchmark}
+  \fancyfoot[LE,RO]{kristiyanto/p3   -- source:PrideID --}
 ---
@@
 ```
+![Required Files in directory](../../media/ls.png)
+
 in this case, ```p3.config``` must have the following fields:
 ```
-REPO = FTP
-FTP1 = (e.g: ftp://ftp.pride.ebi.ac.uk/pride/data/archive/2015/06/PXD001468) 
+REPO = PRIDE
+PRIDEID = (e.g: PXD001468) 
 RUN_MSGF = (e.g: YES)
@@
 
-3. Download / update P3 from Dockerhub, and run the image.
+3. Download / update p3 from Dockerhub, and run the image.
 
+![docker pull](../../media/docker-pull.png)
 ```
@@
 docker pull kristiyanto/p3
-docker run --rm -v ~/Desktop/PXD001468:/root/data kristiyanto/p3
+docker run --rm -v ~/Desktop:/root/data kristiyanto/p3
 ```
+
+![docker run](../../media/docker-run.png)
+
 if necessary, another image can be run simultaneously (in a different terminal windows).
 ```
-docker run --rm -v ~/Desktop/PXD001468:/root/data kristiyanto/p3
+docker run --rm -v ~/Desktop:/root/data kristiyanto/p3
 ```

### 2016-06-24 entry.py

@@ -199,7 +199,7 @@ def get_pride(prideID):
 
 	
 def get_itraq_opts(options):
-	R_OPTS = dict(SPECEVALUE_TRESHOLD= 0, pNA= 4, QUANTIFICATION_METHOD="sum", COMBINE_BY="mean")
+	R_OPTS = dict(SPECEVALUE_TRESHOLD= 0, pNA= 4, QUANTIFICATION_METHOD="sum", COMBINE_BY="SKIP")
 	for k,v in R_OPTS.items():
 		try:
 			x = options.get("ITRAQ4", k)
@@ -226,7 +226,7 @@ def get_msgf_opts(options):
 	return MSGF_OPTS
 
 def get_count_opts(options):
-	R_OPTS = dict(SPECEVALUE_TRESHOLD= 0, pNA= 4, QUANTIFICATION_METHOD="count", COMBINE_BY="mean")
+	R_OPTS = dict(SPECEVALUE_TRESHOLD= 0, pNA= 4, QUANTIFICATION_METHOD="count", COMBINE_BY="SKIP")
 	for k,v in R_OPTS.items():
 		try:
 			x = options.get("ITRAQ4", k)

### 2016-06-24 itraq.R

@@ -89,7 +89,7 @@ rm(msexp.filter1)
 rm(qnt)
 gc(verbose = FALSE)
 
-if(toupper(combine_by) == "SKIP")
+if(toupper(combine_by) == "skip")
 {
   result  <- qnt.filtered
 } else  

### 2016-06-24 entry.py
manuals

@@ -151,7 +151,7 @@ def msgf(spectrum, fasta, options, *opt):
 
 def itraq(mzid, options):
 	ext_set = (".mzXML", ".mzML", ".MZXML", ".mzml", ".MZML", ".mzml")
-	opts_set = ("SPECEVALUE_TRESHOLD", "pNA", "QUANTIFICATION_METHOD", "COMBINE_BY")
+	opts_set = ("SPEC_EVALUE_TRESHOLD", "pNA", "QUANTIFICATION_METHOD", "COMBINE_BY")
 	sp_files = scan_files(ext_set)
 	lock = mzid[:-5] + ".rda.tmp"
 	out = mzid[:-5]+".rda"
@@ -199,7 +199,7 @@ def get_pride(prideID):
 
 	
 def get_itraq_opts(options):
-	R_OPTS = dict(SPECEVALUE_TRESHOLD= 0, pNA= 4, QUANTIFICATION_METHOD="sum", COMBINE_BY="SKIP")
+	R_OPTS = dict(SPEC_EVALUE_TRESHOLD= 0, pNA= 4, QUANTIFICATION_METHOD="sum", COMBINE_BY="SKIP")
 	for k,v in R_OPTS.items():
 		try:
 			x = options.get("ITRAQ4", k)
@@ -226,10 +226,10 @@ def get_msgf_opts(options):
 	return MSGF_OPTS
 
 def get_count_opts(options):
-	R_OPTS = dict(SPECEVALUE_TRESHOLD= 0, pNA= 4, QUANTIFICATION_METHOD="count", COMBINE_BY="SKIP")
+	R_OPTS = dict(SPEC_EVALUE_TRESHOLD= 0, pNA= 4, QUANTIFICATION_METHOD="count", COMBINE_BY="SKIP")
 	for k,v in R_OPTS.items():
 		try:
-			x = options.get("ITRAQ4", k)
+			x = options.get("SPECTRUM_COUNT", k)
 			if len(x) != 0 : R_OPTS[k] = x
 		except:
 			continue
@@ -277,6 +277,15 @@ def check_config(cfg):
 def get_files(options):
 	try: 
 		src = options.get("SOURCE", "REPO").upper()
+		if src == "FTP":
+			try:
+				ftp1 = options.get("SOURCE", "FTP_1")
+			except:
+				sys.exit("Failed to read FTP_1 option in config file.")
+			try:
+				ftp2 = options.get("SOURCE", "FTP_1")
+			except:
+				pass
 	except:
[…]

### 2016-06-24 itraq.R

@@ -89,7 +89,7 @@ rm(msexp.filter1)
 rm(qnt)
 gc(verbose = FALSE)
 
-if(toupper(combine_by) == "skip")
+if(toupper(combine_by) == "SKIP")
 {
   result  <- qnt.filtered
 } else  

### 2016-06-24 itraq.R
latest default config

@@ -31,14 +31,16 @@ if(quant_method=="count")
 {
   print("Spectrum Count Quantification")
   print(paste("Spec E-Value Threshold:", specvalue_threshold))
-  print(paste("features combined using:", combine_by))
+  if(toupper(combine_by) != "SKIP")
+  {
+    print(paste("features combined using:", combine_by))
+  }
 }else{
   print("iTRAQ4 Quantification")
   
   print(paste("Spec E-Value Threshold:", specvalue_threshold))
   print(paste("pNA:", pNA))
   print(paste("quant_method:", quant_method))
-  print(paste("features combined using:", combine_by))
 }
 print("=======================================")
 

### 2016-06-24 itraq.R
spectrum_count

@@ -80,7 +80,7 @@ gc(verbose = FALSE)
 print("Quantifying...")
 if (quant_method=="count")
 {
-  qnt               <- quantify(msexp.filter1, method=quant_method)
+  qnt.filtered      <- quantify(msexp.filter1, method=quant_method)
 } else
 {
   qnt               <- quantify(msexp.filter1, method=quant_method, reporters=iTRAQ4, strict=F, verbose=F)

### 2016-06-24 itraq.R
spectrum count

@@ -30,17 +30,27 @@ print(" Quantification")
 if(quant_method=="count")
 {
   print("Spectrum Count Quantification")
-  print(paste("Spec E-Value Threshold:", specvalue_threshold))
+  print("iTRAQ4 Quantification")
+  if(specvalue_threshold > 0)
+  {
+    print(paste("Spec E-Value Threshold:", specvalue_threshold))
+  }
   if(toupper(combine_by) != "SKIP")
   {
     print(paste("features combined using:", combine_by))
   }
 }else{
   print("iTRAQ4 Quantification")
-  
-  print(paste("Spec E-Value Threshold:", specvalue_threshold))
+  if(specvalue_threshold > 0)
+  {
+    print(paste("Spec E-Value Threshold:", specvalue_threshold))
+  }
   print(paste("pNA:", pNA))
   print(paste("quant_method:", quant_method))
+  if(toupper(combine_by) != "SKIP")
+  {
+    print(paste("features combined using:", combine_by))
+  }
 }
 print("=======================================")
 
@@ -101,10 +111,17 @@ if(toupper(combine_by) == "SKIP")
 save(result, file=out_file)
 ####################################### OUTPUT ###################################################
 print("Writing the output...")
-quantified		  <- as.data.frame(cbind(Scan=fData(result)$'scan number(s)', Spectrum=fData(result)$spectrum, Spec_Evalue=fData(result)$'ms-gf:specevalue', AccessionID=row.names(result), PepSeq=fData(result)$pepseq, exprs(result)))
-#write.table(evalue.table, quote=F, row.names=F, file="evalue.txt", sep ="\t")
-#rm(evalue.table)
-#gc()
+if (quant_method=="count")
+{
+  Cnt=exprs(result)
+  colnames(Cnt) = "Count"
+  quantified		  <- as.data.frame(cbind(Scan=fData(result)$'scan number(s)', Spectrum=fData(result)$spectrum, Spec_Evalue=fData(result)$'ms-gf:specevalue', AccessionID=row.names(result), PepSeq=fData(result)$pepseq, Cnt))
+  
+} else
+{
+  quantified		  <- as.data.frame(cbind(Scan=fData(result)$'scan number(s)', Spectrum=fData(result)$spectrum, Spec_Evalue=fData(result)$'ms-gf:specevalue', AccessionID=row.names(result), PepSeq=fData(result)$pepseq, exprs(result)))
+}
+
[…]

### 2016-06-24 itraq.R
spectrum count

@@ -30,7 +30,6 @@ print(" Quantification")
 if(quant_method=="count")
 {
   print("Spectrum Count Quantification")
-  print("iTRAQ4 Quantification")
   if(specvalue_threshold > 0)
   {
     print(paste("Spec E-Value Threshold:", specvalue_threshold))

### 2016-06-25 itraq.R
some clean up

@@ -89,7 +89,8 @@ gc(verbose = FALSE)
 print("Quantifying...")
 if (quant_method=="count")
 {
-  qnt.filtered      <- quantify(msexp.filter1, method=quant_method)
+  qnt               <- quantify(msexp.filter1, method=quant_method)
+  qnt.filtered      <- qnt
 } else
 {
   qnt               <- quantify(msexp.filter1, method=quant_method, reporters=iTRAQ4, strict=F, verbose=F)
@@ -123,7 +124,7 @@ if (quant_method=="count")
 
 write.table(quantified, row.names = F, quote=F, file=str_replace(out_file,".rda",".txt"), sep = "\t")
 stop.time = Sys.time()
-#rm(result)
+
 print(paste("File:", out_file,"Start Time:", start.time," Stop Time:", stop.time, "Elapsed=",stop.time-start.time))
 rm(result)
 rm(qnt.filtered)

### 2016-06-25 entry.py
default config

@@ -450,7 +450,8 @@ def write_blank_p3(config_file):
 
 	# COMBINE_BY will perform feature folding with the specified function. If "SKIP" is given, this task will not be performed.
 	# COMBINE_BY: SKIP / mean / median / weighted.mean / sum / medpolish
-	COMBINE_BY = mean
+	# For spectrum count use "sum".
+	COMBINE_BY = sum
 
 	[ITRAQ4]
 	# This section is ignored if QUANTIFICATION METHOD is not ITRAQ4

### 2016-06-25 entry.py
additional comments

@@ -147,6 +147,7 @@ def msgf(spectrum, fasta, options, *opt):
 			except:
 				print("MSGF Error: {}".format(file))
 			if not os.path.isfile(out2): itraq(out, options)
+		sys.stdout.flush()
 
 
 def itraq(mzid, options):
@@ -184,6 +185,7 @@ def itraq(mzid, options):
 				os.remove(lock)
 			except:
 				print("Quantification failed.")
+	sys.stdout.flush()
    
 
 def itraq_folding(options):
@@ -207,6 +209,7 @@ def get_itraq_opts(options):
 		except:
 			continue
 	print("ITRAQ. {} : {}".format(k, R_OPTS[k]))
+	sys.stdout.flush()
 	return R_OPTS             
 
 def get_msgf_opts(options):
@@ -223,6 +226,7 @@ def get_msgf_opts(options):
 			MSGF_OPTS.append(k)
 			MSGF_OPTS.append(v)
 	#print(MSGF_OPTS)
+	sys.stdout.flush()
 	return MSGF_OPTS
 
 def get_count_opts(options):
@@ -234,6 +238,7 @@ def get_count_opts(options):
 		except:
 			continue
 	print("ITRAQ. {} : {}".format(k, R_OPTS[k]))
+	sys.stdout.flush()
 	return R_OPTS             
 
 			
@@ -254,7 +259,7 @@ def scquant(mzid_set, options):
 	else:
 		print(cmd)
 		subprocess.call(cmd)
-
+	sys.stdout.flush()
 			  
 ################################################ ADMINISTRIVIA  ################################################
 	
@@ -296,7 +301,8 @@ def get_files(options):
 		sys.exit("Reading from FTP. \n ERROR FTP Source is not defined. Check p3.config")        
 	elif src == "FTP" and options.get("SOURCE", "FTP_1") != "":
 		if len(ftp2) != 0:
-			print("Reading from {} and {}.".format(ftp1, ftp2)) 
+			print("Reading from {} and {}.".format(ftp1, ftp2))
+			sys.stdout.flush() 
 			fetch_ftp(ftp1)
 			fetch_ftp(ftp2)
 

### 2016-06-25 entry.py
general clean up

@@ -1,7 +1,7 @@
 ##########################################################################
 ## P3: Portable Proteomics Pipeline
 ## DANIEL KRISTIYANTO (daniel.kristiyanto@pnnl.gov)
-## APR 27, 2016
+## JUNE 25, 2016
 ##########################################################################
 
 
@@ -23,12 +23,11 @@ from datetime import timedelta
 
 # Set Env
 working_dir = "/root/data"
-#working_dir = "/Users/Daniel/Desktop/LABELLED"
 config_file = "p3.config"
 os.chdir(working_dir) if os.path.isdir(working_dir) else sys.exit("{} not found. Please make sure it's properly mounted.".format(working_dir))
 
 def main():
-	maxwait = 10800 # Wait for 3 hours
+	maxwait = 10800 
 	start_time = time.time()
 	print("Starting at: {}".format(str(datetime.now())))
 	
@@ -41,7 +40,6 @@ def main():
 	options = check_config(config_file)
 	get_files(options)
 	
-		
 	# Unzip the files 
 	unzip_files()
 
@@ -73,47 +71,10 @@ def main():
 	except:
 		pass
 
-	# if Q_METHOD == "SPECTRUM_COUNT":
-	# 	keep_waiting = True
-	# 	wait = 0
-	# 	lock = "SC_RESULT.txt.tmp"
-	# 	if os.path.isfile(lock): sys.exit("Spectrum Count Quantification is already run by other container. Quitting.")
-	# 	while keep_waiting:
-	# 		mzid_set = scan_files((".mzid"))
-	# 		if len(mzid_set) == 0:
-	# 			sys.exit("No .mzid file found")
-	# 		elif len(scan_files('.mzid.tmp')) != 0: 
-	# 			#print("SCAN MZID TMP:" + scan_files('.mzid.tmp'))
-	# 			print("MSGF identification is being run by other containers. Waiting...")
-	# 			if wait > maxwait:
-	# 				keep_waiting = False
-	# 				sys.exit("Had waited for {}s. Quitting now. \n Perhaps remove .tmp files and rerun containers?".format(maxwait))
-	# 			else: wait = wait + 5 
-	# 			time.sleep(5)
-	# 		else:
-	# 			touch(lock)
-	# 			scquant(mzid_set, options)
-	# 			os.remove(lock)
-	# 			keep_waiting = False
-
[…]

### 2016-06-25 entry.py
prettyfing

@@ -323,6 +323,7 @@ def unzip_files():
 	gzfiles = glob.glob("*.gz")
 	if len(gzfiles) != 0:
 		for file in gzfiles:
+			print("Unzipping {}".format(file))
 			base = os.path.basename(file)
 			dest = base[:-3]
 			if not os.path.isfile(dest):
@@ -330,6 +331,7 @@ def unzip_files():
 					with open(dest, 'wb') as outfile:
 						for line in infile:
 							outfile.write(line)
+			sys.stdout.flush()
 
 def scan_files(ext):
 	files = []
@@ -362,6 +364,7 @@ def write_blank_p3(config_file):
 	[SOURCE]
 	# REPO = LOCAL/FTP/PRIDE
 	REPO = LOCAL
+	
 	# If REPO = FTP, at least FTP_1 is required.
 	# e.g: 
 	# FTP_1 = ftp://massive.ucsd.edu/MSV000079527/sequence/ 
@@ -372,7 +375,7 @@ def write_blank_p3(config_file):
 	# if REPO = PRIDEID, PRIDEID must be defined
 	# e.g 
 	# PRIDEID = PXD000001
-	PRIDEID = 
+	PRIDEID = PXD003903
 	
 	[MSGF]
 	# RUN_MSGF = YES / NO ; if NO, MSGF identification will be skipped.
@@ -382,7 +385,7 @@ def write_blank_p3(config_file):
 
 	# MSGF_OPTIONS: OPTIONAL. Additional options for identification other than -s -d and -o
 	# Check https://omics.pnl.gov/software/ms-gf for more detail
-	# e.g
+	
 	# -t = 10ppm 
 	# -m = 0 
 	# -inst = 1 

### 2016-06-28 SAMPLES/FTP/Manual-FTP.Rmd
manuals
manual

@@
 docker pull kristiyanto/p3
+
+# Mac/Linux
 docker run --rm -v ~/Desktop/PXD001468:/root/data kristiyanto/p3
+
+## On Windows:
+docker run --rm -v /c/Users/daniel/Desktop/PXD001468:/root/data kristiyanto/p3
 ```
 
-![docker run](../../media/docker-run.png)
+![docker run](../../media/docker-run-ftp.png)
 
@@
 If the process stop returning error:
-* Make sure all the required files are in the folder. E.g: Fasta files sometimes are not provided in the FTP/Pride repository and must be provided manually. 
+* Make sure all the required files are in the folder. E.g: In the case fasta file is not provided in the FTP/Pride repository and must be provided manually. 
 * Remove all \*.tmp files before re-run the containers.

### 2016-06-28 SAMPLES/PrideID/Manual-PrideID.Rmd
manuals
manual

@@
 docker pull kristiyanto/p3
-docker run --rm -v ~/Desktop:/root/data kristiyanto/p3
+
+# Mac/Linux
+docker run --rm -v ~/Desktop/PXD001468:/root/data kristiyanto/p3
+
+## On Windows:
+docker run --rm -v /c/Users/daniel/Desktop/PXD001468:/root/data kristiyanto/p3
 ```

### 2016-06-29 entry.py
general cleanup

@@ -196,7 +196,7 @@ def get_count_opts(options):
 			if len(x) != 0 : R_OPTS[k] = x
 		except:
 			continue
-	print("ITRAQ. {} : {}".format(k, R_OPTS[k]))
+	#print("Spectrum Count. {} : {}".format(k, R_OPTS[k]))
 	sys.stdout.flush()
 	return R_OPTS             
 
